---
title: "Centrality catalogue"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Centrality catalogue}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{css, echo = FALSE}
.cg-fam-index { line-height: 1.7; }
.cg-fam-index p { margin: 0.15em 0 0.9em 0; }
h3 code { font-size: 0.92em; }
table.cg-argtable td, table.cg-argtable th { padding: 4px 8px; }
```

```{r setup}
library(cograph)
data(student_interactions)
```

A centrality is a **node-level** statistic: it assigns every node a single
number that summarises some aspect of its position in the network — how many
ties it has, how short its paths to others are, how often it sits between other
nodes, or how it participates in the network's global structure. Centralities
describe **nodes**, not edges or whole graphs, and they are the most widely used
way to compare the relative prominence of actors within a network.

`cograph` ships the **widest collection of node centrality measures available in
R — 146 in total** — spanning degree and strength, distance and closeness,
shortest-path brokerage, spectral and walk-based influence, neighbourhood
cohesion, directed prestige, and community/group-based roles. Every measure is
**equivalence-validated**: its output is checked numerically against an
established reference implementation (`igraph`, `sna`, `centiserve`,
`brainGraph`, `influenceR`, `tidygraph`, and NetworkX via `reticulate`), so
values match the canonical definitions to within documented tolerances.

`student_interactions` is a built-in edge-list dataset of observed student
interactions. It can be passed to `centrality()` directly. The single verb
`centrality()` is the recommended entry point: it returns a tidy
one-row-per-node `data.frame` and accepts an argument for every tuning knob
(see the [argument catalogue](#argument-catalogue) below).

```{r}
centrality(student_interactions)
```

Pass `type = "all"` to compute every measure at once, `measures = c(...)` to pick
a subset, `digits =` to round, and `sort_by =` to order the result.

## How to read this catalogue

Every measure below is documented with four fields:

- **Concept** — what the measure captures, in words.
- **Definition** — the formula, faithful to what `cograph` actually computes
  (verified against the package source, which is occasionally normalised
  differently from a textbook statement).
- **Meaning** — how to read a high (or low) value.
- **Example** and **Equivalence reference** — a runnable call and the external
  implementation it is validated against.

### Notation

Throughout, $G = (V, E)$ is a graph with $n = |V|$ nodes and adjacency matrix
$A = (a_{ij})$; $w_{ij}$ are edge weights, $N(v)$ is the neighbour set of $v$,
$k_v = |N(v)|$ its degree, and $s(v) = \sum_u w_{vu}$ its strength. We write
$d(u, v)$ for the shortest-path distance, $\Delta$ for the graph diameter, and
$\sigma_{st}$ (resp. $\sigma_{st}(v)$) for the number of shortest $s$–$t$ paths
(resp. those passing through $v$). $L = D - A$ is the graph Laplacian and
$\mathbf{1}$ the all-ones vector.

```{r records, echo = FALSE}
rec <- function(family, title, key, concept, math, args, meaning, reference,
                grp = FALSE, via_measures = FALSE) {
  ex <- if (via_measures) {
    sprintf('centrality(student_interactions, measures = "%s")', key)
  } else {
    sprintf("centrality_%s(student_interactions%s)", key,
            if (grp) ", membership = groups" else "")
  }
  list(family = family, title = title, key = key, concept = concept,
       math = math, args = args, meaning = meaning, reference = reference,
       example = ex)
}

records <- list(

  ## ---- Family 1: Degree, strength and local connectivity ----
  rec("Degree, strength and local connectivity",
      "Degree Centrality", "degree",
      "Degree centrality counts the number of direct ties incident on a node. In directed graphs, it can be separated into incoming and outgoing ties.",
      r"(C_D(v) = \sum_{u \in V} a_{vu} = k_v)",
      r"(`mode`, `loops`)",
      "A high degree value indicates many direct observed connections. It is a local connectivity measure and does not imply brokerage or global reach.",
      r"(Equivalent to `igraph::degree()` under matching `mode` and loop settings.)"),

  rec("Degree, strength and local connectivity",
      "Indegree Centrality", "indegree",
      "Indegree counts ties pointing into a node under a directed interpretation.",
      r"(k_v^{\mathrm{in}} = \sum_{u \in V} a_{uv})",
      r"(—)",
      "A high indegree value indicates many incoming observed ties. Its substantive meaning depends on what edge direction represents.",
      r"(Equivalent to `igraph::degree(mode = "in")`.)"),

  rec("Degree, strength and local connectivity",
      "Outdegree Centrality", "outdegree",
      "Outdegree counts ties leaving a node under a directed interpretation.",
      r"(k_v^{\mathrm{out}} = \sum_{u \in V} a_{vu})",
      r"(—)",
      "A high outdegree value indicates many outgoing observed ties. In transition networks, this can mean many possible next states.",
      r"(Equivalent to `igraph::degree(mode = "out")`.)"),

  rec("Degree, strength and local connectivity",
      "Strength Centrality", "strength",
      "Strength centrality is weighted degree: it sums edge weights instead of counting edges.",
      r"(s(v) = \sum_{u \in V} w_{vu})",
      r"(`mode`)",
      "A high strength value indicates high total incident edge weight. This should be interpreted according to how weights were defined.",
      r"(Equivalent to `igraph::strength()` when weights are supplied.)"),

  rec("Degree, strength and local connectivity",
      "Instrength Centrality", "instrength",
      "Instrength sums incoming edge weights.",
      r"(s^{\mathrm{in}}(v) = \sum_{u \in V} w_{uv})",
      r"(—)",
      "A high instrength value indicates high total incoming weight. It is a weighted incoming-connectivity measure.",
      r"(Equivalent to `igraph::strength(mode = "in")`.)"),

  rec("Degree, strength and local connectivity",
      "Outstrength Centrality", "outstrength",
      "Outstrength sums outgoing edge weights.",
      r"(s^{\mathrm{out}}(v) = \sum_{u \in V} w_{vu})",
      r"(—)",
      "A high outstrength value indicates high total outgoing weight. It does not show whether that weight is concentrated or distributed.",
      r"(Equivalent to `igraph::strength(mode = "out")`.)"),

  rec("Degree, strength and local connectivity",
      "Expected Centrality", "expected",
      "Expected centrality sums the degrees of a node's neighbours.",
      r"(C_{\mathrm{exp}}(v) = \sum_{u \in N(v)} k_u)",
      r"(`mode`)",
      "A high value indicates adjacency to well-connected nodes.",
      r"(Implemented as a native neighbourhood centrality in `cograph`.)"),

  rec("Degree, strength and local connectivity",
      "Leverage Centrality", "leverage",
      "Leverage centrality compares a node's degree with the degrees of its neighbours.",
      r"(\ell(v) = \frac{1}{k_v} \sum_{u \in N(v)} \frac{k_v - k_u}{k_v + k_u})",
      r"(`mode`)",
      "A positive high value indicates that the node is more connected than its neighbours under this degree comparison.",
      r"(Validated against `centiserve::leverage()`.)"),

  rec("Degree, strength and local connectivity",
      "Lobby Centrality", "lobby",
      "Lobby centrality is the h-index of neighbour degrees.",
      r"(h(v) = \max\bigl\{ h : |\{ u \in \{v\} \cup N(v) : k_u \ge h \}| \ge h \bigr\})",
      r"(`mode`)",
      "A high value indicates many neighbours that themselves have reasonably high degree.",
      r"(Validated against `centiserve::lobby()`.)"),

  rec("Degree, strength and local connectivity",
      "H-Index Strength Centrality", "hindex_strength",
      "H-index strength is a weighted h-index-style neighbourhood measure.",
      r"(h_s(v) = \max\bigl\{ h : |\{ u \in \{v\} \cup N(v) : s(u) \ge h \}| \ge h \bigr\})",
      r"(`mode`)",
      "A high value indicates strong ties to neighbours meeting a weighted connectivity threshold.",
      r"(Equivalent to lobby centrality on unweighted graphs in package tests.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Local H-Index Centrality", "local_hindex",
      "Local h-index centrality iteratively applies h-index logic to local neighbourhoods.",
      r"(h^{(t+1)}(v) = \mathcal{H}\bigl(\{ h^{(t)}(u) : u \in N(v) \}\bigr), \quad h^{(0)}(v) = k_v)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates a locally robust neighbourhood position under the h-index updating rule.",
      r"(Implemented following local h-index centrality formulations and checked in package tests.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Semi-Local Centrality", "semilocal",
      "Semi-local centrality extends degree-like counting beyond immediate neighbours.",
      r"(C_{SL}(v) = \sum_{u \in N(v)} \sum_{w \in N(u)} \bigl| \{\, x : d(w, x) \le 2 \,\} \bigr|)",
      r"(`mode`)",
      "A high value indicates proximity to a locally well-connected neighbourhood.",
      r"(Validated against `centiserve::semilocal()`.)"),

  rec("Degree, strength and local connectivity",
      "ClusterRank Centrality", "clusterrank",
      "ClusterRank combines neighbour degree information with local clustering.",
      r"(C_{CR}(v) = c(v) \sum_{u \in N(v)} \bigl( k_u + 1 \bigr), \quad c(v) = \text{local clustering coefficient})",
      r"(`mode`)",
      "A high value indicates local connectedness adjusted for clustering-related redundancy.",
      r"(Validated against `centiserve::clusterrank()`.)"),

  rec("Degree, strength and local connectivity",
      "Collective Influence Centrality", "collective_influence",
      "Collective influence combines a node's excess degree with excess degree on a local boundary.",
      r"(\mathrm{CI}_\ell(v) = (k_v - 1) \sum_{u \,\in\, \partial B(v, \ell)} (k_u - 1), \quad \ell = 2)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates potential importance under the collective influence model.",
      r"(Based on Morone and Makse's collective influence formulation.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "MNC Centrality", "mnc",
      "Maximum neighbourhood component centrality is the size of the largest connected component in a node's neighbourhood.",
      r"(\mathrm{MNC}(v) = \max_{C \,\in\, \mathcal{C}(G[N(v)])} |C|)",
      r"(`mode`)",
      "A high value indicates that many neighbours belong to one connected local component.",
      r"(Validated against `centiserve::mnc()`.)"),

  rec("Degree, strength and local connectivity",
      "DMNC Centrality", "dmnc",
      "DMNC is a density-adjusted version of maximum neighbourhood component centrality.",
      r"(\mathrm{DMNC}(v) = \frac{E_c}{N_c^{\,\varepsilon}}, \quad \varepsilon = 1.7)",
      r"(`mode`, `dmnc_epsilon`)",
      "A high value indicates a large and dense local neighbour component under the chosen density exponent. Here $E_c$ and $N_c$ are the edges and nodes of the largest component of $G[N(v)]$.",
      r"(Lin et al. (2008). Not equal to `centiserve::dmnc()`: that implementation counts the component's edges in the wrong index space, so it disagrees on 14 of the 34 karate nodes even at a matched epsilon. See the "Divergence from centiserve" section of `?centrality_dmnc`.)"),

  rec("Degree, strength and local connectivity",
      "LAC Centrality", "lac",
      "LAC, or local average connectivity, measures connectivity in a node's neighbourhood.",
      r"(\mathrm{LAC}(v) = \frac{1}{k_v} \sum_{u \in N(v)} \deg_{G[N(v)]}(u))",
      r"(`mode`)",
      "A high value indicates that the node's neighbours form a relatively connected local structure.",
      r"(Corresponds to CytoHubba-style local average connectivity.)"),

  rec("Degree, strength and local connectivity",
      "Gravity Centrality", "gravity",
      "Gravity centrality treats each node's mass as attracting the mass of others over graph distance, and can be truncated at a radius.",
      r"(G(v) = \sum_{u \ne v,\; d(u,v) \le R} \frac{m_v\, m_u}{d(u, v)^2}, \quad m = \text{k-shell or degree})",
      r"(`mode`, `gravity_mass`, `gravity_radius`)",
      "A high value indicates proximity to massive nodes. The default is Ma et al.'s gravity centrality (k-shell mass, radius 3); `gravity_mass = \"degree\", gravity_radius = NULL` is Li et al.'s gravity model and `gravity_radius = \"auto\"` their local gravity model.",
      r"(Ma, Ma, Zhang & Wang (2016); Li, Ren, Ma, Liu, Zhang & Zhou (2019), eqs. 1, 2 and 5. Before 2.4.8 cograph summed $k_u\, ks(u)/d^2$ with no mass on the focal node, which matched no published formula; `gravity_mass = "legacy"` reproduces those values.)"),

  rec("Degree, strength and local connectivity",
      "Neighborhood Connectivity", "neighborhood_connectivity",
      "Neighborhood connectivity is the mean degree of a node's neighbours (average neighbour degree).",
      r"(C_{NC}(v) = \frac{1}{k_v} \sum_{u \in N(v)} k_u)",
      r"(`mode`)",
      "A high value indicates attachment to hubs. Isolates score 0. Direction is respected under `mode`.",
      r"(Equivalent to `igraph::knn(weights = NA)` (Maslov & Sneppen 2002); isolates return 0 instead of NaN.)"),

  rec("Degree, strength and local connectivity",
      "Entropy Variation, Degree", "entropy_variation_degree",
      "Entropy variation is the drop in the Shannon entropy of the degree distribution when the node and its links are removed.",
      r"(EnV_k(i) = I_k(G) - I_k(G - i), \quad I_k(G) = -\sum_j \frac{k_j}{\sum_l k_l} \ln \frac{k_j}{\sum_l k_l})",
      r"(`mode`)",
      "A high value indicates a node whose removal makes the remaining degree distribution more concentrated. Signed; negative values occur.",
      r"(Ai (2017), eqs. 5-10. Matches the author's R code path and the paper's Table 2 quantiles on its 4234-node network.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Flow Coefficient", "flow_coefficient",
      "The flow coefficient is the share of a node's neighbour pairs that are linked through the node but not directly.",
      r"(fc(v) = \frac{|\{(j, k) : j \to v \to k,\ j \not\to k\}|}{k_v (k_v - 1)})",
      r"(—)",
      "A high value indicates a node that mediates local flow. On an undirected graph it equals one minus the clustering coefficient.",
      r"(Honey, Kotter, Breakspear & Sporns (2007), as implemented in the Brain Connectivity Toolbox; matches `bctpy.flow_coef_bd` exactly.)"),

  rec("Degree, strength and local connectivity",
      "Local Entropy", "local_entropy",
      r"(Local entropy sums $-k \log k$ over a node's neighbours.)",
      r"(LE(v) = -\sum_{u \in N(v)} k_u \ln k_u)",
      r"(`mode`)",
      "Always non-positive; a lower (more negative) value indicates a larger, denser neighbourhood. Isolates score 0.",
      r"(Nie, Guo, Zhao & Lu (2016), as printed by the Zoo and by Omar & Plapper's 2021 survey; the article is closed access.)"),

  rec("Degree, strength and local connectivity",
      "Weighted h-index", "weighted_h_index",
      "The weighted h-index takes the h-index over topological link weights, each neighbour's weight repeated by its degree.",
      r"(h^w_v = H\big(\{k_v k_u \text{ repeated } k_u \text{ times} : u \in N(v)\}\big))",
      r"(`mode`)",
      "A high value indicates a node with many well-connected neighbours. Input edge weights play no role.",
      r"(Gao, Yu, Li, Shen & Gao (2019), eq. 3. Matches an independent implementation on 200 random graphs.)"),

  rec("Degree, strength and local connectivity",
      "Redundancy", "redundancy",
      "Redundancy is the mean degree of a node's neighbours inside its ego network.",
      r"(r(v) = \frac{2 t_v}{k_v} = k_v - \text{effective size}(v))",
      r"(—)",
      "A high value indicates neighbours that are connected to each other, so fewer structural holes.",
      r"(Burt (1992); Borgatti (1997). Reproduces Borgatti's worked example and equals degree minus effective size.)"),

  ## ---- Family 2: Distance and closeness ----
  rec("Distance and closeness",
      "Closeness Centrality", "closeness",
      "Closeness centrality summarises how short a node's paths are to other reachable nodes.",
      r"(C_C(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(`mode`)",
      "A high value indicates short graph distances to other nodes. In disconnected graphs, harmonic centrality may be easier to interpret.",
      r"(Equivalent to `igraph::closeness()` under matching `mode` and weight settings.)"),

  rec("Distance and closeness",
      "Incloseness Centrality", "incloseness",
      "Incloseness computes closeness over incoming directed paths.",
      r"(C_C^{\mathrm{in}}(v) = \frac{1}{\sum_{u \ne v} d(u, v)})",
      r"(—)",
      "A high value indicates that other nodes can reach the focal node through short directed paths.",
      r"(Equivalent to `igraph::closeness(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outcloseness Centrality", "outcloseness",
      "Outcloseness computes closeness over outgoing directed paths.",
      r"(C_C^{\mathrm{out}}(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(—)",
      "A high value indicates that the focal node can reach other nodes through short directed paths.",
      r"(Equivalent to `igraph::closeness(mode = "out")`.)"),

  rec("Distance and closeness",
      "Harmonic Centrality", "harmonic",
      "Harmonic centrality sums reciprocal shortest-path distances. Unreachable nodes contribute zero.",
      r"(C_H(v) = \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(`mode`)",
      "A high value indicates broad reach through short paths while handling disconnected components more gracefully than classical closeness.",
      r"(Equivalent to `igraph::harmonic_centrality()` under matching settings.)"),

  rec("Distance and closeness",
      "Inharmonic Centrality", "inharmonic",
      "Inharmonic centrality computes harmonic centrality over incoming directed paths.",
      r"(C_H^{\mathrm{in}}(v) = \sum_{u \ne v} \frac{1}{d(u, v)})",
      r"(—)",
      "A high value indicates that the node is reachable from many others through short directed paths.",
      r"(Equivalent to `igraph::harmonic_centrality(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outharmonic Centrality", "outharmonic",
      "Outharmonic centrality computes harmonic centrality over outgoing directed paths.",
      r"(C_H^{\mathrm{out}}(v) = \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(—)",
      "A high value indicates that many nodes can be reached from the focal node through short directed paths.",
      r"(Equivalent to `igraph::harmonic_centrality(mode = "out")`.)"),

  rec("Distance and closeness",
      "Residual Closeness Centrality", "residual_closeness",
      "Residual closeness sums $1 / 2^d$ over shortest-path distances (the focal node contributes $1$).",
      r"(C_R(v) = \sum_{u \in V} 2^{-d(v, u)})",
      r"(`mode`)",
      "A high value indicates many close reachable nodes with rapid distance decay.",
      r"(Validated against `centiserve::closeness.residual()`.)"),

  rec("Distance and closeness",
      "Dangalchev Closeness Centrality", "dangalchev",
      "Dangalchev closeness is the residual-closeness distance-decay measure.",
      r"(C_D(v) = \sum_{u \in V} 2^{-d(v, u)})",
      r"(`mode`)",
      "A high value indicates short-distance reach with distant nodes down-weighted.",
      r"(Implemented as the residual closeness equivalent used in `cograph`.)"),

  rec("Distance and closeness",
      "Generalized Closeness Centrality", "generalized_closeness",
      r"(Generalized closeness sums $\\alpha^d$, where $d$ is the shortest-path distance.)",
      r"(C_G(v) = \sum_{u \in V} \alpha^{\,d(v, u)}, \quad \alpha = 0.5)",
      r"(`mode`, `decay_parameter`)",
      "A high value indicates reach under the chosen distance-decay parameter.",
      r"(Corresponds to generalized distance-decay closeness formulations.)"),

  rec("Distance and closeness",
      "Harary Centrality", "harary",
      "Harary centrality sums inverse squared shortest-path distances.",
      r"(C_{\mathrm{Har}}(v) = \sum_{u \ne v} \frac{1}{d(v, u)^2})",
      r"(`mode`)",
      "A high value indicates many nearby reachable nodes, with distant nodes strongly down-weighted.",
      r"(Based on the Harary distance family.)"),

  rec("Distance and closeness",
      "Average Distance Centrality", "average_distance",
      "Average distance centrality summarises mean shortest-path distance from a node (the focal node's $d = 0$ term is included; the centiserve convention divides by $n + 1$).",
      r"(\bar{d}(v) = \frac{\sum_{u \in V} d(v, u)}{n + 1})",
      r"(`mode`)",
      "Lower values indicate shorter average graph distance. The direction of interpretation should be checked because it is a distance quantity.",
      r"(Validated against the corresponding `centiserve` average-distance measure.)"),

  rec("Distance and closeness",
      "Barycenter Centrality", "barycenter",
      "Barycenter centrality is the inverse of the sum of shortest-path distances.",
      r"(C_{\mathrm{Bary}}(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(`mode`)",
      "A high value indicates a small total distance to other reachable nodes.",
      r"(Validated against `centiserve::barycenter()`.)"),

  rec("Distance and closeness",
      "Wiener Centrality", "wiener",
      "Wiener centrality records total shortest-path distance from a node (unreachable pairs contribute zero).",
      r"(W(v) = \sum_{u \ne v} d(v, u))",
      r"(`mode`)",
      "Lower values indicate shorter total distance. It is better read as distance burden than influence.",
      r"(Based on the Wiener index distance formulation.)"),

  rec("Distance and closeness",
      "Lin Centrality", "lin",
      "Lin centrality combines reachable nodes and total distance to those nodes.",
      r"(C_{\mathrm{Lin}}(v) = \frac{|R(v)|^2}{\sum_{u \in R(v)} d(v, u)}, \quad R(v) = \{ u \ne v : d(v,u) < \infty \})",
      r"(`mode`)",
      "A high value indicates many reachable nodes through relatively short paths.",
      r"(Validated against `centiserve::lincent()`.)"),

  rec("Distance and closeness",
      "Decay Centrality", "decay",
      "Decay centrality sums reach discounted by distance (the focal node contributes $1$).",
      r"(C_{\delta}(v) = \sum_{u \in V} \delta^{\,d(v, u)}, \quad \delta = 0.5)",
      r"(`mode`, `decay_parameter`)",
      "A high value indicates access to many nodes, especially nearby nodes. The value depends on the decay parameter.",
      r"(Validated against `centiserve::decay()`.)"),

  rec("Distance and closeness",
      "Radiality Centrality", "radiality",
      "Radiality compares node distances to the graph diameter.",
      r"(\mathrm{Rad}(v) = \frac{\sum_{u \ne v} \bigl( \Delta + 1 - d(v, u) \bigr)}{n - 1})",
      r"(`mode`)",
      "A high value indicates short distances to others relative to overall graph diameter.",
      r"(Validated against `centiserve::radiality()`.)"),

  rec("Distance and closeness",
      "Gil-Schmidt Centrality", "gilschmidt",
      "Gil-Schmidt centrality sums reciprocal distances and normalises by graph size.",
      r"(C_{GS}(v) = \frac{1}{n - 1} \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(`mode`)",
      "A high value indicates broad reciprocal-distance access to the network.",
      r"(Validated against `sna` Gil-Schmidt style centrality.)"),

  rec("Distance and closeness",
      "Integration Centrality", "integration",
      "Integration centrality is a distance-based measure of how integrated a node is within the graph.",
      r"(\mathrm{Int}(v) = \sum_{u \ne v} \left( 1 - \frac{d(v, u) - 1}{d_{\max}} \right), \quad d(v,u) = d_{\max} + 1 \text{ if unreachable})",
      r"(`mode`)",
      "A high value indicates broad distance-based access to the network.",
      r"(Implemented as a native distance-based centrality in `cograph`.)"),

  rec("Distance and closeness",
      "Eccentricity Centrality", "eccentricity",
      "Eccentricity is the maximum shortest-path distance from a node to any reachable node.",
      r"(\varepsilon(v) = \max_{u \in V} d(v, u))",
      r"(`mode`)",
      "Lower eccentricity generally indicates smaller worst-case distance. A high value means at least one reachable node is far away.",
      r"(Equivalent to `igraph::eccentricity()`.)"),

  rec("Distance and closeness",
      "Ineccentricity Centrality", "ineccentricity",
      "Ineccentricity computes eccentricity over incoming directed paths.",
      r"(\varepsilon^{\mathrm{in}}(v) = \max_{u \in V} d(u, v))",
      r"(—)",
      "It summarises the largest directed distance from other nodes into the focal node.",
      r"(Equivalent to `igraph::eccentricity(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outeccentricity Centrality", "outeccentricity",
      "Outeccentricity computes eccentricity over outgoing directed paths.",
      r"(\varepsilon^{\mathrm{out}}(v) = \max_{u \in V} d(v, u))",
      r"(—)",
      "It summarises the largest directed distance from the focal node to reachable others.",
      r"(Equivalent to `igraph::eccentricity(mode = "out")`.)"),

  rec("Distance and closeness",
      "Closeness Vitality", "closeness_vitality",
      r"(Closeness vitality measures how total network distance changes when a node is removed, using the Wiener index $W(G) = \\sum_{s, t} d(s, t)$.)",
      r"(\mathrm{CV}(v) = W(G) - W(G \setminus v))",
      r"(`mode`)",
      "A high value indicates that removing the node substantially changes shortest-path structure.",
      r"(Corresponds to NetworkX closeness vitality conventions.)"),

  rec("Distance and closeness",
      "Entropy Centrality", "entropy",
      "Entropy centrality measures the change in graph entropy associated with a node, from the distribution of finite shortest-path distances after the node is removed.",
      r"(H(v) = -\sum_{w} Y_w \log_2 Y_w, \quad Y_w = \frac{|\{ x : d(w, x) < \infty \}|}{\sum_{w'} |\{ x : d(w', x) < \infty \}|})",
      r"(`mode`)",
      "A high value indicates strong contribution under the graph entropy definition being used.",
      r"(Validated against `centiserve::entropy()`.)"),

  rec("Distance and closeness",
      "Centroid Centrality", "centroid",
      "Centroid centrality compares distance dominance between pairs of nodes.",
      r"(f(v, u) = \gamma(v, u) - \gamma(u, v), \quad \gamma(v, u) = |\{ w : d(v, w) < d(u, w) \}|, \quad C_{\mathrm{cen}}(v) = \min_{u \ne v} f(v, u))",
      r"(`mode`)",
      "A high value indicates a favourable position in pairwise distance comparisons.",
      r"(Implemented natively because some reference implementations have known edge-case issues.)"),

  rec("Distance and closeness",
      "Distance Entropy", "distance_entropy",
      "Distance entropy is the normalised Shannon entropy of a node's hop-distance profile, so it summarises the spread of distances where closeness summarises their mean.",
      r"(h(v) = -\frac{1}{\log(M_v - m_v + 1)} \sum_{k = m_v}^{M_v} p_k \log p_k, \quad p_k = \frac{n_k(v)}{R_v})",
      r"(`mode`)",
      "A high value (up to 1) indicates reach spread evenly across many network layers; 0 means every reachable node sits at the same distance. Hop counts only; weights are ignored.",
      r"(Stella & De Domenico (2018). The normaliser uses $M_v - m_v + 1$ distance values so the index is bounded by 1; the printed formula divides by $\log(M_v - m_v)$, which is undefined for two distinct distances.)"),

  rec("Distance and closeness",
      "Local Dimension", "local_dimension",
      "Local dimension is the growth exponent of the ball around a node: how fast the number of nodes within $r$ hops grows with $r$.",
      r"(D_v = \frac{d \ln B_v(r)}{d \ln r}, \quad B_v(r) = 1 + |\{u : d(v, u) \le r\}|, \; r = 1, \ldots, d_{\max}(v))",
      r"(`mode`)",
      r"(A low value indicates a node that reaches most of the network within a few hops, so lower is more influential. With a single radius the discretised derivative $r\, n_v(r) / B_v(r)$ is reported.)",
      r"(Pu et al. (2014). Reproduces the worked example of Wen & Deng (2019), 0.9231 for ring sizes 4, 5, 4, 4.)"),

  rec("Distance and closeness",
      "Local Information Dimensionality", "local_information_dimension",
      "Local information dimensionality replaces the ball count of local dimension by its Shannon information and grows the box only to half the node's eccentricity.",
      r"(D^I_v = -\frac{d I_v(l)}{d \ln l}, \quad I_v(l) = -p_v(l) \ln p_v(l), \; p_v(l) = \frac{B_v(l)}{n}, \; l = 1, \ldots, \lceil d_{\max}(v) / 2 \rceil)",
      r"(`mode`)",
      r"(A high value indicates a more influential node. With a single box size the discretised derivative $l (1 + \ln p_v(l))\, n_v(l) / n$ is reported.)",
      r"(Wen & Deng (2020), formula verified against hand-computed path and star values.)"),

  rec("Distance and closeness",
      "Access Information", "access_information",
      "Access information is the mean number of bits a map-less walker needs to reach every other node along shortest paths.",
      r"(A_i = \frac{1}{N} \sum_j S(i \to j), \quad S(i \to j) = -\log_2 \sum_{p(i, j)} \frac{1}{k_i} \prod_{l \in p,\, l \ne i, j} \frac{1}{k_l - 1})",
      r"(—)",
      "A low value indicates a node that reaches the network with few decisions. Hubs score high, because a walker leaving a hub has many links to choose from.",
      r"(Rosvall et al. (2005); Sneppen et al. (2005). Matches enumeration of all shortest paths and the papers' star and bipartite examples.)"),

  rec("Distance and closeness",
      "Hide Information", "hide_information",
      "Hide information is the mean number of bits the rest of the network needs to locate a node.",
      r"(H_i = \frac{1}{N} \sum_j S(j \to i))",
      r"(—)",
      "A high value indicates a hidden, peripheral node; hubs have low hide information.",
      r"(Rosvall et al. (2005); Sneppen et al. (2005). Matches enumeration of all shortest paths.)"),

  rec("Distance and closeness",
      "Local Dimension, Fixed Radius", "local_dimension_fixed",
      "The Silva-Costa local dimension is the discretised growth exponent of the ball around a node at one chosen radius.",
      r"(D_v(r) = \frac{r\, n_v(r)}{B_v(r)})",
      r"(`mode`, `ld_radius`)",
      "A structural descriptor rather than a ranking: higher means the neighbourhood is still growing fast at that radius. Nodes with eccentricity below the radius score 0.",
      r"(Silva & Costa (2013), eq. 4, at a fixed radius (default 2). Reproduces the paper's path-graph values.)"),

  rec("Distance and closeness",
      "Fuzzy Local Dimension", "fuzzy_local_dimension",
      "Fuzzy local dimension replaces the ball count by a Gaussian-weighted average and takes its log-log slope.",
      r"(N_v(r) = \frac{\sum_{d_{vu} \le r} e^{-d_{vu}^2 / r^2}}{|\{u : d_{vu} \le r\}|}, \quad FLD(v) = \frac{d \log N_v(r)}{d \log r})",
      r"(`mode`)",
      "A high value indicates a more influential node (the opposite orientation to the rest of the dimension family).",
      r"(Wen & Jiang (2019). Reproduces the paper's Table 1 (Krackhardt kite) and its karate-club top ten in order.)"),

  rec("Distance and closeness",
      "Local Volume Dimension", "local_volume_dimension",
      "Local volume dimension is the log-log slope of the total degree inside the ball around a node.",
      r"(V_v(l) = \sum_{d_{vu} \le l} k_u, \quad LVD(v) = \frac{d \ln V_v(l)}{d \ln l})",
      r"(`mode`)",
      "A low value indicates a more important node. The source article is closed access; the definition follows the authors' later preprint.",
      r"(Li & Deng (2021). No published per-node values exist; matches an independent implementation.)"),

  rec("Distance and closeness",
      "Heatmap Centrality", "heatmap",
      "Heatmap centrality is a node's farness minus the mean farness of its neighbours.",
      r"(C_{HM}(v) = f(v) - \frac{1}{k_v} \sum_{u \in N(v)} f(u))",
      r"(`mode`)",
      "A low (more negative) value indicates a more central node. Isolates are undefined.",
      r"(Duron (2020). Reproduces every value and the ranking of the paper's Table 1.)"),

  rec("Distance and closeness",
      "Geodesic k-path", "geodesic_kpath",
      "Geodesic k-path centrality counts the shortest paths of length at most $k$ that start at a node, with multiplicity.",
      r"(C_k(v) = \sum_{0 < d(v, u) \le k} \sigma(v, u))",
      r"(`mode`, `kpath_k`)",
      "A high value indicates many short geodesics leaving the node. Counting nodes instead of paths gives m-reach, which is what `centiserve::geokpath` computes.",
      r"(Borgatti & Everett (2006), p. 469. Matches full shortest-path enumeration.)"),

  rec("Distance and closeness",
      "k-path Census", "kpath",
      "The k-path census counts the simple paths of length at most $k$ that a node lies on, endpoints included.",
      r"(C_{kP}(v) = |\{\, P : |P| \le k,\; v \in P \,\}|)",
      r"(`mode`, `kpath_len`)",
      "A high value indicates a node embedded in many short walks, not only in shortest ones. Length 1 alone reproduces degree. Enumeration is exhaustive, so cost grows with the branching factor to the power $k$.",
      r"(Sade (1989). Matches the per-vertex counts of `sna::kpath.census()` for $k = 2$ and $k = 3$ on directed and undirected graphs.)"),

  rec("Distance and closeness",
      "Distance-weighted Fragmentation", "fragmentation",
      "Distance-weighted fragmentation asks how much worse the network communicates once a node is deleted.",
      r"(F_d(v) = 1 - \frac{\sum_{i \ne j \ne v} 1 / d_{ij}^{\,G - v}}{(n-1)(n-2)})",
      r"(`mode`)",
      "A high value indicates a node whose removal fragments the network or stretches its distances. A node inside a clique scores near 0.",
      r"(Borgatti (2006), eq. 4. Matches `keyplayer::fragment()` on unweighted graphs. Held back from `type = \"all\"`: it re-solves all-pairs shortest paths once per node.)"),

  rec("Distance and closeness",
      "Geodesic Power Closeness", "delta_closeness",
      "Geodesic power closeness raises every distance to a negative power, so one exponent moves the measure between a local and a global reading.",
      r"(c_\delta(i) = \frac{1}{n-1} \sum_{j \ne i} d_{ij}^{-\delta})",
      r"(`mode`, `closeness_delta`)",
      r"(A high value indicates a node close to many others. The exponent spans the family: $\delta = 1$ is harmonic centrality over $n-1$, $\delta = 2$ is the inverse-square sum, a large $\delta$ approaches degree, and $\delta = 0$ counts the reachable set. Unreachable nodes contribute nothing but stay in the denominator.)",
      r"(Agneessens, Borgatti & Everett (2017), eq. 2. Reproduces `harmonic` and `harary` exactly at $\delta$ = 1 and 2.)"),

  ## ---- Family 3: Shortest-path brokerage and flow ----
  rec("Shortest-path brokerage and flow",
      "Betweenness Centrality", "betweenness",
      "Betweenness centrality measures how often a node lies on shortest paths between other pairs of nodes.",
      r"(C_B(v) = \sum_{s \ne v \ne t} \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(—)",
      "A high value is consistent with a bridge or brokerage position under the shortest-path model. It is not direct evidence of intentional mediation.",
      r"(Equivalent to `igraph::betweenness()` under matching directedness, weights, and normalization conventions.)"),

  rec("Shortest-path brokerage and flow",
      "Stress Centrality", "stress",
      "Stress centrality counts shortest paths passing through a node without fractional normalization across tied paths.",
      r"(C_S(v) = \sum_{s \ne v \ne t} \sigma_{st}(v))",
      r"(—)",
      "A high value indicates that many shortest paths include the node.",
      r"(Validated against `sna::stresscent()`.)"),

  rec("Shortest-path brokerage and flow",
      "Load Centrality", "load",
      "Load centrality distributes shortest-path load across alternative shortest routes: at each branch point a unit packet is split evenly among next hops on shortest paths.",
      r"(C_L(v) = \sum_{s \ne v \ne t} \mathrm{load}_{st}(v))",
      r"(—)",
      "A high value indicates that a node carries a large share of geodesic routing load.",
      r"(Validated against `sna::loadcent()`.)"),

  rec("Shortest-path brokerage and flow",
      "Length-scaled Betweenness", "length_scaled_betweenness",
      "Length-scaled betweenness counts the same brokered pairs as betweenness but weights each pair by the reciprocal of its distance.",
      r"(C_{LS}(v) = \sum_{s \ne v \ne t} \frac{1}{d(s,t)} \cdot \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(—)",
      "A high value indicates brokerage between pairs that were already close, which ordinary betweenness treats the same as brokerage across the graph.",
      r"(Borgatti & Everett (2006); Brandes (2008), Algorithm 5. Matches a brute-force enumeration of weighted geodesic pairs on directed and undirected graphs.)"),

  rec("Shortest-path brokerage and flow",
      "Distance-decayed Betweenness", "delta_betweenness",
      "Distance-decayed betweenness discounts each brokered pair by a power of its distance, so the exponent tunes how local the measure is.",
      r"(C_\delta(v) = \sum_{s \ne v \ne t} (d(s,t) - 1)^{-\delta} \cdot \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(`betweenness_delta`)",
      r"(A high value indicates brokerage concentrated among nearby pairs. At $\delta = 0$ the measure is ordinary betweenness. Adjacent pairs have no intermediary, so the singularity at $d = 1$ never arises.)",
      r"(Agneessens, Borgatti & Everett (2017). Matches brute force at three exponents and reproduces betweenness exactly at zero.)"),

  rec("Shortest-path brokerage and flow",
      "Ego Betweenness", "ego_betweenness",
      "Ego betweenness is betweenness computed inside a node's own ego network rather than across the whole graph.",
      r"(C_{EB}(v) = \sum_{i < j \in N(v),\; A_{ij} = 0} \frac{1}{(A^2)_{ij}})",
      r"(—)",
      "A high value indicates a node that brokers among its own neighbours, which is what an egocentric survey can measure. A node with fewer than two neighbours scores 0. It is close to Burt's effective size but is not a function of it.",
      r"(Everett & Borgatti (2005). Matches the paper's $A^2(1-A)$ shortcut and ordinary betweenness on the induced ego subgraph.)"),

  rec("Shortest-path brokerage and flow",
      "Bottleneck Centrality", "bottleneck",
      "Bottleneck centrality counts cases where a node is critical in shortest-path tree structures.",
      r"(\mathrm{BN}(v) = \sum_{s \in V} p_s(v), \quad p_s(v) = 1 \text{ if } v \text{ carries} > \tfrac{n}{4} \text{ of the shortest-path tree } T_s)",
      r"(`mode`)",
      "A high value indicates frequent bottleneck position in local shortest-path trees.",
      r"(Validated against `centiserve::bottleneck()`.)"),

  rec("Shortest-path brokerage and flow",
      "Bridging Centrality", "bridging",
      "Bridging centrality combines betweenness with a bridging coefficient.",
      r"(\mathrm{Br}(v) = C_B(v) \cdot \beta(v), \quad \beta(v) = \frac{1/k_v}{\sum_{u \in N(v)} 1/k_u})",
      r"(—)",
      "A high value indicates a possible bridge position between locally distinct areas.",
      r"(Based on bridging centrality formulations by Hwang and colleagues.)"),

  rec("Shortest-path brokerage and flow",
      "Local Bridging Centrality", "local_bridging",
      "Local bridging centrality measures bridge-like position using local neighbourhood information.",
      r"(\mathrm{LBr}(v) = \frac{1}{k_v} \cdot \beta(v), \quad \beta(v) = \frac{1/k_v}{\sum_{u \in N(v)} 1/k_u})",
      r"(—)",
      "A high value indicates that the node connects neighbours that are not strongly connected through local alternatives.",
      r"(Based on local bridging coefficient formulations.)"),

  rec("Shortest-path brokerage and flow",
      "Percolation Centrality", "percolation",
      "Percolation centrality weights shortest-path brokerage by node states in a percolation process.",
      r"(\mathrm{PC}(v) = \frac{1}{n - 2} \sum_{s \ne v \ne t} \frac{\sigma_{st}(v)}{\sigma_{st}} \cdot \frac{x_s}{\sum_{i \ne v} x_i})",
      r"(`states`)",
      "A high value indicates state-dependent path importance under the supplied state vector $x$.",
      r"(Based on Piraveenan, Prokopenko, and Hossain's percolation centrality; equivalent to betweenness-like behavior when states are equal.)"),

  rec("Shortest-path brokerage and flow",
      "Flow Betweenness Centrality", "flow_betweenness",
      "Flow betweenness measures brokerage using maximum flow rather than only shortest paths.",
      r"(C_{FB}(v) = \sum_{s \ne v \ne t} f_{st}(v), \quad f_{st}(v) = \text{flow through } v \text{ in a max } s\text{-}t \text{ flow})",
      r"(—)",
      "A high value indicates importance for potential flow capacity between other nodes under the graph model.",
      r"(Validated against `sna::flowbet()`.)"),

  rec("Shortest-path brokerage and flow",
      "Current-Flow Betweenness Centrality", "current_flow_betweenness",
      "Current-flow betweenness measures how much electrical current between node pairs passes through a node.",
      r"(C_{CFB}(v) = \frac{1}{(n - 1)(n - 2)} \sum_{s \ne t} \tau_{st}(v), \quad \tau_{st}(v) = \text{current through } v)",
      r"(—)",
      "A high value indicates an intermediary position under an all-path current-flow model.",
      r"(Corresponds to NetworkX current-flow betweenness centrality.)"),

  rec("Shortest-path brokerage and flow",
      "Current-Flow Closeness Centrality", "current_flow_closeness",
      "Current-flow closeness uses electrical-network (effective-resistance) distances rather than only shortest paths.",
      r"(C_{CFC}(v) = \frac{n - 1}{\sum_{u \ne v} R_{vu}}, \quad R_{vu} = \text{effective resistance between } v \text{ and } u)",
      r"(—)",
      "A high value indicates closeness under an all-path flow model. It generally requires connected graphs.",
      r"(Corresponds to NetworkX current-flow closeness centrality.)"),

  rec("Shortest-path brokerage and flow",
      "Entropy Variation, Betweenness", "entropy_variation_betweenness",
      "Entropy variation of the betweenness distribution: the drop in its Shannon entropy when the node is removed.",
      r"(EnV_b(i) = I_b(G) - I_b(G - i))",
      r"(—)",
      "A high value indicates a node whose removal concentrates shortest-path traffic on fewer nodes. Betweenness is recomputed per removal.",
      r"(Ai (2017). Matches the author's R code path and the paper's Table 2 betweenness quantiles.)",
      via_measures = TRUE),

  ## ---- Family 4: Spectral, walk and influence ----
  rec("Spectral, walk and influence",
      "Eigenvector Centrality", "eigenvector",
      "Eigenvector centrality gives high scores to nodes connected to other high-scored nodes.",
      r"(A\,\mathbf{x} = \lambda_{\max}\,\mathbf{x}, \quad C_E(v) = x_v)",
      r"(—)",
      "A high value indicates embeddedness in a central neighbourhood. It should not be interpreted as influence unless the relation supports that interpretation.",
      r"(Equivalent to `igraph::eigen_centrality()`.)"),

  rec("Spectral, walk and influence",
      "PageRank Centrality", "pagerank",
      "PageRank is a damped random-walk centrality. Nodes score highly when a random walker reaches them often.",
      r"(\mathrm{PR}(v) = \frac{1 - \alpha}{n} + \alpha \sum_{u \,:\, u \to v} \frac{\mathrm{PR}(u)}{k_u^{\mathrm{out}}}, \quad \alpha = 0.85)",
      r"(`damping`, `personalized`)",
      "A high value indicates random-walk prominence under the chosen damping, direction, and weight conventions.",
      r"(Equivalent to `igraph::page_rank()` under matching parameters; original method by Page, Brin, Motwani, and Winograd.)"),

  rec("Spectral, walk and influence",
      "Authority Centrality", "authority",
      "Authority centrality is part of HITS. Authorities are nodes pointed to by good hubs.",
      r"(\mathbf{a} = A^{\top} \mathbf{h}, \quad \mathbf{h} = A\,\mathbf{a} \;\Rightarrow\; \mathbf{a} = \text{principal eigenvector of } A^{\top} A)",
      r"(—)",
      "A high value indicates incoming support from nodes that point to good authorities.",
      r"(Equivalent to `igraph::authority_score()`; based on Kleinberg's HITS algorithm.)"),

  rec("Spectral, walk and influence",
      "Hub Centrality", "hub",
      "Hub centrality is the HITS counterpart to authority. Hubs point to good authorities.",
      r"(\mathbf{h} = \text{principal eigenvector of } A\,A^{\top})",
      r"(—)",
      "A high value indicates outgoing ties to high-authority nodes.",
      r"(Equivalent to `igraph::hub_score()`; based on Kleinberg's HITS algorithm.)"),

  rec("Spectral, walk and influence",
      "SALSA Centrality", "salsa",
      "SALSA is a stochastic link-analysis method related to HITS for directed graphs.",
      r"(\mathbf{a} = \text{principal eigenvector of } A_c^{\top} A_r, \quad A_r, A_c = \text{row- and column-normalised } A)",
      r"(—)",
      "A high value indicates directed authority under the SALSA random-walk model.",
      r"(Validated against `centiserve::salsa()` where applicable.)"),

  rec("Spectral, walk and influence",
      "LeaderRank Centrality", "leaderrank",
      "LeaderRank is a PageRank-like directed ranking method that adds a ground node $g$ linked both ways to every node; the stationary random-walk mass on $g$ is then redistributed equally.",
      r"(\mathbf{s}^{*} = \text{stationary distribution of the walk on } G \cup \{g\}, \quad C(v) = s^{*}_v + \tfrac{1}{n} s^{*}_g)",
      r"(—)",
      "A high value indicates directed prestige under the LeaderRank model.",
      r"(Validated against `centiserve::leaderrank()` where applicable.)"),

  rec("Spectral, walk and influence",
      "Alpha Centrality", "alpha",
      "Alpha centrality is an eigenvector-like measure that includes exogenous input.",
      r"(\mathbf{x} = (I - \alpha A^{\top})^{-1} \mathbf{e})",
      r"(`mode`)",
      "A high value indicates recursive prominence under the chosen attenuation and exogenous assumptions.",
      r"(Equivalent to `igraph::alpha_centrality()` under matching parameters.)"),

  rec("Spectral, walk and influence",
      "Bonacich Power Centrality", "power",
      r"(Bonacich power centrality scores nodes using the centrality of their neighbours and a parameter $\\beta$ controlling dependence.)",
      r"(\mathbf{c}(\alpha, \beta) = \alpha (I - \beta A)^{-1} A\,\mathbf{1})",
      r"(`mode`)",
      "A high value indicates a favourable recursive position under the selected Bonacich parameterization.",
      r"(Equivalent to `igraph::power_centrality()` under matching parameters.)"),

  rec("Spectral, walk and influence",
      "Katz Centrality", "katz",
      "Katz centrality counts walks from all nodes to a focal node, attenuating longer walks.",
      r"(\mathbf{x} = (I - \alpha A^{\top})^{-1} \mathbf{1}, \quad \alpha = 0.1)",
      r"(`katz_alpha`)",
      "A high value indicates that many short and longer walks reach the node. The attenuation parameter must be valid for the graph.",
      r"(Validated against `igraph::alpha_centrality(exo = 1)` and NetworkX Katz centrality conventions.)"),

  rec("Spectral, walk and influence",
      "Hubbell Centrality", "hubbell",
      "Hubbell centrality is an input-output centrality where status is recursively reinforced through ties.",
      r"(\mathbf{x} = (I - w W)^{-1} \mathbf{1}, \quad w = 0.5,\; W = \text{weighted adjacency})",
      r"(`hubbell_weight`)",
      "A high value indicates recursive prominence under the chosen weight factor. Some parameter settings are not solvable.",
      r"(Based on Hubbell's input-output centrality.)"),

  rec("Spectral, walk and influence",
      "Subgraph Centrality", "subgraph",
      "Subgraph centrality measures participation in closed walks, with shorter closed walks weighted more strongly.",
      r"(\mathrm{SC}(v) = \sum_{k=0}^{\infty} \frac{(A^k)_{vv}}{k!} = (e^{A})_{vv})",
      r"(—)",
      "A high value indicates embeddedness in many closed walk structures.",
      r"(Equivalent to `igraph::subgraph_centrality()`; based on Estrada's formulation.)"),

  rec("Spectral, walk and influence",
      "Laplacian Centrality", "laplacian",
      "Laplacian centrality measures a node's contribution to the graph's Laplacian energy.",
      r"(C_L(v) = \frac{E_L(G) - E_L(G \setminus v)}{E_L(G)}, \quad E_L(G) = \sum_i \mu_i^2 \;\; (\mu_i = \text{Laplacian eigenvalues}))",
      r"(—)",
      "A high value indicates a large local structural contribution under the Laplacian energy definition.",
      r"(Matches NetworkX and `centiserve::laplacian()` conventions.)"),

  rec("Spectral, walk and influence",
      "Communicability Centrality", "communicability",
      "Communicability centrality uses the matrix exponential to summarise walk-based communication potential.",
      r"(C_{\mathrm{Comm}}(v) = \sum_{u \in V} (e^{A})_{vu})",
      r"(—)",
      "A high value indicates many walk-based routes to other nodes, with shorter walks weighted more strongly.",
      r"(Based on Estrada communicability.)"),

  rec("Spectral, walk and influence",
      "Communicability Betweenness Centrality", "communicability_betweenness",
      "Communicability betweenness measures walk-based communicability between other pairs through a node.",
      r"(C_{CB}(v) = \frac{1}{(n-1)(n-2)} \sum_{s \ne t \ne v} \frac{G_{st} - G_{st}^{(v)}}{G_{st}}, \quad G = e^{A})",
      r"(—)",
      "A high value indicates walk-based intermediary position, not limited to shortest paths. $G^{(v)}$ is computed with $v$ removed.",
      r"(Based on Estrada, Higham, and Hatano's communicability betweenness.)"),

  rec("Spectral, walk and influence",
      "Random Walk Centrality", "random_walk",
      "Random walk centrality uses expected random-walk access times rather than shortest-path distances.",
      r"(C_{RW}(v) = \frac{1}{\sum_{u \ne v} \tilde{m}_{vu}}, \quad \tilde{m}_{vu} = \tfrac{1}{2}\bigl( m_{vu} + m_{uv} \bigr))",
      r"(—)",
      "A high value indicates that the node is reached efficiently under a random-walk process. $m_{uv}$ is the mean first-passage time.",
      r"(Corresponds to random-walk centrality based on mean first-passage or resistance-distance formulations.)"),

  rec("Spectral, walk and influence",
      "Markov Centrality", "markov",
      "Markov centrality is based on mean first-passage times in a Markov process on the graph.",
      r"(C_{\mathrm{Mk}}(v) = \frac{1}{\frac{1}{n} \sum_{u} m_{uv}}, \quad m_{uv} = \text{mean first-passage time } u \to v)",
      r"(—)",
      "A high value indicates that the node is reached quickly on average under the Markov process.",
      r"(Validated against `centiserve::markovcent()`.)"),

  rec("Spectral, walk and influence",
      "Second-Order Centrality", "second_order",
      "Second-order centrality summarises variability in random-walk return times.",
      r"(\mathrm{SO}(v) = \operatorname{sd}_{u}\bigl( m_{uv} \bigr))",
      r"(via `centrality(measures = ...)`)",
      "The statistic describes random-walk regularity rather than direct connectivity (lower is more central).",
      r"(Rank behavior is checked against NetworkX second-order centrality in package tests.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Information Centrality", "information",
      "Information centrality measures centrality through resistance-distance or information-flow ideas (Stephenson and Zelen).",
      r"(C_I(v) = \left( C_{vv} + \frac{T - 2 R_v}{n} \right)^{-1}, \quad C = (D - A + J)^{-1},\; T = \operatorname{tr} C,\; R_v = \textstyle\sum_j C_{vj})",
      r"(—)",
      "A high value indicates a central position under the information-flow model.",
      r"(Based on Stephenson and Zelen's information centrality.)"),

  rec("Spectral, walk and influence",
      "Nonbacktracking Centrality", "nonbacktracking",
      "Nonbacktracking centrality scores nodes using walks that do not immediately return along the edge just traversed (the Hashimoto matrix $B$).",
      r"(B_{(i \to j),\,(k \to l)} = \delta_{jk}\,(1 - \delta_{il}), \quad C(v) \propto \text{aggregated leading eigenvector of } B)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates walk-based prominence after reducing immediate backtracking inflation.",
      r"(Validated against NetworkX-style nonbacktracking behavior in package tests.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Diffusion Centrality", "diffusion",
      "Diffusion centrality estimates reach through a diffusion process over the graph.",
      r"(\mathbf{DC} = \sum_{t=1}^{T} (\lambda A)^{t}\,\mathbf{1}, \quad \lambda = 1)",
      r"(`mode`, `lambda`)",
      "A high value indicates a structurally favourable position for spreading under the selected diffusion model.",
      r"(Validated against `centiserve::diffusion()` where applicable and TNA-style diffusion conventions for transition networks.)"),

  rec("Spectral, walk and influence",
      "Infection Centrality", "infection",
      "Infection centrality estimates spreading potential through infection-style self-avoiding walks with attenuation.",
      r"(\mathrm{Inf}(v) = \sum_{d=1}^{L} \beta^{\,d+1} (1 - \mu)^{d}\, w_d(v), \quad \beta = 0.8,\; \mu = 0,\; L = 6)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates a favourable position under the assumed infection process, not observed contagion. $w_d(v)$ counts length-$d$ self-avoiding walks from $v$.",
      r"(Implemented according to infection centrality formulas used in the network centrality literature.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Edge Percolated Component", "epc",
      "The edge percolated component averages the size of the component a node ends up in when edges survive at random.",
      r"(\mathrm{EPC}(v) = \frac{1}{R\,n} \sum_{r=1}^{R} |C_r(v)|, \quad \Pr(\text{edge survives}) = 1 - t)",
      r"(`epc_threshold`, `epc_runs`, `epc_seed`)",
      "A high value indicates a node that stays connected to a large share of the network under random link failure. The value is a Monte Carlo estimate; set `epc_seed` to make it reproducible.",
      r"(Lin et al. (2008), the cytoHubba EPC. Recovers the exact bond-percolation mean on small graphs. cytoHubba and `centiserve::epc()` divide by $n$ alone, so their number is `epc_runs` times this one. Held back from `type = \"all\"` because it is both costly and stochastic.)"),

  rec("Spectral, walk and influence",
      "VoteRank Centrality", "voterank",
      "VoteRank is an iterative voting algorithm for ranking spreader candidates: each round the highest-voted node is selected, its voting ability is zeroed, and its neighbours' voting abilities are reduced.",
      r"()",
      r"(—)",
      "A high value indicates early selection by the VoteRank rule. It is a heuristic model result, not observed spread.",
      r"(Corresponds to NetworkX VoteRank behavior.)"),

  rec("Spectral, walk and influence",
      "Expected Influence 1-Step", "expected_influence_1",
      "Expected influence 1-step sums signed edge weights adjacent to a node.",
      r"(\mathrm{EI}_1(v) = \sum_{u \in V} W_{vu}, \quad W = \text{signed weight matrix})",
      r"(`mode`)",
      "A high positive value indicates strong positive immediate signed connectivity. This is mainly meaningful for signed networks.",
      r"(Based on Robinaugh, Millner, and McNally's expected influence measure.)"),

  rec("Spectral, walk and influence",
      "Expected Influence 2-Step", "expected_influence_2",
      "Expected influence 2-step extends signed influence to one- and two-step paths.",
      r"(\mathrm{EI}_2(v) = \mathrm{EI}_1(v) + \sum_{u \in V} W_{vu}\,\mathrm{EI}_1(u))",
      r"(`mode`)",
      "A high positive value indicates positive signed connectivity through direct and indirect paths. Interpretation requires a signed network.",
      r"(Based on Robinaugh, Millner, and McNally's expected influence measure.)"),

  rec("Spectral, walk and influence",
      "Spanning Tree Centrality", "spanning_tree",
      "Spanning tree centrality summarises a node's contribution across spanning-tree structures via the Laplacian pseudoinverse $L^{+}$.",
      r"(\mathrm{ST}(v) = \frac{1}{L^{+}_{vv}}, \quad L^{+} = \text{Moore-Penrose pseudoinverse of } L)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates structural participation across many tree-like ways of connecting the graph.",
      r"(Based on matrix-tree theorem centrality formulations.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 1", "shapley_game1",
      "Shapley value of the node in the coalition game whose worth is the number of nodes a coalition covers within one hop.",
      r"(SV_1(v) = \sum_{u \in \{v\} \cup N(v)} \frac{1}{1 + k_u})",
      r"(—)",
      "A high value indicates a node whose presence adds much one-hop coverage to a typical coalition. Values sum to $n$.",
      r"(Michalak et al. (2013), game 1. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 2", "shapley_game2",
      "Shapley value in the game where a node is covered once at least $k$ coalition members are adjacent to it.",
      r"(SV_2(v) = \min\!\left(1, \frac{k}{1 + k_v}\right) + \sum_{u \in N(v)} \max\!\left(0, \frac{k_u - k + 1}{k_u (1 + k_u)}\right))",
      r"(`shapley_k`)",
      "A high value indicates a node that helps push many neighbours over the $k$-neighbour threshold. With $k = 1$ this is game 1.",
      r"(Michalak et al. (2013), game 2. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 3", "shapley_game3",
      "Shapley value in the game where a coalition covers every node within a hop cutoff.",
      r"(SV_3(v) = \sum_{u \in \{v\} \cup N_d(v)} \frac{1}{1 + |N_d(u)|}, \quad N_d(u) = \{w : d(u, w) \le d_{cut}\})",
      r"(`shapley_cutoff`)",
      "A high value indicates a node that reaches many otherwise hard-to-reach nodes within the cutoff. With cutoff 1 this is game 1.",
      r"(Michalak et al. (2013), game 3. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Rumor Centrality", "rumor",
      "Rumor centrality counts the spreading orders that could have started at a node; on a general graph it is evaluated on the node's breadth-first tree.",
      r"(\log R(v) = \log N! - \sum_{u} \log T^v_u)",
      r"(—)",
      "A high value indicates a plausible origin of a spread, typically a node near the centre. Returned on the log scale.",
      r"(Shah & Zaman (2011), eq. 24. Reproduces the paper's Fig. 5 values and brute-force spreading-order counts on trees.)"),

  rec("Spectral, walk and influence",
      "DegreeDiscountIC", "degree_discount",
      "DegreeDiscountIC is the greedy seed-selection order under degree discounting for the independent-cascade model.",
      r"(dd_v = d_v - 2 t_v - (d_v - t_v)\, t_v\, p)",
      r"(`discount_p`)",
      "A high score indicates an early selection: the first node selected scores 1, the last $1/n$. Ties follow node order.",
      r"(Chen, Wang & Yang (2009), Algorithm 4. Selection order matches an independent implementation on random graphs and the karate club.)"),

  rec("Spectral, walk and influence",
      "SingleDiscount", "single_discount",
      "SingleDiscount is the greedy seed-selection order where each neighbour of a new seed discounts its degree by one.",
      r"(dd_v = d_v - t_v)",
      r"(—)",
      "A high score indicates an early selection. Equivalent to repeatedly removing the highest-degree node.",
      r"(Chen, Wang & Yang (2009). Selection order matches an independent implementation and the node-removal formulation.)"),

  rec("Spectral, walk and influence",
      "NCVoteRank", "ncvoterank",
      "NCVoteRank is VoteRank with each voter's ability weighted by its normalised neighbourhood coreness, and two-hop weakening after each election.",
      r"(s_u = \sum_{v \in N(u)} va_v \,[\theta + (1 - \theta)\, nc_v])",
      r"(`ncvote_theta`)",
      r"(A high score indicates an early election. With $\theta = 1$ and no two-hop weakening this is VoteRank.)",
      r"(Kumar & Panda (2020), as restated by the Centrality Zoo and three later papers; the original article was not obtainable. VoteRank limit reproduces `networkx.voterank`.)"),

  rec("Spectral, walk and influence",
      "WVoteRank", "wvoterank",
      "WVoteRank is VoteRank for weighted graphs: votes are weighted by edge weight and the score takes a square root.",
      r"(s_v = \sqrt{k_v \sum_{u \in N(v)} va_u w_{vu}})",
      r"(—)",
      r"(A high score indicates an early election. Neighbours of an elected node lose $1/\langle w \rangle$, with $\langle w \rangle$ the average strength.)",
      r"(Sun, Chen, He & Ch'ng (2019). Reproduces all sixty numbers of the paper's Figure 1.)"),

  rec("Spectral, walk and influence",
      "EnRenew", "enrenew",
      "EnRenew elects the node whose neighbours supply the most entropy, then renews the entropies around it.",
      r"(E_v = \sum_{u \in N(v)} -p_{uv} \ln p_{uv}, \quad p_{uv} = \frac{k_u}{\sum_{l \in N(v)} k_l})",
      r"(`enrenew_depth`)",
      r"(A high score indicates an early election. Terms within the renewal radius are scaled by $1 - 1/(2^{d-1} \ln\langle k \rangle)$.)",
      r"(Guo, Yang, Guo, Pan & Chen (2020), eq. 1 and Algorithm 1. Reproduces the paper's Figure 1.)"),

  rec("Spectral, walk and influence",
      "VoteRank++", "voterank_plus",
      "VoteRank++ starts abilities from degree, splits votes in proportion to neighbour degree, and suppresses abilities multiplicatively after each election.",
      r"(s_v = \sqrt{k_v \sum_{u \in N(v)} va_u\, w_{u \to v}}, \quad va_v^{(0)} = \ln(1 + k_v / k_{\max}))",
      r"(`voterank_lambda`)",
      r"(A high score indicates an early election. Abilities are multiplied by $\lambda$ one step away and $\sqrt{\lambda}$ two steps away.)",
      r"(Liu, Li, Fang & Yao (2021). Matches the authors' released code exactly; the article is closed access.)"),

  rec("Spectral, walk and influence",
      "Node Contraction", "node_contraction",
      "Node contraction importance measures how much the network's cohesion rises when a node and its neighbours are merged into one.",
      r"(IMC(v) = 1 - \frac{\partial(G)}{\partial(G_v)}, \quad \partial(G) = \frac{1}{N \bar{L}})",
      r"(—)",
      "A high value indicates a node whose contraction shortens paths most. Reproduces the paper's Table 1 and the path-graph closed forms.",
      r"(Tan, Wu & Deng (2006), as restated by Wang et al. (2011), eqs. 1-3.)"),

  rec("Spectral, walk and influence",
      "Improved Node Contraction", "node_contraction_improved",
      "Improved node contraction adds the contraction scores of a node's edges, computed on the line graph.",
      r"(IIMC(v) = \alpha\, IMC(v) + \beta \sum_{e \ni v} IMC_{L(G)}(e), \quad \alpha / \beta = 5)",
      r"(`contraction_rho`)",
      "A high value indicates a node that is important both itself and through its edges. Not bounded by 1.",
      r"(Wang et al. (2011), eq. 4. Reproduces the paper's Table 1 with $\alpha + \beta = 1$.)"),

  rec("Spectral, walk and influence",
      "Two-Way Random Walk Betweenness", "two_way_rw",
      "Two-way random walk betweenness counts, over all node pairs, how often a node lies on the most likely two-step out-and-back route.",
      r"(T_{ij}[t, k] = P_{itj} P_{jki}, \quad P_{itj} = \frac{w_{it} w_{tj}}{d_i d_j})",
      r"(—)",
      "A high count indicates a node on many dominant two-way routes; nodes on none score 0. Cost grows as $n^4$.",
      r"(Curado, Rodriguez, Tortosa & Vicent (2022). Reproduces the paper's toy example exactly.)"),

  ## ---- Family 5: Neighbourhood structure and cohesion ----
  rec("Neighbourhood structure and cohesion",
      "Transitivity Centrality", "transitivity",
      "Transitivity measures local clustering: whether a node's neighbours are connected to each other.",
      r"(c(v) = \frac{2\, t_v}{k_v (k_v - 1)}, \quad t_v = \text{number of triangles through } v)",
      r"(`transitivity_type`, `isolates`)",
      "A high value indicates locally closed neighbourhoods. This can represent cohesion or redundancy, depending on the relation.",
      r"(Equivalent to `igraph::transitivity()` for standard types; `cograph` also supports weighted variants.)"),

  rec("Neighbourhood structure and cohesion",
      "Constraint Centrality", "constraint",
      "Constraint measures how redundant a node's contacts are, following Burt's structural holes framework.",
      r"(C(v) = \sum_{u \in N(v)} \left( p_{vu} + \sum_{q \ne v, u} p_{vq}\, p_{qu} \right)^2, \quad p_{vu} = \text{proportional tie strength})",
      r"(—)",
      "A high value indicates a locally constrained ego network. Lower constraint may indicate structural holes, depending on theory and relation type.",
      r"(Equivalent to `igraph::constraint()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Effective Size Centrality", "effective_size",
      "Effective size estimates the number of nonredundant contacts in a node's ego network (Burt).",
      r"(\mathrm{ES}(v) = k_v - \frac{1}{k_v} \sum_{u \in N(v)} |N(v) \cap N(u)|)",
      r"(—)",
      "A high value indicates relatively nonoverlapping contacts.",
      r"(Validated against `influenceR::effective_size()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Topological Coefficient Centrality", "topological_coefficient",
      "Topological coefficient centrality measures shared-neighbour overlap.",
      r"(T(v) = \frac{\operatorname{avg}_{u}\, J(v, u)}{k_v}, \quad J(v, u) = \text{number of neighbours shared by } v \text{ and } u)",
      r"(—)",
      "A high value indicates neighbourhood overlap or topological similarity.",
      r"(Validated against `centiserve::topocoefficient()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Diversity Centrality", "diversity",
      "Diversity centrality measures entropy in the distribution of edge weights around a node.",
      r"(\mathrm{Div}(v) = \frac{-\sum_{u \in N(v)} p_{vu} \log_2 p_{vu}}{\log_2 k_v}, \quad p_{vu} = \frac{w_{vu}}{\sum_{u'} w_{vu'}})",
      r"(—)",
      "A high value indicates that weighted ties are relatively evenly distributed rather than concentrated.",
      r"(Validated against `igraph::diversity()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Cross-Clique Centrality", "cross_clique",
      "Cross-clique centrality counts how many cliques contain a node.",
      r"(X(v) = |\{\, Q \in \mathcal{Q}(G) : v \in Q \,\}|, \quad \mathcal{Q}(G) = \text{set of cliques})",
      r"(—)",
      "A high value indicates participation in many fully connected local groups.",
      r"(Validated against `centiserve::crossclique()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Coreness Centrality", "coreness",
      "Coreness assigns nodes to k-core shells.",
      r"(C_{\mathrm{core}}(v) = \max \{\, k : v \in (k\text{-core of } G) \,\})",
      r"(`mode`)",
      "A high value indicates membership in a dense core. It does not imply brokerage or short paths to all nodes.",
      r"(Equivalent to `igraph::coreness()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Onion Centrality", "onion",
      "Onion centrality assigns nodes to layers from onion decomposition, a fine-grained extension of k-core decomposition.",
      r"(\text{layer}(v) = \text{iteration index at which } v \text{ is peeled by the onion decomposition})",
      r"(via `centrality(measures = ...)`)",
      "A high layer indicates that the node remains until later stages of the peeling process.",
      r"(Validated against NetworkX onion layer behavior in package tests.)",
      via_measures = TRUE),

  rec("Neighbourhood structure and cohesion",
      "K-Reach Centrality", "kreach",
      "K-reach centrality counts nodes reachable within path length $k$.",
      r"(C_{kR}(v) = |\{\, u : 0 < d(v, u) \le k \,\}|, \quad k = 3)",
      r"(`mode`, `k`)",
      "A high value indicates broad reach within a fixed local radius. Results depend on the chosen $k$.",
      r"(Validated against k-path reach conventions.)"),

  rec("Neighbourhood structure and cohesion",
      "s-shell Index", "s_shell",
      "The s-shell index peels the graph by node strength built from asymmetric topological link weights, generalising k-shell.",
      r"(w_{ij} = 1 + (k_i\, k^{out}_j)^a, \quad s_i = \sum_{j \in N(i)} w_{ij})",
      r"(`s_shell_a`)",
      "A high shell index indicates a node deep in the strength-based core. With $a = 0$ the shells are the dense ranks of k-core.",
      r"(Liu, Tang, Do & Hui (2017). Each peeled shell equals the complement of the maximal subgraph with strength above the threshold; $a = 0$ reproduces k-core ranks.)"),

  rec("Neighbourhood structure and cohesion",
      "Weighted k-shell", "weighted_kshell",
      "The weighted k-shell peels the graph by a generalised degree that mixes degree and strength.",
      r"(k'_v = \big(k_v^{\alpha} s_v^{\beta}\big)^{1 / (\alpha + \beta)})",
      r"(`wks_alpha`, `wks_beta`)",
      "A high shell index indicates a node deep in the weighted core. Unit weights give the k-core number.",
      r"(Garas, Schweitzer & Havlin (2012), eq. 1 with their weight normalisation. Reproduces the paper's Figure 1 example and Table 2 core size.)"),

  rec("Neighbourhood structure and cohesion",
      "Renewed Coreness", "renewed_coreness",
      "Renewed coreness is the k-core number after removing links that lead nowhere new.",
      r"(D_{ij} = \frac{|N(j) \setminus N[i]| + |N(i) \setminus N[j]|}{2}, \quad \text{keep } D_{ij} \ge 2)",
      r"(`renewed_threshold`)",
      "A high value indicates a core node whose links reach beyond shared neighbourhoods. A clique with no outside links scores 0.",
      r"(Liu, Tang, Zhou & Do (2015). Reproduces the paper's Figure 1 and all twelve percentages of its Table S1.)"),

  rec("Neighbourhood structure and cohesion",
      "s-core Index", "s_core",
      "The s-core index is the weighted k-core: the largest strength threshold whose core still contains the node.",
      r"(s\text{-core}(s) = \text{maximal } H \subseteq G \text{ with } s_i^H \ge s \;\; \forall i \in H)",
      r"(—)",
      "A high value indicates a node deep in the strength-based core. Unit weights give the k-core number exactly.",
      r"(Eidsaa & Almaas (2013). Matches `igraph::coreness()` on unweighted graphs and a brute-force reading of the definition on weighted ones; `brainGraph::s_core()` reports the peeling round instead.)"),

  rec("Neighbourhood structure and cohesion",
      "Local Efficiency", "local_efficiency",
      "Local efficiency is how well a node's neighbours still communicate once the node itself is gone, using only the links among them.",
      r"(E_{loc}(v) = \frac{1}{k_v (k_v - 1)} \sum_{i \ne j \in N(v)} \frac{1}{d_{ij}^{\,G_v}})",
      r"(`mode`)",
      "A high value indicates a fault-tolerant neighbourhood; a node whose neighbours are mutually unconnected scores 0. Note that `igraph::local_efficiency()` measures those distances through the rest of the network instead, so it reports larger values.",
      r"(Latora & Marchiori (2001). Matches `brainGraph::efficiency(type = \"local\")` and the networkx induced-subgraph form.)"),

  ## ---- Family 6: Directed prestige and hierarchy ----
  rec("Directed prestige and hierarchy",
      "Prestige Domain Centrality", "prestige_domain",
      "Prestige domain centrality counts how many nodes can reach a focal node in a directed graph.",
      r"(P(v) = |\{\, u \ne v : u \rightsquigarrow v \,\}|)",
      r"(—)",
      "A high value indicates a large incoming reach domain.",
      r"(Based on Wasserman-Faust prestige concepts and `sna`-style prestige measures.)"),

  rec("Directed prestige and hierarchy",
      "Prestige Domain Proximity Centrality", "prestige_domain_proximity",
      "Prestige domain proximity measures how close nodes in the prestige domain are to the focal node.",
      r"(C(v) = \frac{|R^{-}(v)|^2}{(n - 1) \sum_{u \in R^{-}(v)} d(u, v)}, \quad R^{-}(v) = \{ u \ne v : u \rightsquigarrow v \})",
      r"(—)",
      "A high value indicates that many predecessors can reach the node through short directed paths.",
      r"(Based on Wasserman-Faust prestige proximity concepts.)"),

  rec("Directed prestige and hierarchy",
      "Local Reaching Centrality", "reaching_local",
      "Local reaching centrality measures how much of the network is reachable from a node through directed paths.",
      r"(\mathrm{LRC}(v) = \frac{|\{\, u : v \rightsquigarrow u \,\}|}{n - 1})",
      r"(`mode`)",
      "A high value indicates broad directed reach from the node.",
      r"(Matches `networkx.local_reaching_centrality` in package equivalence tests.)"),

  rec("Directed prestige and hierarchy",
      "Pairwise Disconnectivity Centrality", "pairwisedis",
      "Pairwise disconnectivity measures how directed reachability between pairs changes when a node is removed.",
      r"(\mathrm{Dis}(v) = \frac{P(G) - P(G \setminus v)}{P(G)}, \quad P(G) = |\{ (s, t) : s \rightsquigarrow t \}|)",
      r"(—)",
      "A high value indicates structural importance for preserving directed reachability.",
      r"(Validated against reference implementations in package tests.)"),

  rec("Directed prestige and hierarchy",
      "Trophic Level Centrality", "trophic_level",
      "Trophic level estimates hierarchical position in a directed flow network.",
      r"((I - W)\,\mathbf{s} = \mathbf{1}, \quad W_{ji} = \frac{a_{ij}}{k_j^{\mathrm{in}}}, \quad \text{basal nodes have level } 1)",
      r"(via `centrality(measures = ...)`)",
      "A higher value indicates a higher position in the inferred directed hierarchy. This is appropriate only for flow-like relations.",
      r"(Checked against NetworkX trophic-level behavior in package tests.)",
      via_measures = TRUE),

  ## ---- Family 7: Community and group-based ----
  rec("Community and group-based",
      "Participation Coefficient", "participation",
      "Participation coefficient measures how evenly a node's ties are distributed across communities.",
      r"(P(v) = 1 - \sum_{m} \left( \frac{k_v^{(m)}}{k_v} \right)^2, \quad k_v^{(m)} = \text{ties from } v \text{ to module } m)",
      r"(`membership`, `mode`)",
      "A high value indicates ties spread across multiple communities. It requires a meaningful membership vector.",
      r"(Validated against `brainGraph` participation coefficient conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Within-Module Z Centrality", "within_module_z",
      "Within-module z centrality standardises a node's within-community degree against other nodes in the same community.",
      r"(z(v) = \frac{k_v^{(m_v)} - \mu_{m_v}}{\sigma_{m_v}}, \quad m_v = \text{community of } v)",
      r"(`membership`, `mode`)",
      "A high value indicates unusually high within-module connectivity.",
      r"(Validated against `brainGraph` within-module z-score conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Gateway Centrality", "gateway",
      "Gateway centrality measures inter-community brokerage weighted by centrality of communities or nodes involved.",
      r"(g(v) = 1 - \frac{1}{k_v^2} \sum_{s} k_{vs}^2\, \gamma_{vs}^2, \quad k_{vs} = \text{ties from } v \text{ to module } s)",
      r"(`membership`, `mode`)",
      "A high value indicates a structurally prominent position between communities.",
      r"(Validated against `brainGraph::gateway()` conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Coordinator Centrality", "brokerage_coordinator",
      r"(Coordinator brokerage occurs when a node mediates between two nodes in its own group. It counts open directed two-paths $a \\to v \\to c$ (with no direct $a \\to c$).)",
      r"(\mathrm{Coord}(v) = |\{\, a \to v \to c : g(a) = g(v) = g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates within-group mediation under the supplied membership vector.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Itinerant Centrality", "brokerage_itinerant",
      "Itinerant brokerage occurs when a node mediates between two nodes in another group.",
      r"(\mathrm{Itin}(v) = |\{\, a \to v \to c : g(a) = g(c) \ne g(v) \,\}|)",
      r"(`membership`)",
      "A high value indicates brokerage among members outside the node's own group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Representative Centrality", "brokerage_representative",
      "Representative brokerage occurs when a node mediates from its own group to another group.",
      r"(\mathrm{Rep}(v) = |\{\, a \to v \to c : g(a) = g(v) \ne g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates outward brokerage from the node's group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Gatekeeper Centrality", "brokerage_gatekeeper",
      "Gatekeeper brokerage occurs when a node mediates from another group into its own group.",
      r"(\mathrm{Gate}(v) = |\{\, a \to v \to c : g(a) \ne g(v) = g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates inward brokerage into the node's group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Liaison Centrality", "brokerage_liaison",
      "Liaison brokerage occurs when a node mediates between two groups, neither of which is its own.",
      r"(\mathrm{Liai}(v) = |\{\, a \to v \to c : g(a),\, g(v),\, g(c) \text{ all distinct} \,\}|)",
      r"(`membership`)",
      "A high value indicates between-group brokerage outside the node's own group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Modularity Vitality", "modularity_vitality",
      "Modularity vitality is the drop in Newman modularity when a node is deleted and the remaining nodes keep their communities.",
      r"(V_Q(v) = Q(G, C) - Q(G - v,\; C \setminus \{v\}))",
      r"(`membership`)",
      "A positive value indicates a community hub; a negative value indicates a bridge whose removal sharpens the partition. Weighted and directed graphs use the corresponding modularity.",
      r"(Magelinski, Bartulovic & Carley (2021). Matches brute-force `igraph::modularity()` after vertex deletion on random directed, undirected and weighted graphs.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community Hub-Bridge", "community_hub_bridge",
      "Community hub-bridge scores nodes that are hubs inside their community and bridges between communities.",
      r"(CHB(v) = |C_v|\, k^{intra}_v + NNC_v\, k^{inter}_v)",
      r"(`membership`, `mode`)",
      "A high value indicates a node with many intra-community links in a large community and links into several other communities.",
      r"(Ghalmane, El Hassouni & Cherifi (2019), eqs. 2-4, raw form. Matches an independent implementation on random partitions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community-Based Centrality", "community_based",
      "Community-based centrality weights every link of a node by the size of the community it lands in.",
      r"(CbC(v) = \frac{1}{N} \sum_w d_{vw} S_w)",
      r"(`membership`, `mode`)",
      "A high value indicates many links into large communities. No tuning parameter.",
      r"(Zhao, Wang, Zhang & Zhu (2015), eq. 1. Reproduces the paper's Table 1 and Table 1 of Tulu et al. (2018).)",
      grp = TRUE),

  rec("Community and group-based",
      "Comm Centrality", "comm_centrality",
      "Comm centrality combines a node's scaled intra-community degree with the square of its scaled inter-community degree, weighted by how outward-looking its community is.",
      r"(CC(v) = (1 + \mu_C)\,\frac{k^{in}_v}{\max_{u \in C} k^{in}_u} R + (1 - \mu_C)\left(\frac{k^{out}_v}{\max_{u \in C} k^{out}_u} R\right)^2)",
      r"(`membership`, `mode`, `comm_r`)",
      "A high value indicates a node that is central within its community and well linked outside it. $R$ defaults to the community's maximum intra-degree.",
      r"(Gupta, Singh & Cherifi (2016), eqs. 3-4. Matches an independent implementation; the paper prints no per-node values.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community-Based Mediator", "community_mediator",
      "The community-based mediator score is the entropy of a node's link distribution over communities times its share of total degree.",
      r"(CbM(v) = H_v \frac{d_v}{\sum_u d_u}, \quad H_v = -\sum_k p_{vk} \log_2 p_{vk})",
      r"(`membership`, `mode`)",
      "A high value indicates a well-connected node whose links are spread over several communities; nodes linked to one community score 0.",
      r"(Tulu, Hou & Younas (2018), eqs. 9-12. Base-2 entropy reproduces the paper's Table 1 exactly.)",
      grp = TRUE)
)

family_order <- c(
  "Degree, strength and local connectivity",
  "Distance and closeness",
  "Shortest-path brokerage and flow",
  "Spectral, walk and influence",
  "Neighbourhood structure and cohesion",
  "Directed prestige and hierarchy",
  "Community and group-based"
)

emit_measure <- function(r) {
  cat("\n### ", r$title, " {#cent-", r$key, "}\n\n", sep = "")
  cat(r$concept, "\n\n", sep = "")
  if (nzchar(r$math)) cat("$$\n", r$math, "\n$$\n\n", sep = "")
  cat("**Meaning.** ", r$meaning, "\n\n", sep = "")
  cat("```r\n", r$example, "\n```\n\n", sep = "")
  cat("**Equivalence reference.** ", r$reference, "\n\n", sep = "")
}

emit_family <- function(fam) {
  cat("\n## ", fam, "\n\n", sep = "")
  for (r in records) if (identical(r$family, fam)) emit_measure(r)
}
```

## Catalogue index

```{r index, results = 'asis', echo = FALSE}
cat("<div class=\"cg-fam-index\">\n\n")
for (fam in family_order) {
  cat("**", fam, "**\n\n", sep = "")
  items <- Filter(function(r) identical(r$family, fam), records)
  links <- vapply(items, function(r) sprintf("[%s](#cent-%s)", r$title, r$key),
                  character(1))
  cat(paste(links, collapse = " · "), "\n\n")
}
cat("</div>\n\n")
```

```{r families_1_6, results = 'asis', echo = FALSE}
for (fam in family_order[1:6]) emit_family(fam)
```

The measures below need a **community membership vector**. Build one with
`detect_communities()` (`walktrap` works on the directed `student_interactions`
graph), then pass it as `membership =`:

```{r groups}
comm   <- detect_communities(student_interactions, method = "walktrap")
groups <- setNames(comm$community, comm$node)
centrality_participation(student_interactions, membership = groups)
```

```{r families_7, results = 'asis', echo = FALSE}
emit_family(family_order[7])
```

## Argument catalogue {#argument-catalogue}

All measures are reachable through the single `centrality()` verb. These
arguments control how they are computed. Measure-specific knobs are repeated in
each measure's **Arguments** line.

| Argument | Default | Affects | What it does |
|---|---|---|---|
| `type` | `"basic"` | all | Curated tier of measures: `"basic"`, `"extended"`, or `"all"`. |
| `measures` | `NULL` | all | Character vector of specific measures to compute (overrides `type`). |
| `mode` | `"all"` | directed measures | Traversal direction: `"all"`, `"in"`, or `"out"`. |
| `normalized` | `FALSE` | most | Divide each score by its maximum. |
| `weighted` | `TRUE` | weighted measures | Use edge weights when present. |
| `directed` | `NULL` | all | Force directed/undirected; `NULL` auto-detects. |
| `loops` | `TRUE` | degree, strength | Keep self-loops. |
| `simplify` | `"sum"` | multigraphs | How to combine parallel edges. |
| `cutoff` | `-1` | path-based | Cap path length (`-1` = no cap). |
| `invert_weights` | `NULL` | distance/path | Treat weights as distances vs. strengths. |
| `alpha` | `1` | weight transform | Exponent applied when `invert_weights = TRUE`. |
| `damping` | `0.85` | PageRank | Random-walk damping factor. |
| `personalized` | `NULL` | PageRank | Personalization vector. |
| `transitivity_type` | `"local"` | transitivity | `"local"`, `"global"`, or weighted variants. |
| `isolates` | `"nan"` | transitivity | How isolates are scored. |
| `lambda` | `1` | diffusion | Diffusion scaling factor. |
| `k` | `3` | k-reach | Path-length radius. |
| `states` | `NULL` | percolation | Per-node percolation state vector. |
| `decay_parameter` | `0.5` | decay, generalized closeness | Distance-decay base. |
| `dmnc_epsilon` | `1.7` | DMNC | Density exponent. |
| `katz_alpha` | `0.1` | Katz | Attenuation factor. |
| `hubbell_weight` | `0.5` | Hubbell | Weight factor $w$. |
| `membership` | `NULL` | group-based | Community assignment vector. |
| `digits` | `NULL` | all | Round numeric columns. |
| `sort_by` | `NULL` | all | Order rows by a column name. |
