---
title: "Centrality catalogue"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Centrality catalogue}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{css, echo = FALSE}
.cg-fam-index { line-height: 1.7; }
.cg-fam-index p { margin: 0.15em 0 0.9em 0; }
h3 code { font-size: 0.92em; }
table.cg-argtable td, table.cg-argtable th { padding: 4px 8px; }
```

```{r setup}
library(cograph)
data(student_interactions)
```

A centrality is a **node-level** statistic: it assigns every node a single
number that summarises some aspect of its position in the network — how many
ties it has, how short its paths to others are, how often it sits between other
nodes, or how it participates in the network's global structure. Centralities
describe **nodes**, not edges or whole graphs, and they are the most widely used
way to compare the relative prominence of actors within a network.

`centrality()` offers **`r nrow(list_centralities())` selectable measures**,
spanning degree and strength, distance and closeness,
shortest-path brokerage, spectral and walk-based influence, neighbourhood
cohesion, directed prestige, and community/group-based roles. This catalogue
also describes named variants. Verification evidence varies by measure:
external implementations, published examples, independently evaluated
definitions, or rank comparisons. The reference entry states the evidence;
rank comparison alone does not establish numerical equivalence.

`student_interactions` is a built-in edge-list dataset of observed student
interactions. It can be passed to `centrality()` directly. The single verb
`centrality()` is the recommended entry point: it returns a tidy
one-row-per-node `data.frame` and accepts an argument for every tuning knob
(see the [argument catalogue](#argument-catalogue) below).

```{r}
centrality(student_interactions)
```

Pass `type = "all"` for all ordinary-cost measures, `include = "costly"` to
add costly ones, `measures = c(...)` to pick a subset, `digits =` to round,
and `sort_by =` to order the result.

## How to read this catalogue

Every measure below is documented with four fields:

- **Concept** — what the measure captures, in words.
- **Definition** — the formula, faithful to what `cograph` actually computes
  (verified against the package source, which is occasionally normalised
  differently from a textbook statement).
- **Meaning** — how to read a high (or low) value.
- **Example** and **Equivalence reference** — a runnable call and the external
  implementation it is validated against.

### Notation

Throughout, $G = (V, E)$ is a graph with $n = |V|$ nodes and adjacency matrix
$A = (a_{ij})$; $w_{ij}$ are edge weights, $N(v)$ is the neighbour set of $v$,
$k_v = |N(v)|$ its degree, and $s(v) = \sum_u w_{vu}$ its strength. We write
$d(u, v)$ for the shortest-path distance, $\Delta$ for the graph diameter, and
$\sigma_{st}$ (resp. $\sigma_{st}(v)$) for the number of shortest $s$–$t$ paths
(resp. those passing through $v$). $L = D - A$ is the graph Laplacian and
$\mathbf{1}$ the all-ones vector.

```{r records, echo = FALSE}
rec <- function(family, title, key, concept, math, args, meaning, reference,
                grp = FALSE, via_measures = FALSE) {
  ex <- if (key == "bridging_capital") {
    "centrality_bridging_capital(student_interactions, weighted = FALSE)"
  } else if (via_measures) {
    sprintf('centrality(student_interactions, measures = "%s")', key)
  } else {
    sprintf("centrality_%s(student_interactions%s)", key,
            if (grp) ", membership = groups" else "")
  }
  list(family = family, title = title, key = key, concept = concept,
       math = math, args = args, meaning = meaning, reference = reference,
       example = ex)
}

records <- list(
  rec("Spectral, walk and influence",
      "Trust-PageRank", "trust_pagerank",
      "Replace PageRank's even split of a node's score among its neighbours by a trust-value that mixes how similar the two nodes are with how large the receiver's degree is.",
      r"(TPR_i=\frac{1-\alpha}{n}+\alpha\sum_{j\in N_i}T(i,j)TPR_j,\qquad T(i,j)=(1-k)\frac{s(i,j)}{\sum_{l\in N_j}s(j,l)}+k\frac{d_i}{\sum_{l\in N_j}d_l})",
      "`tpr_alpha`, `tpr_k`, `tpr_decay`, `tpr_tol`, `tpr_max_iter`, `normalized`",
      "PageRank hands a node's score to its neighbours in equal shares, which the source argues is not how information actually moves: a node passes more to the neighbours it trusts, and trust has two parts. The similarity ratio is SimRank, the recursive statement that two nodes are similar when their neighbours are similar; the degree ratio says a neighbour with a large degree is worth more of the message because it can carry it further. Both ratios are normalised over the receiving node's neighbourhood and the similarity is symmetric, so each of them sums to one down a column and so does their blend, whatever the mixing weight k is. The trust matrix is therefore column-stochastic, the iteration is an ordinary damped PageRank with a unique fixed point, and the scores sum to one on a graph with no isolate. That also settles a question the source leaves open: it never fixes an iteration count, and it does not need to, because the count is a convergence tolerance rather than a modelling choice. Both recursions here stop on a relative change below tpr_tol, relative rather than absolute because the similarities on one graph span many orders of magnitude, the mass reaching a line decaying geometrically with its distance from the nearest triangle; a recursion still moving at tpr_max_iter raises a warning rather than returning a quietly unconverged estimate. The similarity recursion runs on the lines of the graph only. The source's algorithm quantifies over connected pairs and its similarity table marks every non-adjacent cell with a dash, so a non-adjacent pair entering the recursion contributes zero rather than the 0.1 that initialises the lines, and that restriction is what makes the recursion usable: the base case s(a, a) = 1 becomes the only term that is not a multiple of another similarity, and it reaches a line exactly through the common neighbours of its endpoints, which is to say through the triangles the line carries. Each row of the linear part then sums to less than one on any line carrying a triangle, so the recursion contracts even at the source's decay constant of one. Pinning the non-adjacent pairs at 0.1 instead reproduces neither of the paper's two published fixtures. The consequence is a degenerate class that is not a corner case: on a component that has lines but no triangle the recursion is homogeneous, its least non-negative fixed point is zero everywhere, and the similarity ratio is a zero over zero. Every path, tree, star, even cycle and complete bipartite graph is in that class, and so is the Petersen graph. cograph returns NA for the whole of such a component, with a classed warning, rather than naming a value: unlike the vanishing denominators of the degree and importance of lines and of the Lhc index, this quotient is not determined by its numerator, since the ratios need only sum to one over the neighbourhood and nothing in the source chooses between the ways of doing that. The obvious fallback, one over the receiver's degree, would silently turn the measure into a degree-ratio PageRank over that whole class while still calling it Trust-PageRank. An isolate is not in the class: it is never a denominator, and it keeps the bare teleport share (1 - alpha)/n, so a graph with isolates has scores summing to less than one. The domain does not move with tpr_k either, k = 1 included, because the similarity ratio is part of the trust-value at every mixing weight. tpr_alpha and tpr_k both default to the source's 0.85, the second chosen there from a Kendall-against-SIR sweep on four networks. tpr_decay defaults to the source's 1, and the source's claim that its value does not affect the results is false for the converged recursion: that holds for a homogeneous recursion, where the constant is an overall scale, but the base case makes this one affine, so the constant enters the resolvent as well, and moving it from 1 to 0.5 moves the similarity ratios of the karate club by up to 0.141. Direction and weights are dropped to the simple undirected skeleton the source defines on; mode, cutoff and weight inversion are ignored, empty graphs return no scores, and normalized = TRUE max-scales the finished vector. Marked costly: two fixed-point recursions over dense n by n matrices, one of them a triple product per sweep.",
      "Sheng, Zhu, Wang, Wang and Hou (2020), Algorithms13(11), 280, DOI10.3390/a13110280, equations (2) and (4) on page5, equations (5) and (6) on page5, equation (7) and Algorithm1 on page7, figure3 and table3 on page6, and table5 on page10. The paper is fully open access and the publisher PDF was read, pages5, 6, 7 and10 visually inspected for the equations, the pseudocode, the annotated figure and both printed tables. THE CENTRALITY ZOO CITES THE WRONG PAPER: its entry 2.381 attributes Trust-PageRank to Sheng et al., Physica A541, 123262, which defines the unrelated global-and-local-structure index of entry 2.149; a reader following that reference lands on a different measure. Both published fixtures reproduce. Table3's seven similarities each round to their printed two decimals, and its S_v column is the sum of the paper's own rounded cells rather than the rounded sum, a convention that node5 alone separates. Table5's karate club top ten reproduces in order at all ten positions, the eighth and ninth separated by a real gap of about 3e-05, and its kite top ten reproduces up to three exact ties forced by the kite's own automorphism group. The one printed value that does not reproduce is table4's karate mean degree, printed 4.5888 where 156/34 is 4.588235; it is recorded as a slip rather than rounded away. Verified in addition against three independent references: a pure-Python route holding the graph as sets and iterating both recursions by explicit loops with no matrix anywhere, a NumPy route that solves both fixed points as linear systems rather than iterating them, and exact rational arithmetic end to end with a hand-written Gauss-Jordan, whose zero test on the similarity denominator settles the domain question without any tolerance. The restatement in Hajarathaiah, Enduri, Anamalamudi, Subba Reddy and Tokala (2022), Entropy24(5), 704, DOI10.3390/e24050704, was also read; its own figure2 contradicts its own equation on which ratio carries the weight k, and the annotated figure3 of the original settles the orientation. No author or third-party code exists, so no author-parity claim is made, and the paper's SIR spreading experiments were not reproduced."),
  rec("Shortest-path brokerage and flow",
      "Randomized shortest paths (RSP) betweenness", "rsp_betweenness",
      "Count the visits a node gets from walks that are neither strictly shortest nor purely random, and slide between the two with one parameter.",
      r"(bet_i=\sum_{s=1}^{n}\sum_{t=1}^{n}\Bigl(\frac{z_{si}}{z_{st}}-\frac{z_{ti}}{z_{tt}}\Bigr)z_{it},\qquad \mathbf{Z}=(\mathbf{I}-\mathbf{W})^{-1},\quad \mathbf{W}=(\mathbf{D}^{-1}\mathbf{A})\circ\exp(-\beta\mathbf{C}))",
      "`rsp_beta`, `rsp_cost`, `normalized`",
      "One knob between shortest-path betweenness and a random walk. The randomized shortest paths framework puts a Boltzmann distribution over the absorbing walks from s to t: at a high inverse temperature the distribution concentrates on the cheapest walks and the score approaches shortest-path likelihood betweenness, while at a low one it relaxes to the unbiased random walk, where the source states that an undirected network's score becomes proportional to degree. A node scores the expected number of visits it receives, summed over every ordered source-target pair, so the source contributes to its own score while the target never does, which is the paper's definition and not an oversight. The published closed form of equation (15) divides by every entry of the fundamental matrix and is therefore defined only on a strongly connected graph, which is what Algorithm 1 demands; cograph evaluates it masked by reachability, applying the source's own rule below equation (9) that a pair with no s-to-t path contributes zero. That mask reproduces equation (15) to machine precision whenever the graph is strongly connected and extends it consistently when it is not, and it must reach both halves of the term because both come from the same expected-visit expression. NetworkToolbox::rspbc masks only the reciprocal and leaves the other half counting every source, so the two agree exactly on strongly connected input and part company on a disconnected graph. The consequence is that scores are component-local: two disjoint triangles score exactly what one triangle scores, and adding a disconnected component or an isolate leaves every existing score untouched. A node with no outgoing arc has an undefined D inverse; cograph writes that row of the reference transition matrix as zero, which is the paper's own killed random walk read at a node where the walker dies at once, and the arithmetic then gives exactly 1 - 1 = 0. An isolate, a singleton and every node of an edgeless graph therefore score a derived zero rather than an imputed one, where NetworkToolbox::rspbc raises an error and current-flow betweenness returns NA. rsp_beta defaults to 0.01, which is not the source's number: the paper fixes no default and treats beta as a modelling choice, and 0.01 is the value NetworkToolbox recommends, adopted so the two implementations are comparable out of the box. It sits near the high-temperature end, so the default reading is close to the random walk; raise it to 1 or beyond to move towards shortest paths, which can reorder the nodes. The domain is beta > 0 and anything outside it is refused. rsp_cost decides how a weight becomes a cost, which the source leaves free: inverse, the default, reads a weight as an affinity and sets C = 1/w, as NetworkToolbox hard-codes; weight reads it as a distance and sets C = w. The two coincide on a binary graph, where both give unit cost per arc. Negative and non-finite weights are refused, Algorithm 1 requiring a non-negative cost matrix. Direction is read from the graph rather than from mode, since the reference transition matrix normalises by out-strength and the fundamental matrix counts directed walks; a reversed input generally scores differently. Loops are dropped and mode, cutoff and weight inversion are ignored. Empty graphs return no scores and normalized = TRUE max-scales the finished vector. Marked costly: one dense n x n inverse, which the source itself calls the computational bottleneck at O(n^3) time and O(n^2) memory.",
      "Kivimaki, Lebichot, Saramaki and Saerens (2016), Scientific Reports6, 19668, DOI10.1038/srep19668, equations (6) and (8) on pages5-6, equations (14) and (15) and Algorithm1 on pages6-7, and the beta to 0+ limit on page9. The paper is fully open access and the publisher PDF was read, pages5, 6, 7 and9 visually inspected for the equations, the pseudocode and the limit claim. The paper prints no table of node scores on a small graph, so there is no published numerical example to reproduce; what is checked against the paper instead is its printed page9 claim that the score becomes proportional to degree as beta approaches zero from above, which holds and does so at first order in beta. Verified against four independent references: equation (15) in float64 NumPy through an explicit inverse with NetworkX reachability, the definitional double sum of equations (8) and (14) accumulated pair by pair with no matrix product at all, the same double sum over a fundamental matrix built as a truncated Neumann series with no inverse or solve anywhere, and equation (15) again in mpmath at 60 decimal digits with mpmath's own inverse. Three hand-derived closed forms are also checked: a single undirected edge scores exactly1 at every beta, a directed n-cycle scores n(n-1)/2 at every beta, and a complete graph matches a Sherman-Morrison derivation. Cross-checked against CRAN NetworkToolbox::rspbc1.4.4 on the strongly connected fixtures after undoing that function's rounding and shifting, which are its own post-processing and are nowhere in the paper. The authors' MATLAB at github.com/ikivimak/RSP-betweenness, named in the paper's Materials section, was not fetched, so no author-code parity claim is made, and the paper's OpenStreetMap and Wikipedia experiments were not reproduced."),
  rec("Neighbourhood structure and cohesion",
      "Degree and importance of lines (DIL)", "dil",
      "Add to a node's degree the share it can claim of the importance of the lines that touch it, where a line matters when its endpoints reach far beyond it and no triangle offers a way round.",
      r"(L_{v_i}=k_i+\sum_{v_j\in\Gamma_i}W_{v_iv_j},\qquad W_{v_iv_j}=I_{e_{ij}}\frac{k_i-1}{k_i+k_j-2},\qquad I_{e_{mn}}=\frac{(k_m-p-1)(k_n-p-1)}{p/2+1})",
      "`normalized`",
      "Degree, corrected for whether a node's lines are worth anything. Degree alone counts every line the same; this measure first asks what each line is worth and then asks how much of that worth belongs to the node at each end. A line is worth a lot when both its endpoints reach far past it, which is the product of the two degrees reduced by the line itself and by the triangles carrying it, and it is worth less when triangles do carry it, because a triangle is a way round. The worth is then split between the two endpoints in proportion to their own degrees, so the busier endpoint claims more of it. The two shares sum to one, which makes the split a genuine conservation: the network's total excess over degree is exactly the total importance of its lines. The number of triangles on a line is the number of common neighbours of its endpoints, and because an endpoint's neighbour list already contains the other endpoint, that count can never exceed either degree minus one. Both factors of the numerator are therefore at least zero, every line's importance is at least zero, and no score ever falls below its node's degree. Equality is the common case rather than the exceptional one: every line of a complete graph is carried by n - 2 triangles, and every line of a star touches a leaf, so both score exactly the degree at every node. The parameter written lambda is p/2 + 1 and not 2p + 1, which matters because the published PDF's text layer renders that stacked fraction wrongly in the original as well as in its later reproduction; the paper's own worked example prints the value 1.5 at one triangle and settles it. The one undefined case is an isolated pair of nodes, where the denominator of the split vanishes because both degrees are one. The source says nothing about it. It resolves rather than refuses, because the same two degrees that make the split indeterminate also make the line's importance exactly zero, and a share of nothing is nothing whichever share it is; the test is taken before the division, so no zero over zero is ever evaluated, and both nodes of an isolated pair score one. Nothing in the construction reaches past a node's second neighbours, so raw scores are component-local and a disjoint component moves nothing: an isolate scores zero, a singleton graph and an edgeless graph score zero everywhere, a disconnected graph needs no special rule, and an empty graph returns no scores. Direction and weights are dropped to the simple undirected skeleton, the authors stating that domain themselves in the opening line of their derivation and every quantity in the three equations being a count; mode, cutoff and weight inversion are ignored, and normalized = TRUE max-scales the finished vector, the source stating no normalization. Not costly: the source calls it local information at O(n<k>^2), and the kernel is one masked matrix product plus elementwise work.",
      "Liu, Xiong, Shi, Shi and Wang (2016), Physica A 452, 209-219, DOI 10.1016/j.physa.2016.02.049, equation (1) with its symbol list on page 210, equations (2) and (3) on page 211, the complexity claim in table 4 on page 218, and the ARPA fixture in table 3 and figure 6 on page 217. The paper is CC-BY-NC-ND open access and the original was read, every equation and every figure from 300 dpi page images rather than from the text layer, which mangles the definition of lambda. Its three published fixtures all reproduce: the two edge importances of figure 1 as exact fractions, the four edge importances and both node scores of figure 2 as exact fractions, and all twenty-one values of the table 3 column for the ARPA network, each matching the paper's own rounding at four decimal places, in the descending order the table prints them. The edge list read off figure 6 is corroborated by the paper's own degree column, which it matches at all twenty-one nodes; the paper's prose calls that network twenty-three lines where its table and its figure both say twenty-six, and the table and the figure are followed. Zoo entry 2.62 and the reproduction in Almasi and Hu (2019), PLoS ONE 14(3), e0205936, agree with the original symbol for symbol, so no divergence is recorded anywhere. Verified in addition against four independent references: exact rational arithmetic over Python sets, a NetworkX route accumulating the equations one incident line at a time, a dense NumPy route, and exact rational arithmetic again with the triangle census by exhaustive enumeration of every node triple. Seven closed forms derived by hand are also checked, for complete graphs, stars, rings, the Petersen graph, paths and complete bipartite graphs. No author or third-party code exists, so no author-parity claim is made, and the paper's network-efficiency experiments were not reproduced."),
  rec("Neighbourhood structure and cohesion",
      "Lhc index", "lhc",
      "Score a node by how much degree, inflated by each contributor's share of the network's triangles, sits within a couple of steps of its neighbours.",
      r"(Lhc(v)=\sum_{w\in\tau(v)}C(w),\qquad C(v)=\sum_{u\in\Phi(v)}\frac{k_u\bigl(1+TP(u)\bigr)}{d^{2}(uv)},\qquad TP(u)=\frac{NTS(u)}{TNTS})",
      "`lhc_radius`, `normalized`",
      "Neighbour information and topological location in one number. The neighbour half is degree; the location half is the share of the network's triangles that sit on a node, on the reasoning that a node carrying many triangles is embedded in a dense part of the graph rather than dangling off it. Both travel: each member of the ball of radius lhc_radius around a node contributes its degree, inflated by its triangle share, discounted by the square of its distance, and the index is that influence summed once more over the node's own neighbours. The two-step construction is what makes it semi-local rather than local, and it is why a node with modest degree but well-embedded neighbours can outscore a locally busy one. The triangle share is normalised by TNTS, the sum over nodes of the triangle counts, which the source states is three times the number of distinct triangles; the share therefore sums to exactly one over the nodes. Entry 2.221 of the Centrality Zoo transcribes both equations correctly but names the denominator the number of triangular structures in the network, which read literally is three times too small and gives 125.45 where the paper gives 100.15 on the Krackhardt kite; cograph follows the paper, which settles the point itself. Both neighbourhoods are open: the focal node is outside its own ball, because a zero distance would divide by zero, and unreachable nodes fall outside the radius so nothing becomes infinite. It follows, though the source does not remark on it, that a node does enter its own score, since it lies at distance one from each of its neighbours. lhc_radius is the source's own parameter, written d there, set to 2 in the paper and swept over eleven real networks in its experiments, which report 2 to 3 as optimal and the correlation as stable beyond 3. At radius 1 the ball collapses to the neighbours; at or above the graph radius the ball has saturated and the score stops moving. A triangle-free graph is a cograph decision the source does not make: every tree, star, path, even cycle and bipartite graph has no triangles at all, so the share is a zero over zero at every node. Because the total vanishes exactly when every numerator does, there is no share to distribute and none is given: the share is written as zero and the index reduces to the pure degree-over-squared-distance sum, which is the neighbour and location half of the hybrid with the triangle half contributing nothing. The test is made before any division, so nothing divides by zero and nothing is returned as an unexplained zero. Raw scores are not component-local, because the triangle total is global: attaching a disconnected component that carries a triangle rescales every share and moves every score, while attaching one with no triangle, an isolate included, changes nothing. An isolate scores zero because it has no neighbours to sum over, and a singleton graph and every node of an edgeless graph score zero for the same reason. Direction, weights, loops and parallel edges are dropped to the simple undirected skeleton the source defines on, since degree is a count, distance a hop count and the triangle count combinatorial; mode, cutoff and weight inversion are ignored, empty graphs return no scores, and normalized = TRUE max-scales the finished vector, the source stating no normalization. The paper prints no worked example and no table of node scores, so there is no published fixture to reproduce; verification rests on independent reference implementations and on hand-derived closed forms for stars, complete graphs, rings and paths.",
      "Wang, Yang, Liu and Ma (2021), PLoS ONE 16(5), e0251208, DOI 10.1371/journal.pone.0251208, equation (1) and its symbol list on page 3, equation (2), the d = 2 statement and Algorithm 1 on page 4, and the d sweep on page 7. The paper is fully open access and the publisher PDF was read."),
  rec("Neighbourhood structure and cohesion",
      "Hybrid characteristic centrality (HCC)", "hcc",
      "Add a node's blended local degree to how late a repeated minimum-degree peel gets round to removing it.",
      r"(HCC(u)=\frac{k^{ex}(u)}{k^{ex}_{\max}}+\frac{pos(u)}{pos_{\max}},\qquad k^{ex}(u)=\delta k(u)+(1-\delta)\!\!\sum_{v\in\phi(u)}\!\!k(v))",
      "`hcc_delta`, `normalized`",
      "Two characteristics on one scale. The extended degree is the node's own degree blended with its neighbours', so a node with few but well-connected neighbours is not written off; the E-shell position index is the round in which a peel that repeatedly removes every remaining node of minimum extended degree gets to this one, so it says how deep in the graph the node sits. Both are divided by their largest value, so each lies in [0, 1] and the raw score lies in [0, 2]. The E-shell decomposition is not a k-shell decomposition, although the Centrality Zoo describes it as a variant of one: there is no outer loop over a shell index and no repeat-until-stable inner loop, so the position indexes run 1 to pos_max with every value attained. On a four-node path the k-shell reading puts all four nodes in one shell, while the E-shell peel takes two rounds. The source's printed step 3 is a typo, and cograph implements the correction the source's own tables require: it prints arg max where the same sentence calls the set 'the set of minimum nodes' and where table 2's column, headed 'Minimum extended degree', increases through 2, 2.5, 3, 4.5, 5, 6. Reading it literally as a maximum peel gives a different measure. A second reading is settled the same way: step 6 recomputes the extended degrees on the residual graph after each removal, but the k^ex and k^ex_max of the score itself are the original-graph values, as the paper's worked line 4.5/11 + 4/6 shows and as its node d confirms, the original 9.5 giving the printed 1.86 where the residual 6 would give 1.55. hcc_delta defaults to the source's 0.5 and is confined to the source's stated [0, 1]; one recovers the classical degree, zero drops the node's own degree entirely, and a value outside the interval is refused rather than extended, because it can make the extended degree negative and then the score divides by a nonpositive maximum. Raw scores are not component-local: k^ex_max and pos_max are single global constants, so adding a disconnected component rescales the two halves independently rather than applying one common factor. An isolate has extended degree zero, the global minimum for every admissible delta, so it always leaves in the first round; on an edgeless graph every extended degree is zero and the first term is 0/0, written as zero, which leaves the E-shell term alone, so every node of an edgeless graph, a singleton included, scores exactly 1. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed. Weights, mode, cutoff and inversion are ignored and a directed input is symmetrised, the source defining no directed case. Empty graphs return no scores; normalized = TRUE max-scales on top of the two divisions the formula already performs. Cost is one dense matrix-vector product per peeling round.",
      "Liu and Zheng (2023), Scientific Reports13, 3197, DOI10.1038/s41598-023-30308-5, equations (3) and (4) and the eight-step E-shell hierarchy decomposition on page3, with the worked example and tables1-3 on page4. The paper is fully open access and the publisher PDF was read, pages2-4 visually inspected and the figure1 edge list transcribed from a 500dpi crop. Eighty-five of the eighty-six values it prints reproduce: all ten classical degrees, all ten extended degrees, all six rows of the decomposition trace, both worked lines, the stated maxima 11 and 6, all ten HCC values and nine of the ten EHCC values. The tenth is an unresolved disagreement, recorded rather than tuned away: table3 prints EHCC(g) = 10.01 where the exact value 661/66 is 10.015151 and rounds to 10.02; that cell is the truncation, but six other printed cells require rounding, so no single convention reproduces all twenty. Verified against four independent references: a NetworkX induced-subgraph rebuild every round with exact rational extended degrees, a repeated-minimum-extraction peel over rational-keyed buckets with local rebucketing, the same peel decided at 60 digits, and the closed neighbourhood as an exact integer matrix product. No author software exists, so no author-parity claim is made, and the paper's SIR spreading results were not reproduced."),
  rec("Neighbourhood structure and cohesion",
      "Extended hybrid characteristic centrality (EHCC)", "ehcc",
      "Collect a node's own hybrid characteristic score together with every neighbour's.",
      r"(EHCC(u)=HCC(u)+\sum_{v\in\phi(u)}HCC(v))",
      "`hcc_delta`, `normalized`",
      "The closed-neighbourhood sum of the hybrid characteristic centrality, the focal node counted once and each neighbour of the open one-order neighbourhood once. It rewards a node whose neighbours are themselves both locally dense and deep in the hierarchy, which a node can be without being either itself; on the source's own figure 1 it lifts node g above node e, which ties with it on HCC. Because HCC lies in [0, 2], EHCC lies in [0, 2(1 + k)], and an isolate scores exactly its own HCC, having nothing to add. Everything recorded for the hybrid characteristic centrality carries over unchanged: the source's arg max / arg min typo, the original-graph reading of the extended degree against the residual-graph peel, the global and therefore not component-local normalisers, the hcc_delta domain [0, 1], the 0/0 of an edgeless graph written as zero, the simple undirected unweighted skeleton, and the ignored weights, mode, cutoff and inversion.",
      "Liu and Zheng (2023), Scientific Reports13, 3197, DOI10.1038/s41598-023-30308-5, equation (5) on page3, with the printed worked line EHCC(a) = HCC(a) + HCC(b) + HCC(e) = 4.15 and table3 on page4. Nine of the ten printed EHCC values reproduce; the tenth, EHCC(g), is printed 10.01 where the exact 661/66 rounds to 10.02, and that disagreement is retained in the batch's published audit. Verified against the same four independent references as HCC, with a fourth EHCC-only route forming the closed neighbourhood as an exact object-dtype matrix product instead of a floating-point one."),
  rec("Neighbourhood structure and cohesion",
      "KED method", "ked",
      "Weight the degree by how evenly a node's neighbours carry its local paths, then by how many second-step paths there are.",
      r"(KED(i)=k_i\bigl(1+H_i\bigr)\exp\!\Bigl(\frac{K_i}{N}\Bigr),\qquad H_i=\frac{\sum_{j\in N(i)}-p_j\log p_j}{\log k_i},\quad p_j=\frac{k_j}{K_i},\quad K_i=\sum_{j\in N(i)}k_j)",
      "`normalized`",
      "Two nodes of the same degree with the same number of second neighbours can still spread very differently: if one neighbour carries almost all the onward paths, the information dies with it. H is the entropy of the neighbours' degree distribution divided by its own maximum, the entropy of the uniform distribution on k_i outcomes, so it lies in [0, 1] and equals one exactly when the neighbour degrees are all equal. That ratio is taken in one base top and bottom, so the logarithm base cancels and is not a convention to choose. The measure takes no parameters: equation (6) is a bare product, and the tunable exponents alpha and beta the Centrality Zoo attributes to Chen et al. appear nowhere in the paper. Two degenerate cases are cograph decisions the source never mentions. A node with one neighbour has zero entropy and a zero normaliser, a 0/0 written as H = 0, which is the value approached from k_i = 2 as one neighbour's share vanishes and the one that gives a single-path node the least diversity; reading it as H = 1 instead would double every leaf's score. An isolate has both sums empty and scores zero, which the degree factor forces anyway. Raw scores are not comparable across graphs of different order, and here that is more than a rescaling: N is the whole graph's vertex count, and exp(K_i/N) shrinks a large neighbour-degree sum more than a small one, so adding a disconnected component can reorder nodes. The source's stated range 1 <= D <= e is not general either; it needs K_i <= N, which holds on its sparse toy networks and fails on dense graphs, where every node of the five-clique has K_i = 16 against N = 5. cograph implements the formula, not the range claim. The Centrality Zoo prints the formula twice wrong, dropping the 1 + from E and dividing by the largest cluster degree instead of by N, which gives 13.5914 and 6.5672 where the paper prints 25.9187 and 19.2212, so no Zoo variant is offered. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed. Weights, mode, cutoff and inversion are ignored, and the source's directed out-degree variant is not implemented, so a directed input is symmetrised. Empty graphs return no scores; normalized = TRUE max-scales. Cost is two matrix-vector products; an exponent past the range of exp(), which needs about 710 vertices on a complete graph, raises an error rather than returning Inf.",
      "Chen, Xiao, Zeng and Zhang (2014), EPL104(6):68006, DOI10.1209/0295-5075/104/68006, equations (1) and (2) page2 and equation (6) page4. The IOP version of record was NOT read; what was read is the author preprint arXiv:1305.7480, with pages2-4 visually inspected and the figure1 graphs transcribed from a 500dpi crop. Both scores the paper prints, f=25.9187 for the red node of panel (a) and f=19.2212 for the red node of panel (b), reproduce to all four printed decimals, as do the figure1 caption's three structural claims. Verified against five independent references: exact rational neighbour probabilities with the entropy accumulated at 60 digits, the same terms in float64 with an exactly rounded sum, a traversal bucketed by distinct neighbour degree, the whole ratio taken in base ten, and the exponential split at the exact integer quotient and remainder. No author software exists, so no author-parity claim is made, and the paper's SIR spreading results were not reproduced."),
  rec("Neighbourhood structure and cohesion",
      "Local neighbor contribution (LNC)", "lnc",
      "Multiply what a node contributes on its own by what its neighbourhood contributes to it.",
      r"(LNC(i)=\underbrace{d_i\bigl(1-1/d_i\bigr)^{d_i-1}}_{ownCon(i)}\cdot\underbrace{d_i^{2}\frac{\sum_{j\in N(i)}d_j}{n-1}}_{neiCon(i)},\qquad 0^0:=1)",
      "`normalized`",
      "The own contribution is the chance that a node picking one neighbour uniformly at random picks a given one and misses the rest, scaled by its degree; the neighbour contribution is the source's cluster degree, the sum of the neighbours' degrees, weighted by their degree centralities. A node scores well when it has many neighbours and those neighbours are themselves well connected, and a degree-one node scores exactly its neighbour's degree centrality. The measure takes no parameters at all, which the source advertises as one of its contributions. Raw scores are not comparable across graphs of different order: the 1/(n - 1) comes from the degree centrality of equation (1), where n is the vertex count of the whole network rather than of the node's component, so adding a disconnected component multiplies every score by (n - 1)/(n' - 1) and leaves only the ranking untouched. The source's printed equations do not literally give its printed numbers, and cograph follows the numbers. Equations (4) and (5) both sum a term over j = 1 to k, and k is described three incompatible ways: the prose calls it the number of nearest and next nearest neighbours, Algorithm 1 sets it to the degree, and equation (5) taken literally carries one factor of d_i too many, giving 6.75 for the node the paper prints 1.6875 for. Inverting each of the eleven printed influences gives k = d_i^2 in equation (4) and k = d_i in equation (5), the reading implemented here; the equally literal split that moves one d_i from the neighbour factor to the own factor gives the same product, so the measure itself is unambiguous. The Centrality Zoo prints a different formula again, replacing the focal node's contribution probability by each neighbour's and the binomial count by the size of the two-hop neighbourhood; it reproduces none of the printed values and inverts the source's headline ranking, so it is not offered. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed. Weights, mode, cutoff and inversion are ignored. An isolate has no contribution probability and scores zero by explicit extension, and so does the single node of a singleton graph, where n - 1 vanishes too; empty graphs return no scores. There is no normalization in the source; normalized = TRUE max-scales. Cost is one sparse matrix-vector product, and nothing overflows.",
      "Dai, Wang, Sheng, Sun, Khawaja, Ullah, Dejene and Duan (2019), IEEE Access7,131719-131731, DOI10.1109/ACCESS.2019.2939804, Definitions1-5, equations (1)-(6) and Algorithm1, journal pages131721-131723, with the Figure1 graph and Table1 on page131720. IEEE Xplore refuses non-browser clients, so the open-access PDF read is the Internet Archive capture of the publisher file; pages2-5 were visually inspected. All eleven printed Table1 influences, the printed ranking and the three printed intermediates D(v5)=12, ownCon(v5)=1.6875 and neiCon(v5)=19.2 reproduce. Verified against five independent references: exact rational sums over NetworkX neighbour lists, the cluster degree read off an exact integer square of the adjacency matrix, an alternating binomial expansion with explicitly enumerated length-two walks, 60-digit arithmetic, and a separately formed own/neighbour split. No author software exists, so no author-parity claim is made, and the paper's SIR spreading results were not reproduced."),
  rec("Spectral, walk and influence",
      "Iterative resource allocation (IRA)", "ira",
      "Give every node one unit of resource, hand it repeatedly to neighbours in proportion to the receiver's centrality, and read the steady state.",
      r"(I(t+1)=AI(t),\quad a_{ij}=\frac{\theta_i^{\alpha}}{\sum_{u\in\Gamma(j)}\theta_u^{\alpha}}\delta_{ij},\quad I(0)=\mathbf{1})",
      "`ira_mass`, `ira_alpha`, `ira_tol`, `ira_max_iter`, `normalized`",
      "Resource flows out of a node in proportion to what its neighbours are worth, so a node scores well when the nodes that feed it are themselves well fed. Every non-empty column of A sums to one, so nothing is created or destroyed: the scores of a connected component always sum to its vertex count, and that makes raw scores comparable across components. The equilibrium has a closed form, I_i proportional to theta_i^alpha times the sum of theta^alpha over its neighbours, which reproduces the source's own printed steady state exactly. Defaults ira_mass = coreness, ira_alpha = 1 and ira_tol = 1e-6 are the source's values; ira_max_iter = 1000 covers its stated bound of 2N - 1 for graphs up to 500 nodes. The iteration does not always converge, and cograph says so rather than hiding it. A is the transition matrix of a reversible walk, so on a bipartite component it has an eigenvalue of exactly -1 whose coefficient in the all-ones start is the difference between the two class sizes. When those sizes differ the resource settles into a period-two cycle and never meets the tolerance: the three-star alternates for ever between 3, 1/3, 1/3, 1/3 and 1, 1, 1, 1, while the four-path, whose classes are equal, converges to 2/3, 4/3, 4/3, 2/3. In that case cograph stops at ira_max_iter, raises a cograph_no_converge warning naming the largest remaining change, and returns that iterate, which depends on the parity of the bound. It does not average the two alternating iterates and it does not substitute the eigenvector the Centrality Zoo asks for; both converge, and neither is the source's algorithm. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed. Weights, mode, cutoff and inversion are ignored. An isolate is in nobody's neighbourhood, so it receives nothing and passes nothing on and scores zero, which is why the sum-to-n conservation is stated only for graphs without isolates. Empty graphs return no scores; normalized = TRUE max-scales.",
      "Ren, Zeng, Chen, Liao and Liu (2014), EPL106(4):48005, DOI10.1209/0295-5075/106/48005, equations1-3 page2 and algorithm i-iii page3. The original was obtained and read as the author postprint recovered through the Internet Archive, with pages2 and3 visually inspected. All25 printed entries of the equation4 matrix and all20 printed table1 values reproduce, table1 from the exact steady states. One qualification: panel (a) node0 has exact limit 15/8, which the paper rounds up to1.88, while the iteration approaches from below and at the source's own tolerance returns1.8749998, which rounds to1.87. The paper's own claim that I(50) equals those fractions is off by up to1.86e-7. Verified against exact rational propagation, exact binary exponentiation of A, a per-component eigen-decomposition of the symmetrised matrix, the exact closed-form spectral projections, mpmath and extended precision. No author software exists, so no author-parity claim is made, and the SIR spreading results were not reproduced."),
  rec("Spectral, walk and influence",
      "Improved iterative resource allocation (IIRA)", "iira",
      "The same resource iteration, with each node's share scaled by how much of a spreading process it could actually carry.",
      r"(a_{ij}=\bigl[1-(1-\beta)^{k_i}\bigr]\theta_i\Bigl(\sum_{u\in\Gamma(j)}\theta_u\Bigr)^{-1}\delta_{ij},\quad I(t)=A^{t}\mathbf{1})",
      "`ira_mass`, `iira_beta`, `iira_steps`, `normalized`",
      "The extra factor 1 - (1 - beta)^k is the chance that a node with k neighbours is reached at least once at spreading rate beta, so a well-connected receiver draws more resource than its centrality alone would earn it. There is no alpha exponent here: the exponent of IRA is dropped, not set to a value. That factor is strictly below one, so every column of A sums to less than one, the spectral radius is below one, and the resource decays geometrically instead of settling. The source therefore fixes the number of steps rather than a tolerance, runs 50 of them, and prints an I(50) of order 1e-20; cograph returns that raw vector so the printed example is reproducible, and normalized = TRUE max-scales it for reading. Only the ranking carries meaning, and raw scores from different connected components must never be compared: each component decays at its own rate, so after iira_steps steps they sit on different exponential scales. A large iira_steps underflows to zero. Defaults iira_beta = 0.2, iira_steps = 50 and ira_mass = coreness are the worked example's settings; the experiments sweep beta and the step count, so 50 is an example value rather than a tuned recommendation. beta = 0 would annihilate the whole matrix and is refused rather than silently returning zeros; iira_steps = 0 returns the initial unit resource. The Centrality Zoo prints a different formula, pairing the numerator index with the denominator's own neighbourhood, which is stochastic in neither direction and reproduces neither printed quantity; cograph implements the paper. Uses the simple undirected unweighted skeleton; weights, mode, cutoff and inversion are ignored; isolates score zero and empty graphs return no scores.",
      "Zhong, Liu and Shang (2015), Physics LettersA379(38):2272-2276, DOI10.1016/j.physleta.2015.05.021, equations1, 2 and4 page2. What was read is the author preprint arXiv:1505.03214v1, with page2 visually inspected; the Elsevier version of record was not read. All25 printed entries of the equation5 matrix reproduce at the paper's own truncation, which truncates rather than rounds, and all five printed I(50) values reproduce at the printed three significant figures. Because the raw values are of order1e-20 the equivalence run requires a plain relative error as well as a scaled one. Verified against the same independent reference family as IRA. No author software exists, so no author-parity claim is made, and the SIR spreading results were not reproduced."),
  rec("Neighbourhood structure and cohesion",
      "Neighborhood (neighbor distance) centrality", "neighbor_distance",
      "Add up a benchmark centrality over the non-backtracking walks that leave the node, discounted once per step.",
      r"(C^n_i(\theta)=\theta_i+\sum_{k=1}^{n}a^k\!\!\sum_{w\in W_k(i)}\!\!\theta_{\mathrm{end}(w)},\quad W_k(i)=\{\text{non-backtracking walks of length }k\text{ from }i\})",
      "`nd_order`, `nd_decay`, `nd_mass`, `normalized`",
      "The source writes the terms as nested sums, over j in Gamma_i, then over l in Gamma_j minus i, then over m in Gamma_l minus j, and so on: each level excludes only the node the walk just came from. The k-th term is therefore a sum over the non-backtracking walks of length k, and an endpoint reached by several such walks counts once per walk. A walk may return to a node it already visited, the focal node included; only immediate backtracking is barred. This is not a sum over distance shells. The Centrality Zoo paraphrases the measure with sums over the k-hop neighbour sets, which agrees on trees and disagrees on any graph with a triangle or a cycle of length at most 2n. On the triangle-plus-pendant A-B, A-C, B-C, A-D the implemented reading gives 4.16, 3.24, 3.24, 1.76 while distance shells would give 4.00, 3.04, 3.04, 1.76. No shell variant is offered, because the shell form appears only in that paraphrase. Defaults nd_mass = degree, nd_order = 2 and nd_decay = 0.2 are the source's own recommendation and are what the Zoo calls neighbor distance centrality; nd_mass = coreness is the source's other benchmark. nd_order = 0 or nd_decay = 0 returns the benchmark itself. The source's parameter domain is a in [0,1] and n from 1 to 4; cograph accepts any finite decay and any nonnegative whole order, which leaves that domain. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed, since a loop would make the previous node ambiguous. Weights, mode, cutoff and inversion are ignored. Isolates score zero, walks never leave a component so raw scores are component-local, and empty graphs return no scores. There is no normalization in the source; normalized = TRUE max-scales as elsewhere. Cost is nd_order matrix-vector products, O(n^2) each; walk counts grow geometrically, so a large order overflows.",
      "Liu, Tang, Zhou and Do (2016), Physica A452,289-298, DOI10.1016/j.physa.2016.02.028, section2.3 equation1, read in the author preprint arXiv:1511.00441v1 page4; the published version is paywalled and was not read. The paper prints no table of node scores, so there is no published numerical fixture; its printed statements about the measure are checked instead. Verified against four independent walk-counting references: dictionary edge propagation, explicit enumeration of every non-backtracking walk, brute-force enumeration of all walks with the backtracking ones filtered out, and a dense Hashimoto edge matrix, all in exact rational arithmetic. No author software exists, so no author-parity claim is made, and the paper's SIR spreading results were not reproduced."),
  rec("Shortest-path brokerage and flow",
      "Relative-entropy integrated evaluation", "relative_entropy",
      "Turn several indexes into distributions and take the distribution closest to all of them.",
      r"(u_{ji}=C_j(i)/\textstyle\sum_k C_j(k)\ \text{or}\ (1-C_j(i)/\sum_k C_j(k))/\sum_l(1-C_j(l)/\sum_k C_j(k)),\quad w_i=\prod_{j=1}^{m}u_{ji}^{1/m}\Big/\sum_{i}\prod_{j=1}^{m}u_{ji}^{1/m})",
      "`re_indexes`, `re_negative`, `normalized`",
      "The score minimising the total relative entropy to m index distributions has a closed form: the normalised geometric mean of those distributions. No index weights have to be chosen, and the result sums to one, so it reads as a share of importance. A positive index (larger is more important) is divided by its own total; a negative index (smaller is more important) has its complement renormalised instead, so only an index's shape matters, never its units, and the log base in the objective cancels out entirely. The geometric mean is unforgiving: a node that is exactly zero on any one index is exactly zero overall, which is the paper's own printed behaviour for the three Kite nodes with zero betweenness. re_indexes defaults to the paper's four distinctiveness indexes (degree, closeness, betweenness, constraint) and also accepts n_components and largest_component, the two destructiveness indexes measured after deleting the node; re_negative overrides which of them are read as negative. Only these six are offered because the paper defines and declares a direction for exactly these six. Two conventions are unusual: equation 6's constraint sums over every other node rather than over the neighbours, so it is not Burt's constraint, and equation 4's betweenness counts ordered pairs, twice the usual value, which the map then cancels. Equation 3's closeness sums distances over the whole node set, which is identically zero on a disconnected graph; cograph sums the reachable partners instead, an explicit extension outside the paper's connected domain, giving isolates closeness and constraint zero. There is no value when an index is zero at every node, so betweenness on a complete graph, degree on an edgeless one, and equation 9 on a single node all raise a classed error rather than returning zeros. Naming the measure yourself always raises; when a tier such as centrality(type = \"all\") asked for it instead, the condition becomes a warning and an NA column, which is what happens on a complete graph. Uses the simple undirected unweighted skeleton; weights, mode, cutoff and inversion are ignored; empty graphs return no scores. Raw output already sums to one, so normalized = TRUE only rescales it by the maximum.",
      "Chen, Wang and Luo (2016), Journal of Systems Engineering and Electronics27(6),1219-1226, DOI10.21629/JSEE.2016.06.10, equations3,4,6,8,9,10,11 and Tables1-3. All60 printed Table1 and Table3 index entries reproduce exactly at the printed precision, and all30 printed Table2 integrated values reproduce to six decimals when the paper's own rounded columns are used as inputs; from the exact graph the printed values differ by up to 3.6e-5, because the paper integrated its rounded intermediates. Verified against independent NetworkX shortest-path counts, exact rational constraint sums and high-precision roots. The paper offers no software, so no author-software or spreading-performance claim is made."),
  rec("Shortest-path brokerage and flow",
      "DK-based gravity model", "dkgm",
      "Degree, k-shell and the stage at which peeling reached the node act together as gravitational mass.",
      r"(k_s^*(i)=k_s(i)+p(i)/(\max_k q(k)+1),\quad DK(i)=k(i)+k_s^*(i),\quad DKGM_i=\sum_{j\ne i,\,d(i,j)\le R}DK(i)DK(j)/d(i,j)^2)",
      "`dkgm_radius`, `normalized`",
      "The stage p(i) counts how many synchronous removal rounds the node's own shell needed before it left, so two nodes of the same shell are separated by how late the peeling reached them. Stages restart inside every shell, but max q(k)+1 is a single global denominator: adding a disconnected component that peels in more stages changes every raw score. That follows the published definition, not a cograph choice. The paper's Algorithm 1 prints degree exactly k while its stage loop ends at degree greater than k and its Methods define k-shell by degree at most k; cograph follows the at-most reading, the only one that terminates, and it reproduces the printed Tables 2 to 5. The level starts at one, so an isolate lands in the one-shell rather than the zero-shell coreness reports; isolates carry no edges, so nothing else changes. Default radius two is the printed example's setting and one of the two the paper recommends generally; NULL or infinity includes all reachable partners, fractional cutoffs are literal and values below one give zero. Auto applies the paper's own R = mean distance over two, with cograph rounding to the nearest integer, ties to even, minimum one, over reachable pairs. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once and loops are removed. Weights, mode, cutoff, gravity_mass and inversion are ignored. Isolates and singleton graphs score zero; empty graphs return no scores. Dense O(n^3) time/O(n^2) memory.",
      "Li and Huang (2021), Scientific Reports11,22194, DOI10.1038/s41598-021-01218-1, equations1-3, Algorithm1 and Tables1-5. All45 printed Table1-5 entries and the printed node-3 worked example reproduce; independent NetworkX node-deletion peeling, exhaustive subset cores, integer-power distances and exact rational sums. No author software was located, so no author-software parity or spreading-performance claim is made."),
  rec("Shortest-path brokerage and flow",
      "Mixed gravitational centrality", "mixed_gravity",
      "Core-number mass at the source interacts with degree mass at nearby nodes.",
      r"(MGC_i=k_s(i)\sum_{j:0<d(i,j)\le r}k(j)/d(i,j)^2)",
      "`gravity_radius`, `normalized`",
      "Default radius three follows the explicit published reproduction. Source core number and partner degree are asymmetric masses, both measured on the original graph. The Zoo's literal immediate-neighbor sum is available with radius one. NULL or infinity includes all reachable partners; fractional cutoffs are literal and values below one give zero. Auto is a cograph heuristic: rounded half the mean finite positive hop distance, ties to even, minimum one. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallels count once, loops are removed. Weights, mode, cutoff, gravity_mass and inversion are ignored. Isolates and singleton graphs score zero; empty graphs return no scores. With fixed radius, disconnected additions preserve existing raw scores; auto and global maximum normalization can change them. Dense O(n^3) time/O(n^2) memory.",
      "Wang, Li and Xia2018, DOI10.1016/j.amc.2018.04.028, as reproduced in Li and Huang2022, DOI10.1038/s41598-022-14005-3, equations5-8. The original full equations and software have not been inspected. Verified with NetworkX core/BFS, exhaustive subset cores, integer-power distances and exact rational sums; no author-software or general predictive-performance claim."),
  rec("Shortest-path brokerage and flow",
      "Extended mixed gravitational centrality", "extended_mixed_gravity",
      "Sum immediate neighbors' raw mixed gravitational scores.",
      r"(EMGC_i=\sum_{j\in N(i)}k_s(j)\sum_{l:0<d(j,l)\le r}k(l)/d(j,l)^2)",
      "`gravity_radius`, `normalized`",
      "The inner radius is centered on each neighbor j, so contributions can reach r+1 hops from the focal node; returns to the focal node count. The outer sum has no distance or mass factor. Default inner radius three follows the published reproduction; radius one matches the Zoo literal interpretation. All features and distances belong to the original simple undirected unweighted skeleton. Weights, mode, cutoff, gravity_mass and inversion are ignored; loops are removed and parallels count once. NULL/Inf, fractional and auto radius conventions are shared with MGC. Isolates, singleton graphs and radii below one score zero; empty graphs return no scores. Optional maximum normalization occurs only after the raw outer sum. Dense O(n^3) time/O(n^2) memory.",
      "Wang, Li and Xia2018, DOI10.1016/j.amc.2018.04.028, reproduced in Li and Huang2022, DOI10.1038/s41598-022-14005-3, equation8 with neighborhoods defined in equations5-7. Original full equations/software unread. Verified with independent nested pair sums, exact rational references and public analytic graph families."),
  rec("Spectral, walk and influence",
      "Multi-characteristics gravity model", "mcgm",
      "Combine degree, coreness and eigenvector features in distance-decaying node interactions.",
      r"(m_i=K_i+\alpha S_i+X_i,\quad \alpha=\max\{\mathrm{med}(K),\mathrm{med}(X)\}/\mathrm{med}(S),\quad MCGM_i=\sum_{j:0<d(i,j)\le R}m_i m_j/d(i,j)^2)",
      "`mcgm_radius`, `mcgm_alpha`, `normalized`",
      "K, S and X divide each original-graph feature by its global maximum. Default radius two follows the paper; NULL or infinity includes all reachable partners. Uses the simple undirected unweighted skeleton: either arc creates one edge, parallel edges count once and loops are removed. Weights, mode, cutoff, gravity parameters and inversion are ignored. For disconnected inputs, the explicit cograph eigenvector convention projects a uniform vector onto the global dominant eigenspace; weaker components have eigenvector feature zero. Roots within 64 machine epsilons times n times max(1,rho) are treated as tied. Medians and maxima remain global. A zero median coreness with edges makes automatic alpha undefined and raises an error; supply an explicit nonnegative mcgm_alpha to override it. Alpha one recovers equation16. Edgeless graphs and radii below one score zero by an empty-interaction convention. Isolates score zero when masses are defined. Optional maximum normalization follows the complete gravity sum and supports large alpha when raw scores overflow. Dense O(n^3) time/O(n^2) memory; unresolved positive eigenvectors and overflowing raw scores error.",
      "Li and Huang (2022), Scientific Reports12,9879, DOI10.1038/s41598-022-14005-3, equations17-18 and Algorithm1. All36 Table1-2 feature and score entries reproduced at printed precision; independent NetworkX power/BFS/core and exact-root resolvent references. No author-software or universal predictive-performance claim."),
  rec("Spectral, walk and influence",
      "SpectralRank", "spectralrank",
      "Outgoing influence after adding a ground node and optional node priors.",
      r"(B=\begin{pmatrix}A+\operatorname{diag}(p)&\mathbf{1}\\\mathbf{1}^{T}&0\end{pmatrix},\quad Bs=\rho(B)s,\quad SR_i=s_i/\max_{j\le n+1}s_j)",
      "`sr_prior`, `directed`, `weighted`, `simplify`, `normalized`",
      "Default prior zero gives SpectralRank. A scalar prior broadcasts; a vector supplies nonnegative node information, with named values reordered to match nodes. The ground prior remains zero and its links have fixed unit weights. Raw maximum scaling includes the ground node; it is omitted without redistribution, so returned maxima can be below one. Optional normalized=TRUE rescales original nodes alone. Uses outgoing neighbors; transpose input for incoming influence. Binary adjacency follows the source, while nonnegative interaction weights extend the same matrix definition and differ from the paper's diagonal-prior meaning of weighted SpectralRank. Tiny asymmetric matrices require explicit directed=TRUE or a directed igraph object. Loops removed, remaining parallel edges sum after simplify; unweighted remaining edges count one each. Mode/inversion/cutoff ignored. Isolates are positive; edgeless prior-zero scores are1/sqrt(n), singleton1 and empty output. Adding disconnected nodes changes the common ground system. Uses the unique positive Perron eigenvector even where the source's unshifted iteration oscillates. Dense O(n^3) time/O(n^2) memory; unresolved positive eigenpairs or extreme ranges error.",
      "Xu, Wang, Zhang and Lu (2019; online2018), IEEE TCYB49(12),4253-4261, DOI10.1109/TCYB.2018.2861568, sectionIII-A eq4-8. Nonzero priors follow the prose's Atilde+P; Algorithm1 constructs this matrix but omits P in its update line. Independent NetworkX shifted iteration on the reversed augmented graph, exact-polynomial-root resolvents and high-precision eigenvectors verify values. Figure2's two outgoing update equations are reproduced; no published numerical table or author-code parity is claimed."),
  rec("Spectral, walk and influence",
      "ControlRank", "controlrank",
      "Smallest grounded eigenvalue after pinning each node in turn.",
      r"(CR_i=\lambda_{\min}(((L+L^T)/2)_{-i,-i}),\quad L=\operatorname{diag}(A\mathbf{1})-A)",
      "`directed`, `weighted`, `simplify`, `normalized`",
      "Original degrees are retained after deletion. Directed inputs use outgoing strengths; transpose the input for incoming strengths. Tiny asymmetric matrix weights require explicit directed=TRUE or a directed igraph object because the shared parser uses approximate symmetry. Symmetrizing this row-Laplacian differs from taking the Laplacian of an undirected projection, and signed directed scores are retained. Uses finite nonnegative interaction weights, removes loops, and sums remaining parallel edges after the simplify rule; unweighted remaining edges contribute one each. Mode, inversion and cutoff are ignored. Connected undirected graphs have positive scores; disconnected undirected graphs score zero globally. Empty graphs return no scores and singleton zero explicitly extends the undefined empty minor. The matrix formula extends the source beyond its no-isolates domain. Optional normalization divides by a positive maximum, otherwise retains raw units. Global weight scaling multiplies raw scores. Dense O(n^4) time/O(n^2) memory; marked costly. Separate disconnected blocks preserve structural zeros before normalization. Extreme weight ranges or unresolved positive grounded spectra raise errors; small eigenvalues can lose relative accuracy. This spectral index does not simulate controllers, establish a general directed stability guarantee, or optimize controller sets.",
      "Zhou, Yu and Lu (2019; online2018), IEEE TCAS-II66(3),437-441, DOI10.1109/TCSII.2018.2845940, Theorem3 and Figure1. The published bi-star has11 numerical node values. Independent references use SciPy row-Laplacians and spectral bisection, exact SymPy characteristic-polynomial root intervals, and NetworkX incidence-matrix singular values. Counterexamples retain the distinction between grounded scores and finite-feedback convergence rates."),
  rec("Community and group-based",
      "Map equation centrality", "map_equation",
      "Bits saved by redesigning a fixed module's codebook after silencing a node.",
      r"(MEC(i)=-(s_m-p_i)\log_2((s_m-p_i)/s_m),\quad s_m=\sum_{j\in m}p_j+q_m)",
      "`membership`, `map_flow`, `map_convention`, `damping`, `weighted`, `simplify`, `normalized`",
      "Default paper convention includes module-exit flow q_m. The infomap convention sets q_m to zero in this score, reproducing Infomap2.15.1 and the paper's Table1; these conventions can change rankings and are not made equivalent by normalization. Both are nonnegative, with the continuous boundary value zero. Default unrecorded link teleportation targets out-strength and records only link steps; on undirected inputs visit rates are proportional to strength. Recorded node teleportation uses uniform targets and records all moves. Damping defaults to0.85 and must be below1; dangling nodes teleport. NULL membership uses one global module. Supply globally unique leaf-module labels for a hierarchical partition; upper codebooks cancel. The partition stays fixed and no community detection runs. Retains direction and nonnegative interaction weights, removes loops, and sums remaining parallel edges after the simplify rule. Mode/inversion/cutoff ignored. Empty/singleton scores are empty/zero; edgeless unrecorded scores zero, recorded flow uniform. Dense O(n^3) time/O(n^2) memory; unrecorded undirected flow O(n^2). Raw units are bits; optional maximum scaling changes those units. Extreme weight ranges or singular numerical solves error.",
      "Blocker, Nieves and Rosvall2022, DOI10.1007/s41109-022-00477-9, eq2/9-11 and Figure2 (paper convention), Table1 (Infomap convention). Lambiotte-Rosvall2012, DOI10.1103/PhysRevE.85.056107, unrecorded link teleportation. Verified with NetworkX PageRank, direct silenced-code differences, external Infomap2.15.1, all24 table entries, hierarchical codebooks and700-digit small-score calculations. The Zoo summary subtracts from the full original code length and thus includes a different self-information term."),
  rec("Spectral, walk and influence",
      "Node and Neighbor Layer Information", "ninl",
      "Propagate degree volume through a chosen number of neighbor steps.",
      r"(b_i=\sum_{j:d(i,j)\le r}d_j,\quad r=\lceil L\rceil,\quad NINL_p=A^p b)",
      "`ninl_order`, `ninl_radius`, `normalized`",
      "Default order3 follows Zhu and Wang. Order0 returns closed-neighborhood degree volume; walks may repeat edges and vertices. Automatic radius is the ceiling of mean distance over all distinct pairs. For disconnected graphs, cograph explicitly extends this to infinite radius and sums only reachable nodes. Isolates score zero; empty graphs return no scores. Numeric radius or Inf overrides generalize the source rule. Uses simple undirected unweighted topology, removing loops and duplicates; either arc creates an edge, and weights/mode/inversion/cutoff are ignored. Stepwise propagation preserves finite-order bipartite alternation. Only exactly repeated floating-point states of period1 or2 permit skipping; no approximate convergence criterion. Maximum normalization rescales each step to avoid overflow; raw overflow errors and very small relative values can underflow. Dense O(n^3+p*n^2) time/O(n^2) memory; huge orders may be slow without an exact repeated state.",
      "Zhu and Wang (2021), Symmetry13,1570, DOI10.3390/sym13091570, section2.1 eq1-2, Figure1 and Table1. All52 published entries reproduced. Independent NetworkX BFS neighborhoods, NumPy powers with arbitrary-precision integers, and explicit walks verify numerical values. This is a finite walk family; ranking correlation with communicability is not equivalence."),
  rec("Shortest-path brokerage and flow",
      "Localized bridging centrality", "localized_bridging",
      "Brokerage in the one-hop ego network, adjusted for neighbor degrees.",
      r"(LBC(v)=B_{G[N_{\leq1}(v)]}(v)\,\frac{1/d_v}{\sum_{u\in N(v)}1/d_u})",
      "`normalized`",
      "Ego betweenness counts unordered pairs, excludes endpoints and is not normalized by ego size. Bridging-coefficient degrees come from the original graph. Uses simple undirected unweighted topology: either direction creates an edge; loops and duplicate edges removed; weights/mode/inversion/cutoff ignored. Isolates and leaves score zero; the isolate rule extends the undefined coefficient by zero. Final maximum scaling is optional. Common-neighbor matrix multiplication over all ego networks has worst-case O(n^4) time and O(n^2) memory.",
      "Nanda and Kotz (2012), DOI10.1007/978-1-4614-0857-4_7, eq7.7-7.8, author chapter restating their2008 LBC definition. Macker2016 eq4 and TableI reproduce this definition. Verified with NetworkX ego graphs/Brandes, independent explicit shortest-path enumeration, and all11rows of Macker's synthetic example. The legacy local_bridging key computes inverse degree times the coefficient and is a different score."),
  rec("Shortest-path brokerage and flow",
      "Extended local bridging centrality", "extended_local_bridging",
      "Brokerage in the two-hop ego network, adjusted for neighbor degrees.",
      r"(LBC_2(v)=B_{G[N_{\leq2}(v)]}(v)\,\frac{1/d_v}{\sum_{u\in N(v)}1/d_u})",
      "`normalized`",
      "Uses every edge induced by the focal vertex and all vertices at hop distance at most two. Paths inside this ego graph can have up to four edges; this is not a global path-length cutoff. Betweenness uses unordered pairs and no ego-size scaling; coefficient degrees come from the original graph. Same simple undirected unweighted projection and zero conventions as localized_bridging. Macker's weighted link-quality/cost model is outside this implementation. Native breadth-first counts take O(sum n_ego(n_ego+m_ego)) time, at worst O(n^4), and O(n^2) memory. Marked costly; select explicitly.",
      "Macker (2016), DOI10.1109/MILCOM.2016.7795393, sectionsIV-V, eq5 and TableI; original PDFpages2-3 visually read. Independently verified by NetworkX ego/Brandes and explicit shortest-path enumeration. All11original synthetic example rows agree. Numerical definition verification does not establish the paper's empirical ranking correlations or equivalence to unreleased Zoo code."),
  rec("Directed prestige and hierarchy",
      "BG-index (beta power)", "beta_measure",
      "Expected number of times a node is selected as a predecessor.",
      r"(\beta^+(i)=\sum_{i\to j}1/d^-(j),\quad\beta^-(i)=\sum_{j\to i}1/d^+(j))",
      "`beta_direction`, `normalized`",
      "Positive (default) credits sources; each successor divides one unit equally among its predecessors. Negative applies the same rule to the reversed graph. Both coincide on undirected graphs. Uses simple unweighted topology, preserving direction: loops and duplicate arcs removed; weights/mode/inversion/cutoff ignored. Isolates score zero and empty graphs return no scores. Raw totals equal the number of vertices with positive in-degree (positive variant) or out-degree (negative variant); normalized=TRUE divides by the maximum, not the total. Dense O(n^2) time and memory. The original weighted extension is outside this implementation.",
      "Van den Brink and Gilles (1992), FEW565 definition2.1/example2.2 pp3-4, visually read; (2000) DOI10.1016/S0378-8733(00)00019-8 definition2.1. Negative orientation: Boldi and Vigna (2014), DOI10.1080/15427951.2013.865686. Verified by independent exact predecessor-choice enumeration, NetworkX neighbor queries with rational arithmetic, and the original diamond example. This is numerical definition verification, not parity with unreleased Zoo code."),
  rec("Spectral, walk and influence",
      "Expected Force", "expected_force",
      "Entropy of onward transmission opportunities after two infection events.",
      r"(ExF(i)=-\sum_{j=1}^{J}p_j\log p_j,\quad p_j=D_j/\sum_kD_k)",
      "`normalized`",
      "Enumerates ordered infected-to-susceptible edge transmissions without recovery. Each event sequence retains its own normalized boundary degree, even when infected sets coincide. Boundary edges to the same susceptible node count separately. Directed inputs use outgoing edges. Simple unweighted graph: loops and duplicate arcs removed; weights/mode/inversion/cutoff ignored. No two-event sequences or no positive onward force gives zero, the latter an explicit extension of undefined all-zero normalization. A single positive-force outcome also has entropy zero. Worst-case O(n^3) time/O(n^2) memory. This is a local score, not an epidemic probability.",
      "Lawyer (2015), DOI10.1038/srep08665, eq1 and directed extension. Verified by NetworkX explicit transmission sequences and pinned author C++ on connected undirected graphs of order>=4. The author R example counts distinct outside nodes, whereas the paper/C++ count edges; that R behavior is not replicated. The existing expected key sums neighbor degrees and is a different measure."),
  rec("Spectral, walk and influence",
      "Modified Expected Force", "modified_expected_force",
      "Expected Force adjusted for the seed degree.",
      r"(ExF^M(i)=\log(\alpha d_i)ExF(i),\quad\alpha>1)",
      "`exf_alpha`, `normalized`",
      "Uses Expected Force after exactly two events. Alpha defaults to two as in the paper; it must be finite and greater than one. Directed graphs use outgoing degree. Isolates return zero without log(0). All Expected Force graph and exhausted-force conventions apply. Log addition avoids overflow of alpha times degree; normalization divides the resulting modified scores by their maximum. The weighted extension and alternative event horizons are outside the verified scope.",
      "Lawyer (2015), DOI10.1038/srep08665, eq2. Independent event enumeration and the pinned author C++ force followed by the published degree modification. Tested across alpha1.0001/1.5/2/4/16/1e308; high ranking correlations are not used as evidence of equivalence."),
  rec("Shortest-path brokerage and flow",
      "Proximal betweenness", "proximal_betweenness",
      "Brokerage at the first or last intermediate vertex of shortest paths.",
      r"(C_{ps}(v)=\sum_{s,t:(v,t)\in E}\sigma_{st}(v)/\sigma_{st})",
      "`proximal_variant`, `normalized`",
      "Source (default) means the last intermediary before the destination; target means the first after the origin. Sum counts both roles; union counts a two-edge intermediary once. Endpoints and unreachable pairs are excluded. Raw scores use ordered pairs even on undirected graphs, without halving. Directed simple unweighted skeleton: loops and duplicate arcs removed, weights/mode/inversion/cutoff ignored. Empty graphs return no scores; isolates and complete graphs score zero. Breadth-first traversal takes O(n(n+m)) time after dense O(n^2) preparation; nonfinite path counts raise an error.",
      "Brandes (2008), DOI10.1016/j.socnet.2007.11.001, section3.2 Algorithm3; author preprint12Nov2007 pp7-8 read. Independent NetworkX shortest-path enumeration and exact integer adjacency powers verify all four variants. No equivalence claim for weighted geodesics, edge-distinct multigraph paths, or unreleased Zoo/UCINET software."),
  rec("Spectral, walk and influence",
      "Bridging capital", "bridging_capital",
      "Loss of valued information walks after deleting each outgoing matrix entry.",
      r"(Brid_i=\sum_j\sum_{s,t}v_{st}\sum_{h=1}^{T}[P^h-(P-P_{ij}E_{ij})^h]_{st})",
      "`bridging_steps`, `bridging_values`, `weighted`, `loops`, `simplify`, `normalized`",
      "Per-contact transmission probabilities must be in [0,1]; row sums need not equal one. Default horizon is two and source-destination values are all ones. Named value matrices reorder by node labels. Single-entry deletion leaves the reverse entry intact even on undirected input. Walks may repeat nodes/edges, but each distinct selected arc receives each lost walk once. Loops remain; parallel weights aggregate within probability bounds. Zero horizon/values and isolates yield zero. Mode/inversion/cutoff are ignored. Dense O(m T n^3) time/O(n^2) memory; request explicitly. Use weighted=FALSE for a binary probability-one example when input weights are interaction counts.",
      "Jackson (2020), DOI10.1007/s00355-019-01189-3; author preprint arXiv1711.09504v3 section3.3, printedp18 visually read. Implements EInf expected walk counts and the literal single-entry deletion, not PInf or whole-edge/node removal. Verified by NetworkX graph deletion/NumPy powers and independent explicit walk-set enumeration. Native first-use tracking avoids power-subtraction cancellation; nonrepresentable intermediate masses raise errors."),
  rec("Neighbourhood structure and cohesion",
      "Coleman-Theil hierarchy", "coleman_theil",
      "Concentration of Burt's dyadic constraints over a node's contacts.",
      r"(H_i=\frac{\sum_{j\in N(i)}r_{ij}\log(r_{ij})}{d_i\log d_i},\quad r_{ij}=c_{ij}/\operatorname{mean}_{k\in N(i)}c_{ik})",
      "`weighted`, `simplify`, `normalized`",
      "Mutual weights sum both directions; local constraints use full-graph investment proportions and organizational multipliers fixed at one. Distinct positive mutual contacts determine the count. Zero weights and loops are removed; remaining parallel weights sum. The author's manual sets isolates to zero and one-contact nodes to one. Default scores lie in [0,1]; normalized=TRUE additionally divides by the global maximum. Mode, inversion and cutoff are ignored. Dense O(n^3) time/O(n^2) memory; stable entropy arithmetic preserves tiny departures from uniformity.",
      "Burt, STRUCTURE4.2 Reference Manual (copyright1991), pp181–183, reproducing Burt1992 eq2.9. Author formula and small-network conventions visually read. Verified using NetworkX local_constraint plus direct entropy, exact rational constraints and mpmath100 near-uniform cases. JUNG documents a different isolate convention (NaN); that behavior is not claimed equivalent."),
  rec("Degree, strength and local connectivity",
      "X-degree", "x_degree",
      "Nonbacktracking four-edge walks centered at each node.",
      r"(Xdeg(i)=\left[\sum_{j\in N(i)}(d_j-1)\right]^2-\sum_{j\in N(i)}(d_j-1)^2)",
      "`normalized`",
      "Uses original neighbor degrees on the simple undirected unweighted skeleton. Loops and repeated connections are removed; weights, direction, mode, inversion and cutoff are ignored. Isolates, leaves and every node in a star score zero. Walks may revisit vertices but cannot immediately reverse an edge. Components are independent before maximum normalization. Native pair accumulation avoids subtracting large squares; dense skeleton preparation uses O(n^2) time and memory. This is a static centrality score, not the iterative immunization strategy.",
      "Torres et al. (2021), DOI10.1137/20M1352132, Proposition3.8 eq3.15. Verified against the unchanged x_degree function from the author's inbox repository, commit401bf028b56886ce67b15b2c5eacd7a28dbb4a48, independent nonbacktracking block products DFE and explicit four-edge walk enumeration. Includes every simple labeled graph through five vertices."),
  rec("Spectral, walk and influence",
      "LineRank", "linerank",
      "Stationary edge-state probabilities aggregated at original endpoints.",
      r"(p=cQ^T p+(1-c)\mathbf{1}/m,\quad LR_v=\sum_{e\text{ incident to }v}p_e)",
      "`damping`, `linerank_aggregation`, `weighted`, `loops`, `simplify`, `normalized`",
      "Directed line transitions join consecutive edges; undirected inputs use one state per edge and connect distinct states sharing an endpoint. Transition weights are products of original edge weights, evaluated without forming those products. Default probability aggregation sums endpoint probabilities; weight aggregation additionally multiplies original edge weights. Loops count twice in endpoint aggregation, directed loops permit self transitions, and undirected line graphs exclude self transitions. Generic loops/simplify apply first; remaining parallel states are retained. Dangling states redistribute uniformly. Isolates and edgeless graphs score zero. Dense O(m^3) time/O(m^2) memory; request explicitly.",
      "Kang et al. (2011), DOI10.1137/1.9781611972818.11, definitions2–4 and weighted aggregation in Algorithm2; Kosa et al. (2015), DOI10.2298/CSIS141101092K, section4 clarifies undirected construction. Follows the random-walk definition; the original pseudocode's inconsistent row/column normalization is not replicated. Verified against NetworkX line_graph and PageRank and independent Markov-chain tree cofactors."),
  rec("Spectral, walk and influence",
      "Random walk decay", "random_walk_decay",
      "Discounted first arrival at each node, summed over starting-node weights.",
      r"(RWD_v=\sum_u b_u\,\mathbb{E}_u[a^{T_v};T_v<\infty],\quad 0\leq a<1)",
      "`rwd_decay`, `rwd_node_weights`, `weighted`, `loops`, `simplify`, `normalized`",
      "Decay defaults to0.5 and starting weights default to one. Each node contributes its own starting weight at time zero; later returns do not count. Sinks terminate the walk outside the graph. Retains direction, loops and nonnegative edge weights; undirected edges become opposite transitions. Use simplify=FALSE to retain unweighted parallel multiplicity. Named starting weights match node labels; all-zero weights and zero decay have explicit linear/limit extensions. Raw scores obey lack of self-impact: changing a node's outgoing edges cannot change its own score. Generic mode, inversion and cutoff are ignored. Per-target absorbing solves cost up to O(n^4), so request explicitly.",
      "Was, Rahwan and Skibski (2019), DOI10.1609/aaai.v33i01.33012197, Definition1 eq6, transition eq3 and terminal-sink convention. Original PDF and figures read visually. Independent full-resolvent ratios, first-visit series, exact rational and high-precision arithmetic; published Example4/5 tables agree. Example3 contains internally inconsistent numbers retained in the audit."),
  rec("Spectral, walk and influence",
      "Graph regularization centrality", "graph_regularization",
      "Reciprocal retention of a unit impulse under weighted Laplacian smoothing.",
      r"(GRC_i=1/[(I+\gamma L)^{-1}]_{ii},\quad L=D-W,\quad \gamma\geq0)",
      "`grc_gamma`, `weighted`, `normalized`",
      "Finite nonnegative gamma defaults to one. Uses the unnormalized weighted Laplacian; scores lie between one and component size. Isolates and gamma zero score one. Weighted opposite arcs and remaining parallel edges are summed; unweighted graphs use the simple skeleton. Loops, mode, inversion and cutoff are ignored. These directed projections are cograph conventions. A component spectral calculation separates the constant mode and uses log-space attenuation for extreme parameters; unresolved weight ranges or spectra raise errors.",
      "Dal Col and Petronetto (2023), DOI10.1016/j.physa.2023.129188; author implementation linked by Mendeley Data DOI10.17632/ns63f5dj86.1. Independent SciPy Cholesky solves, LU determinant ratios and 700-digit arithmetic verify the exact inverse definition. The retained author's ten-term Chebyshev approximation differs in general; convergence at 1024 terms is checked separately."),
  rec("Spectral, walk and influence",
      "Adaptive LeaderRank", "adaptive_leaderrank",
      "Stationary resource scores with every destination weighted by its original H-index and a ground node with H-index one.",
      r"(h_g=1,\quad w_{ji}=a_{ji}h_i,\quad s_i=\sum_j\frac{w_{ji}}{\sum_k w_{jk}}s_j,\quad \sum_{i\cup g}s_i=N)",
      "`alr_h_mode`, `normalized`",
      "Computes H-indices from original open neighborhoods before adding ground. Default H-index mode all uses the undirected skeleton; out uses outgoing neighbors' out-degrees and in uses incoming neighbors' in-degrees. The paper leaves this directed convention unspecified, so these are explicit cograph choices. Resource flow retains original arcs. Input weights, generic mode, loops and cutoffs are ignored; parallels collapse. Raw scores omit ground without redistribution. All-zero H-indices give NaN; otherwise H-zero nodes score zero. A native stationary solve handles periodicity.",
      "Xu and Wang (2017), DOI10.1016/j.physa.2016.11.034, section 2.2, equation 3 and steps 1–4. Published PDF obtained from the author's archive and equation visually checked. Verified using independent H-index threshold enumeration and NetworkX lazy-chain iteration, Markov-chain tree cofactors, and the undirected reversible-conductance identity."),
  rec("Spectral, walk and influence",
      "Weighted LeaderRank", "weighted_leaderrank",
      "Stationary resource scores with a ground node that distributes according to original in-degree powers.",
      r"(w_{gi}=(k_i^{in})^{\alpha},\quad w_{ig}=1,\quad s_i=\sum_j\frac{w_{ji}}{\sum_l w_{jl}}s_j,\quad \sum_{i\cup g}s_i=N+1)",
      "`wlr_alpha`, `normalized`",
      "Retains original directed arcs; undirected edges become opposite arcs. Input weights, mode, loops and cutoffs are ignored. Raw scores follow the paper's all-nodes-one initialization and omit the ground without redistribution. Zoo's ground-zero initialization gives scores multiplied by N/(N+1); max normalization agrees. Any finite exponent is accepted, but negative values require positive in-degree everywhere. At zero exponent all ground weights are one; positive exponent with no edges gives NaN. A stationary solve handles periodicity; shifted logarithms avoid power overflow, with tiny probabilities allowed to underflow.",
      "Li, Zhou, Lu and Chen (2014), DOI10.1016/j.physa.2014.02.041, section 2 and equations 1–2; author preprint arxiv1306.5042v2. Independently checked with NetworkX PageRank on the lazy augmented chain, Markov-chain tree cofactors and 100-digit mpmath stationary equations. No author-code or predictive-performance parity is claimed."),
  rec("Distance and closeness",
      "Improved Global Structure Model", "improved_global_structure",
      "Focal degree influence combined with degrees of reachable partners and a distance exponent set by global mean degree.",
      r"(IGSM_i=e^{k_i/N}\sum_{j\ne i}\frac{k_j}{d_{ij}^{a}},\quad a=\lceil\log_2\overline{k}\rceil)",
      "`normalized`",
      "Uses simple undirected degrees, hop distances and original N, including isolates. Weights, mode, loops and cutoffs are ignored. Unreachable partners contribute zero; edgeless graphs score zero by explicit extension. Zero or negative exponents for sparse disconnected graphs are retained; negative powers increase contributions from distant reachable partners. No additional neighbor aggregation for extended IGSM is applied.",
      "Zhu and Wang (2022), DOI10.1088/1674-1056/ac380d; the exact implemented definition was read in Mukhtar et al. (2023), DOI10.1038/s41598-023-37570-7, eq. 5, not the original full text. Verified using independent NetworkX degrees/BFS, Floyd-Warshall distances and analytic mean-degree ceiling cases."),
  rec("Distance and closeness",
      "Global Structure Model", "global_structure",
      "Focal coreness combined with distance-discounted coreness of all reachable partners.",
      r"(GSM_i=e^{k_s(i)/N}\sum_{j\ne i}\frac{k_s(j)}{d_{ij}})",
      "`normalized`",
      "Original core numbers and global N are used, including isolates. All reachable partners contribute, with no radius cutoff. Uses the simple undirected skeleton; weights, mode and loops are ignored. Unreachable partners contribute zero and isolates score zero. Other components can change the focal exponential through N.",
      "Ullah et al. (2021), DOI10.1038/s41598-021-84684-x, eqs. 5–8. Verified against NetworkX cores/BFS distances and exhaustive subset cores with Floyd-Warshall. A constructed graph consistent with the paper's stated core/distance inputs reproduces its focal calculation; the original figure was not visually transcribed."),
  rec("Distance and closeness",
      "Hybrid Global Structure Model", "hybrid_global_structure",
      "Exponential degree-coreness influences with a distance penalty set by their global mean.",
      r"(s_i=e^{k_s(i)k_i/N},\quad a=\lceil\log_2\overline{s}\rceil,\quad H\!GSM_i=s_i\sum_{j\ne i}\frac{s_j}{d_{ij}^{a}})",
      "`normalized`",
      "Uses original N and the mean over all nodes, including isolates. Only reachable partners contribute. Uses the simple undirected skeleton and ignores weights/mode. Logarithmic arithmetic supports normalized results even if raw scores overflow; requesting an unrepresentable raw score raises an error. Very small normalized ratios can underflow to zero.",
      "Mukhtar et al. (2023), DOI10.1038/s41598-023-37570-7, eqs. 6–8. Verified against independent direct formulas using NetworkX cores/distances, exhaustive small-graph cores and Floyd-Warshall, a published focal calculation on a constructed consistent graph, and 100-digit mpmath clique identities. No author-code or epidemic-performance parity is claimed."),
  rec("Distance and closeness",
      "Exogenous Centrality", "exogenous",
      "Contribution of a node to the base centrality of all other nodes, measured by deleting it.",
      r"(E_i=\sum_{j\ne i}\left[C_G(j)-C_{G-i}(j)\right])",
      "`exogenous_base`, `mode`, `normalized`",
      "Bases are degree, betweenness and reverse_closeness (default). Reverse-closeness sums N minus finite hop distances and zero for unreachable partners; N stays the original input size after deletion. Betweenness contributions may be negative. Directed mode refers to the base direction; outgoing degree gives incoming exogenous degree. Weights are ignored, loops removed, parallel connections collapsed. Final max normalization retains signs. Costly tier.",
      "Everett & Borgatti (2010), DOI10.1016/j.socnet.2010.06.004, eqs. 3 and 8, sections 3.1–3.3. Independently checked against NetworkX base recomputation and explicit path enumeration. Some Florentine table entries remain inconsistent with the reconstructed graph; verification is of the stated definition, not full published-table or UCINET parity."),
  rec("Distance and closeness",
      "Improved Closeness Centrality", "improved_closeness",
      "Closeness adjusted for the number of shortest paths connecting each pair of nodes.",
      r"(ICC_i=\frac{n-1}{\sum_{j\ne i}d_{ij}/\sigma_{ij}^{\alpha}},\quad 0\le\alpha\le1)",
      "`icc_alpha`, `normalized`",
      "Multiple shortest paths reduce effective distances. Alpha defaults to 0.2; zero recovers ordinary normalized closeness on connected graphs, and trees are independent of alpha. Scores may exceed one. Uses the simple undirected skeleton and ignores weights. Disconnected graphs score all zero under a global infinite-distance convention; singleton zero is a cograph extension. Final max normalization is optional.",
      "Luan, Bao & Zhang (2021), DOI10.1007/s11424-021-0111-7, eq. 7. Verified using independent Python exact integer adjacency powers, NetworkX shortest-path enumeration, igraph alpha-zero closeness, and a closed-form layered graph with 2^1029 shortest paths. These checks establish numerical definition agreement, not author-code parity or spreading-performance superiority."),
  rec("Degree, strength and local connectivity",
      "Clustering Degree Algorithm", "cda",
      "Degree and strength adjusted by Barrat weighted clustering, plus weighted contributions from immediate neighbors.",
      r"(PC_i=CD_i+\sum_j\frac{w_{ij}}{w_{\max}}CD_j,\quad CD_i=\frac{\alpha d_i+(1-\alpha)s_i}{1+e^{-C_i^w}})",
      "`cda_alpha`, `weighted`, `simplify`",
      "Higher scores combine connectivity, clustering and neighbor contributions. Alpha defaults to 0.5; endpoints select strength or degree while preserving the weighted clustering and neighbor terms. The maximum weight is global across components. Weight units matter. Zero weights are absent edges; low-degree clustering and isolate scores are zero. Directed weighted arcs are summed into undirected weights; loops are removed.",
      "Wang et al. (2018), equations 2–6; igraph Barrat clustering and independently enumerated weighted neighbor pairs, checked across the alpha family on binary and weighted graphs."),

  rec("Degree, strength and local connectivity",
      "Extended Neighborhood Coreness", "extended_coreness",
      "The sum of neighbors' neighborhood-coreness scores, using core numbers from the original simple undirected graph.",
      r"(C_{nc+}(i)=\sum_{j\in N(i)}\sum_{l\in N(j)}k_s(l)=(A^2 k_s)_i)",
      "—",
      "Rewards access to core-rich neighborhoods. Every length-two walk contributes, including returns to the focal node and multiple walks reaching the same endpoint. Isolates score zero; on a regular graph of degree d it equals d cubed. Other inputs are projected to the simple undirected skeleton.",
      "Bae & Kim (2014); explicit equations 2 and 3 reproduced in Ma et al. (2016). Verified using NetworkX cores, common-neighbor walk counts and exhaustive subset-derived core numbers."),

  rec("Distance and closeness",
      "Extended Gravity Centrality", "extended_gravity",
      "The sum of immediate neighbors' raw gravity scores, with k-shell masses and hop distances.",
      r"(G^+(i)=\sum_{j\in N(i)}\sum_{l:0<d(j,l)\le r}\frac{k_s(j)k_s(l)}{d(j,l)^2})",
      "`gravity_radius`",
      "The radius applies around each neighbor, so contributions can reach one hop beyond the focal node's radius. Default r=3 follows the paper; zero gives zero and NULL or infinity includes all reachable partners. Auto is an explicit cograph heuristic. Uses the simple undirected skeleton, with k-shell masses fixed regardless of gravity_mass. Normalize only after summing raw neighbor scores.",
      "Ma, Ma, Zhang & Wang (2016), equations 6 and 7; independently checked using NetworkX core numbers and BFS distances across radii, plus an exhaustive core oracle on small graphs."),

  rec("Spectral, walk and influence",
      "Node Resistance Curvature", "resistance_curvature",
      "A geometric descriptor based on electrical resistance, evaluated separately within each connected component.",
      r"(p_i=1-\frac{1}{2}\sum_{j\sim i}w_{ij}R_{ij})",
      "`weighted`, `simplify`",
      "Low or negative curvature identifies tree-like junctions; higher values indicate redundant connections. Weights are conductances. Isolates score one, and raw scores sum to the component count. Weighted directed arcs are added into undirected conductances; unweighted inputs use the simple skeleton. Loops are removed. Dense electrical solves make this an explicitly requested costly measure. Normalization preserves negative values but changes the component-sum identity.",
      "Devriendt & Lambiotte (2022), definition 1, equation 2; NetworkX effective resistance and exhaustive conductance-weighted spanning-tree degree expectations."),

  rec("Spectral, walk and influence",
      "Dynamics-Sensitive Centrality", "dynamics_sensitive",
      "A finite-time linearized spreading score with explicit spreading and recovery rates, on the simple undirected skeleton.",
      r"(S(T)=\sum_{r=0}^{T-1}\beta A[\beta A+(1-\mu)I]^r\mathbf{1})",
      "`ds_beta`, `ds_mu`, `ds_steps`",
      "Higher scores indicate more cumulative spreading activity in this approximation. Values can exceed the node count and are not bounded infection probabilities. Defaults are beta=0.1, mu=1, T=5. Recovery mu=1 recovers finite diffusion; mu=0 selects the SI case. Isolates and horizon zero score zero; overflow raises an error.",
      "Liu et al. (2016), preprint equations 5 and 7; binomial expansion checked through NumPy adjacency powers and explicit walk enumeration over spreading, recovery and time parameters."),

  rec("Degree, strength and local connectivity",
      "Malatya Centrality", "malatya",
      "The sum of a node's degree divided by each neighbour's degree, calculated on the original simple undirected graph.",
      r"(M(i)=\sum_{j\in N(i)}\frac{d_i}{d_j})",
      "—",
      "Favours nodes with many low-degree neighbours. Isolates score zero. On nonisolated vertices the score is exactly the reciprocal of the bridging coefficient; on a regular graph it equals degree.",
      "Karci, Yakut & Oztemiz (2022), equation 1; independent NetworkX neighbour ratios and a separate reciprocal identity check."),

  rec("Spectral, walk and influence",
      "Finite-Horizon Diffusion Centrality", "diffusion_centrality",
      "Total weighted walks of lengths 1 through T starting at a node, allowing repeated visits and returns.",
      r"(DC(A;q,T) = \sum_{t=1}^{T}(qA)^t\mathbf{1})",
      "`diffusion_q`, `diffusion_steps`, `weighted`, `loops`, `simplify`",
      "High values indicate more weighted walk activity from the source. Probability interpretation requires entries of qA in [0,1]. Defaults q=1 and T=3 are cograph choices. Directed arcs carry information outwards; mode and path-weight inversion do not alter the result. Overflow raises an error.",
      "Banerjee et al. (2013, eq. 5; 2019, section 3.1.2); independent Python walk enumeration and NumPy matrix powers. T=1 gives q times outgoing strength; T=0 gives zero."),

  rec("Spectral, walk and influence",
      "Dynamical Importance", "dynamical_importance",
      "Relative loss of adjacency spectral radius after removing the node, recomputed directly for each deletion.",
      r"(I_i = \frac{\rho(A)-\rho(A_{-i})}{\rho(A)})",
      "`weighted`, `simplify`",
      "High values indicate a larger effect on the graph's spectral radius. Supports directed nonnegative weighted graphs and always removes loops. The ratio is undefined (NaN) if the original radius is zero. Repeated eigendecomposition is held back from the default all tier. This is the deletion definition, not the paper's eigenvector-product approximation.",
      "Restrepo, Ott & Hunt (2006, eq. 2); independent NumPy eigenspectra, exact SymPy characteristic polynomials for small binary graphs, and analytic clique/star/cycle examples."),

  rec("Neighbourhood structure and cohesion",
      "Maximal Clique Centrality", "mcc",
      "Sum of factorial contributions from maximal cliques containing the node, on the simple undirected skeleton.",
      r"(MCC(v) = \sum_{C\in\mathcal{M}(v),\,|C|\geq2} (|C|-1)!)",
      "—",
      "Larger cliques contribute much more than edges or triangles. Contained cliques are excluded. Isolates score 0 by explicit convention. Exponential enumeration is held back from the default all tier; raw-score overflow raises an error.",
      "Chin et al. (2014); NetworkX maximal cliques and independent exhaustive subset recognition on small graphs. No author-software parity claim."),

  rec("Degree, strength and local connectivity",
      "Volume Centrality", "volume",
      "The total original-graph degree inside a closed hop neighbourhood, including its centre.",
      r"(V_r(i) = \sum_{j:\,d(i,j)\leq r,\ d(i,j)<\infty} k_j)",
      "`volume_radius`",
      "Measures connectivity within and leaving the neighbourhood. Radius 0 gives degree, default 2 uses two hops, and infinite radius gives twice the component's edge count. Uses the simple undirected skeleton.",
      "Wehmuth & Ziviani (2011, eq. 1; 2013 DACCER); independently checked using NetworkX BFS neighbourhoods and full-graph degrees."),

  rec("Neighbourhood structure and cohesion",
      "Node Truss Number", "truss",
      "The largest truss number of an incident edge, on the simple undirected skeleton.",
      r"(t(v) = \max\{k : v \in V(T_k)\},\quad T_k:\ \text{each edge has at least } k-2\text{ triangles})",
      "—",
      "Higher values indicate triangle-supported cohesion. Tree vertices score 2, a k-clique scores k, and isolates score 0.",
      "Malliaros et al. (2016); exact comparison against NetworkX k_truss using the k-2 convention."),

  rec("Neighbourhood structure and cohesion",
      "Mixed Degree Decomposition", "mdd",
      "Shell thresholds from residual degree plus attenuated exhausted degree.",
      r"(k_i^{m} = k_i^{r} + \lambda k_i^{e})",
      "`mdd_lambda`",
      "Higher means membership of a stronger mixed-degree shell. Lambda 0 gives coreness; lambda 1 gives degree. Default 0.7; scores need not be integers.",
      "Zeng & Zhang (2013); exhaustive subset-threshold oracle independent of peeling, plus igraph coreness and degree limits."),

  rec("Neighbourhood structure and cohesion",
      "Bridging Coefficient", "bridging_coefficient",
      "The reciprocal-degree ratio before multiplication by betweenness.",
      r"(B(i) = \frac{1/k_i}{\sum_{j\in N(i)}1/k_j})",
      "—",
      "Higher values identify low-degree nodes adjacent to high-degree nodes. Isolates score 0. Uses the simple undirected skeleton.",
      "Hwang et al. (2006, eq. 3; 2008); independent Python evaluation using NetworkX neighbourhoods and degrees."),

  rec("Neighbourhood structure and cohesion",
      "Godfather Index", "godfather",
      "The number of unconnected unordered pairs of a node's neighbours.",
      r"(GF(i) = {k_i\choose 2} - t_i)",
      "—",
      "Higher values indicate more local brokerage opportunities. Here t_i counts focal triangles. Uses the simple undirected skeleton.",
      "Jackson (2020), section 3.2; Python neighbour-pair enumeration checks the production triangle-subtraction formula."),

  rec("Neighbourhood structure and cohesion",
      "Supported Relationships", "support",
      "The number of neighbours sharing at least one common neighbour with the node.",
      r"(S(i) = |\{j\in N(i):(A^2)_{ij}>0\}|)",
      "—",
      "Higher values mean more triangle-supported relationships; a relationship counts once even if several common neighbours support it. Uses the simple undirected skeleton.",
      "Jackson (2020), section 3.4; exact comparison to degrees in the NetworkX 3-truss."),


  ## ---- Family 1: Degree, strength and local connectivity ----
  rec("Degree, strength and local connectivity",
      "Degree Centrality", "degree",
      "Degree centrality counts the number of direct ties incident on a node. In directed graphs, it can be separated into incoming and outgoing ties.",
      r"(C_D(v) = \sum_{u \in V} a_{vu} = k_v)",
      r"(`mode`, `loops`)",
      "A high degree value indicates many direct observed connections. It is a local connectivity measure and does not imply brokerage or global reach.",
      r"(Equivalent to `igraph::degree()` under matching `mode` and loop settings.)"),

  rec("Degree, strength and local connectivity",
      "Indegree Centrality", "indegree",
      "Indegree counts ties pointing into a node under a directed interpretation.",
      r"(k_v^{\mathrm{in}} = \sum_{u \in V} a_{uv})",
      r"(—)",
      "A high indegree value indicates many incoming observed ties. Its substantive meaning depends on what edge direction represents.",
      r"(Equivalent to `igraph::degree(mode = "in")`.)"),

  rec("Degree, strength and local connectivity",
      "Outdegree Centrality", "outdegree",
      "Outdegree counts ties leaving a node under a directed interpretation.",
      r"(k_v^{\mathrm{out}} = \sum_{u \in V} a_{vu})",
      r"(—)",
      "A high outdegree value indicates many outgoing observed ties. In transition networks, this can mean many possible next states.",
      r"(Equivalent to `igraph::degree(mode = "out")`.)"),

  rec("Degree, strength and local connectivity",
      "Strength Centrality", "strength",
      "Strength centrality is weighted degree: it sums edge weights instead of counting edges.",
      r"(s(v) = \sum_{u \in V} w_{vu})",
      r"(`mode`)",
      "A high strength value indicates high total incident edge weight. This should be interpreted according to how weights were defined.",
      r"(Equivalent to `igraph::strength()` when weights are supplied.)"),

  rec("Degree, strength and local connectivity",
      "Instrength Centrality", "instrength",
      "Instrength sums incoming edge weights.",
      r"(s^{\mathrm{in}}(v) = \sum_{u \in V} w_{uv})",
      r"(—)",
      "A high instrength value indicates high total incoming weight. It is a weighted incoming-connectivity measure.",
      r"(Equivalent to `igraph::strength(mode = "in")`.)"),

  rec("Degree, strength and local connectivity",
      "Outstrength Centrality", "outstrength",
      "Outstrength sums outgoing edge weights.",
      r"(s^{\mathrm{out}}(v) = \sum_{u \in V} w_{vu})",
      r"(—)",
      "A high outstrength value indicates high total outgoing weight. It does not show whether that weight is concentrated or distributed.",
      r"(Equivalent to `igraph::strength(mode = "out")`.)"),

  rec("Degree, strength and local connectivity",
      "Expected Centrality", "expected",
      "Expected centrality sums the degrees of a node's neighbours.",
      r"(C_{\mathrm{exp}}(v) = \sum_{u \in N(v)} k_u)",
      r"(`mode`)",
      "A high value indicates adjacency to well-connected nodes.",
      r"(Implemented as a native neighbourhood centrality in `cograph`.)"),

  rec("Degree, strength and local connectivity",
      "Leverage Centrality", "leverage",
      "Leverage centrality compares a node's degree with the degrees of its neighbours.",
      r"(\ell(v) = \frac{1}{k_v} \sum_{u \in N(v)} \frac{k_v - k_u}{k_v + k_u})",
      r"(`mode`)",
      "A positive high value indicates that the node is more connected than its neighbours under this degree comparison.",
      r"(Validated against `centiserve::leverage()`.)"),

  rec("Degree, strength and local connectivity",
      "Lobby Centrality", "lobby",
      "Lobby centrality is the h-index of neighbour degrees.",
      r"(h(v) = \max\bigl\{ h : |\{ u \in \{v\} \cup N(v) : k_u \ge h \}| \ge h \bigr\})",
      r"(`mode`)",
      "A high value indicates many neighbours that themselves have reasonably high degree.",
      r"(Validated against `centiserve::lobby()`.)"),

  rec("Degree, strength and local connectivity",
      "H-Index Strength Centrality", "hindex_strength",
      "H-index strength is a weighted h-index-style neighbourhood measure.",
      r"(h_s(v) = \max\bigl\{ h : |\{ u \in \{v\} \cup N(v) : s(u) \ge h \}| \ge h \bigr\})",
      r"(`mode`)",
      "A high value indicates strong ties to neighbours meeting a weighted connectivity threshold.",
      r"(Equivalent to lobby centrality on unweighted graphs in package tests.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Local H-Index Centrality", "local_hindex",
      "Local h-index centrality iteratively applies h-index logic to local neighbourhoods.",
      r"(h^{(t+1)}(v) = \mathcal{H}\bigl(\{ h^{(t)}(u) : u \in N(v) \}\bigr), \quad h^{(0)}(v) = k_v)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates a locally robust neighbourhood position under the h-index updating rule.",
      r"(Implemented following local h-index centrality formulations and checked in package tests.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Semi-Local Centrality", "semilocal",
      "Semi-local centrality extends degree-like counting beyond immediate neighbours.",
      r"(C_{SL}(v) = \sum_{u \in N(v)} \sum_{w \in N(u)} \bigl| \{\, x : d(w, x) \le 2 \,\} \bigr|)",
      r"(`mode`)",
      "A high value indicates proximity to a locally well-connected neighbourhood.",
      r"(Validated against `centiserve::semilocal()`.)"),

  rec("Degree, strength and local connectivity",
      "ClusterRank Centrality", "clusterrank",
      "ClusterRank combines neighbour degree information with local clustering.",
      r"(C_{CR}(v) = c(v) \sum_{u \in N(v)} \bigl( k_u + 1 \bigr), \quad c(v) = \text{local clustering coefficient})",
      r"(`mode`)",
      "A high value indicates local connectedness adjusted for clustering-related redundancy.",
      r"(Validated against `centiserve::clusterrank()`.)"),

  rec("Degree, strength and local connectivity",
      "Collective Influence Centrality", "collective_influence",
      "Collective influence combines a node's excess degree with excess degree on a local boundary.",
      r"(\mathrm{CI}_\ell(v) = (k_v - 1) \sum_{u \,\in\, \partial B(v, \ell)} (k_u - 1), \quad \ell = 2)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates potential importance under the collective influence model.",
      r"(Based on Morone and Makse's collective influence formulation.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "MNC Centrality", "mnc",
      "Maximum neighbourhood component centrality is the size of the largest connected component in a node's neighbourhood.",
      r"(\mathrm{MNC}(v) = \max_{C \,\in\, \mathcal{C}(G[N(v)])} |C|)",
      r"(`mode`)",
      "A high value indicates that many neighbours belong to one connected local component.",
      r"(Validated against `centiserve::mnc()`.)"),

  rec("Degree, strength and local connectivity",
      "DMNC Centrality", "dmnc",
      "DMNC is a density-adjusted version of maximum neighbourhood component centrality.",
      r"(\mathrm{DMNC}(v) = \frac{E_c}{N_c^{\,\varepsilon}}, \quad \varepsilon = 1.7)",
      r"(`mode`, `dmnc_epsilon`)",
      "A high value indicates a large and dense local neighbour component under the chosen density exponent. Here $E_c$ and $N_c$ are the edges and nodes of the largest component of $G[N(v)]$.",
      r"(Lin et al. (2008). Not equal to `centiserve::dmnc()`: that implementation counts the component's edges in the wrong index space, so it disagrees on 14 of the 34 karate nodes even at a matched epsilon. See the "Divergence from centiserve" section of `?centrality_dmnc`.)"),

  rec("Degree, strength and local connectivity",
      "LAC Centrality", "lac",
      "LAC, or local average connectivity, measures connectivity in a node's neighbourhood.",
      r"(\mathrm{LAC}(v) = \frac{1}{k_v} \sum_{u \in N(v)} \deg_{G[N(v)]}(u))",
      r"(`mode`)",
      "A high value indicates that the node's neighbours form a relatively connected local structure.",
      r"(Corresponds to CytoHubba-style local average connectivity.)"),

  rec("Degree, strength and local connectivity",
      "Gravity Centrality", "gravity",
      "Gravity centrality treats each node's mass as attracting the mass of others over graph distance, and can be truncated at a radius.",
      r"(G(v) = \sum_{u \ne v,\; d(u,v) \le R} \frac{m_v\, m_u}{d(u, v)^2}, \quad m = \text{k-shell or degree})",
      r"(`mode`, `gravity_mass`, `gravity_radius`)",
      "A high value indicates proximity to massive nodes. The default is Ma et al.'s gravity centrality (k-shell mass, radius 3); `gravity_mass = \"degree\", gravity_radius = NULL` is Li et al.'s gravity model and `gravity_radius = \"auto\"` their local gravity model.",
      r"(Ma, Ma, Zhang & Wang (2016); Li, Ren, Ma, Liu, Zhang & Zhou (2019), eqs. 1, 2 and 5. Before 2.4.8 cograph summed $k_u\, ks(u)/d^2$ with no mass on the focal node, which matched no published formula; `gravity_mass = "legacy"` reproduces those values.)"),

  rec("Degree, strength and local connectivity",
      "Neighborhood Connectivity", "neighborhood_connectivity",
      "Neighborhood connectivity is the mean degree of a node's neighbours (average neighbour degree).",
      r"(C_{NC}(v) = \frac{1}{k_v} \sum_{u \in N(v)} k_u)",
      r"(`mode`)",
      "A high value indicates attachment to hubs. Isolates score 0. Direction is respected under `mode`.",
      r"(Equivalent to `igraph::knn(weights = NA)` (Maslov & Sneppen 2002); isolates return 0 instead of NaN.)"),

  rec("Degree, strength and local connectivity",
      "Entropy Variation, Degree", "entropy_variation_degree",
      "Entropy variation is the drop in the Shannon entropy of the degree distribution when the node and its links are removed.",
      r"(EnV_k(i) = I_k(G) - I_k(G - i), \quad I_k(G) = -\sum_j \frac{k_j}{\sum_l k_l} \ln \frac{k_j}{\sum_l k_l})",
      r"(`mode`)",
      "A high value indicates a node whose removal makes the remaining degree distribution more concentrated. Signed; negative values occur.",
      r"(Ai (2017), eqs. 5-10. Matches the author's R code path and the paper's Table 2 quantiles on its 4234-node network.)",
      via_measures = TRUE),

  rec("Degree, strength and local connectivity",
      "Flow Coefficient", "flow_coefficient",
      "The flow coefficient is the share of a node's neighbour pairs that are linked through the node but not directly.",
      r"(fc(v) = \frac{|\{(j, k) : j \to v \to k,\ j \not\to k\}|}{k_v (k_v - 1)})",
      r"(—)",
      "A high value indicates a node that mediates local flow. On an undirected graph it equals one minus the clustering coefficient.",
      r"(Honey, Kotter, Breakspear & Sporns (2007), as implemented in the Brain Connectivity Toolbox; matches `bctpy.flow_coef_bd` exactly.)"),

  rec("Degree, strength and local connectivity",
      "Local Entropy", "local_entropy",
      r"(Local entropy sums $-k \log k$ over a node's neighbours.)",
      r"(LE(v) = -\sum_{u \in N(v)} k_u \ln k_u)",
      r"(`mode`)",
      "Always non-positive; a lower (more negative) value indicates a larger, denser neighbourhood. Isolates score 0.",
      r"(Nie, Guo, Zhao & Lu (2016), as printed by the Zoo and by Omar & Plapper's 2021 survey; the article is closed access.)"),

  rec("Degree, strength and local connectivity",
      "Weighted h-index", "weighted_h_index",
      "The weighted h-index takes the h-index over topological link weights, each neighbour's weight repeated by its degree.",
      r"(h^w_v = H\big(\{k_v k_u \text{ repeated } k_u \text{ times} : u \in N(v)\}\big))",
      r"(`mode`)",
      "A high value indicates a node with many well-connected neighbours. Input edge weights play no role.",
      r"(Gao, Yu, Li, Shen & Gao (2019), eq. 3. Matches an independent implementation on 200 random graphs.)"),

  rec("Degree, strength and local connectivity",
      "Redundancy", "redundancy",
      "Redundancy is the mean degree of a node's neighbours inside its ego network.",
      r"(r(v) = \frac{2 t_v}{k_v} = k_v - \text{effective size}(v))",
      r"(—)",
      "A high value indicates neighbours that are connected to each other, so fewer structural holes.",
      r"(Burt (1992); Borgatti (1997). Reproduces Borgatti's worked example and equals degree minus effective size.)"),

  ## ---- Family 2: Distance and closeness ----
  rec("Distance and closeness",
      "Closeness Centrality", "closeness",
      "Closeness centrality summarises how short a node's paths are to other reachable nodes.",
      r"(C_C(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(`mode`)",
      "A high value indicates short graph distances to other nodes. In disconnected graphs, harmonic centrality may be easier to interpret.",
      r"(Equivalent to `igraph::closeness()` under matching `mode` and weight settings.)"),

  rec("Distance and closeness",
      "Incloseness Centrality", "incloseness",
      "Incloseness computes closeness over incoming directed paths.",
      r"(C_C^{\mathrm{in}}(v) = \frac{1}{\sum_{u \ne v} d(u, v)})",
      r"(—)",
      "A high value indicates that other nodes can reach the focal node through short directed paths.",
      r"(Equivalent to `igraph::closeness(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outcloseness Centrality", "outcloseness",
      "Outcloseness computes closeness over outgoing directed paths.",
      r"(C_C^{\mathrm{out}}(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(—)",
      "A high value indicates that the focal node can reach other nodes through short directed paths.",
      r"(Equivalent to `igraph::closeness(mode = "out")`.)"),

  rec("Distance and closeness",
      "Harmonic Centrality", "harmonic",
      "Harmonic centrality sums reciprocal shortest-path distances. Unreachable nodes contribute zero.",
      r"(C_H(v) = \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(`mode`)",
      "A high value indicates broad reach through short paths while handling disconnected components more gracefully than classical closeness.",
      r"(Equivalent to `igraph::harmonic_centrality()` under matching settings.)"),

  rec("Distance and closeness",
      "Inharmonic Centrality", "inharmonic",
      "Inharmonic centrality computes harmonic centrality over incoming directed paths.",
      r"(C_H^{\mathrm{in}}(v) = \sum_{u \ne v} \frac{1}{d(u, v)})",
      r"(—)",
      "A high value indicates that the node is reachable from many others through short directed paths.",
      r"(Equivalent to `igraph::harmonic_centrality(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outharmonic Centrality", "outharmonic",
      "Outharmonic centrality computes harmonic centrality over outgoing directed paths.",
      r"(C_H^{\mathrm{out}}(v) = \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(—)",
      "A high value indicates that many nodes can be reached from the focal node through short directed paths.",
      r"(Equivalent to `igraph::harmonic_centrality(mode = "out")`.)"),

  rec("Distance and closeness",
      "Residual Closeness Centrality", "residual_closeness",
      "Residual closeness sums $1 / 2^d$ over shortest-path distances (the focal node contributes $1$).",
      r"(C_R(v) = \sum_{u \in V} 2^{-d(v, u)})",
      r"(`mode`)",
      "A high value indicates many close reachable nodes with rapid distance decay.",
      r"(Validated against `centiserve::closeness.residual()`.)"),

  rec("Distance and closeness",
      "Dangalchev Closeness Centrality", "dangalchev",
      "Dangalchev closeness is the residual-closeness distance-decay measure.",
      r"(C_D(v) = \sum_{u \in V} 2^{-d(v, u)})",
      r"(`mode`)",
      "A high value indicates short-distance reach with distant nodes down-weighted.",
      r"(Implemented as the residual closeness equivalent used in `cograph`.)"),

  rec("Distance and closeness",
      "Generalized Closeness Centrality", "generalized_closeness",
      r"(Generalized closeness sums $\\alpha^d$, where $d$ is the shortest-path distance.)",
      r"(C_G(v) = \sum_{u \in V} \alpha^{\,d(v, u)}, \quad \alpha = 0.5)",
      r"(`mode`, `decay_parameter`)",
      "A high value indicates reach under the chosen distance-decay parameter.",
      r"(Corresponds to generalized distance-decay closeness formulations.)"),

  rec("Distance and closeness",
      "Harary Centrality", "harary",
      "Harary centrality sums inverse squared shortest-path distances.",
      r"(C_{\mathrm{Har}}(v) = \sum_{u \ne v} \frac{1}{d(v, u)^2})",
      r"(`mode`)",
      "A high value indicates many nearby reachable nodes, with distant nodes strongly down-weighted.",
      r"(Based on the Harary distance family.)"),

  rec("Distance and closeness",
      "Average Distance Centrality", "average_distance",
      "Average distance centrality summarises mean shortest-path distance from a node (the focal node's $d = 0$ term is included; the centiserve convention divides by $n + 1$).",
      r"(\bar{d}(v) = \frac{\sum_{u \in V} d(v, u)}{n + 1})",
      r"(`mode`)",
      "Lower values indicate shorter average graph distance. The direction of interpretation should be checked because it is a distance quantity.",
      r"(Validated against the corresponding `centiserve` average-distance measure.)"),

  rec("Distance and closeness",
      "Barycenter Centrality", "barycenter",
      "Barycenter centrality is the inverse of the sum of shortest-path distances.",
      r"(C_{\mathrm{Bary}}(v) = \frac{1}{\sum_{u \ne v} d(v, u)})",
      r"(`mode`)",
      "A high value indicates a small total distance to other reachable nodes.",
      r"(Validated against `centiserve::barycenter()`.)"),

  rec("Distance and closeness",
      "Wiener Centrality", "wiener",
      "Wiener centrality records total shortest-path distance from a node (unreachable pairs contribute zero).",
      r"(W(v) = \sum_{u \ne v} d(v, u))",
      r"(`mode`)",
      "Lower values indicate shorter total distance. It is better read as distance burden than influence.",
      r"(Based on the Wiener index distance formulation.)"),

  rec("Distance and closeness",
      "Lin Centrality", "lin",
      "Lin centrality combines reachable nodes and total distance to those nodes.",
      r"(C_{\mathrm{Lin}}(v) = \frac{|R(v)|^2}{\sum_{u \in R(v)} d(v, u)}, \quad R(v) = \{ u \ne v : d(v,u) < \infty \})",
      r"(`mode`)",
      "A high value indicates many reachable nodes through relatively short paths.",
      r"(Validated against `centiserve::lincent()`.)"),

  rec("Distance and closeness",
      "Decay Centrality", "decay",
      "Decay centrality sums reach discounted by distance (the focal node contributes $1$).",
      r"(C_{\delta}(v) = \sum_{u \in V} \delta^{\,d(v, u)}, \quad \delta = 0.5)",
      r"(`mode`, `decay_parameter`)",
      "A high value indicates access to many nodes, especially nearby nodes. The value depends on the decay parameter.",
      r"(Validated against `centiserve::decay()`.)"),

  rec("Distance and closeness",
      "Radiality Centrality", "radiality",
      "Radiality compares node distances to the graph diameter.",
      r"(\mathrm{Rad}(v) = \frac{\sum_{u \ne v} \bigl( \Delta + 1 - d(v, u) \bigr)}{n - 1})",
      r"(`mode`)",
      "A high value indicates short distances to others relative to overall graph diameter.",
      r"(Validated against `centiserve::radiality()`.)"),

  rec("Distance and closeness",
      "Gil-Schmidt Centrality", "gilschmidt",
      "Gil-Schmidt centrality sums reciprocal distances and normalises by graph size.",
      r"(C_{GS}(v) = \frac{1}{n - 1} \sum_{u \ne v} \frac{1}{d(v, u)})",
      r"(`mode`)",
      "A high value indicates broad reciprocal-distance access to the network.",
      r"(Validated against `sna` Gil-Schmidt style centrality.)"),

  rec("Distance and closeness",
      "Integration Centrality", "integration",
      "Integration centrality is a distance-based measure of how integrated a node is within the graph.",
      r"(\mathrm{Int}(v) = \sum_{u \ne v} \left( 1 - \frac{d(v, u) - 1}{d_{\max}} \right), \quad d(v,u) = d_{\max} + 1 \text{ if unreachable})",
      r"(`mode`)",
      "A high value indicates broad distance-based access to the network.",
      r"(Implemented as a native distance-based centrality in `cograph`.)"),

  rec("Distance and closeness",
      "Eccentricity Centrality", "eccentricity",
      "Eccentricity is the maximum shortest-path distance from a node to any reachable node.",
      r"(\varepsilon(v) = \max_{u \in V} d(v, u))",
      r"(`mode`)",
      "Lower eccentricity generally indicates smaller worst-case distance. A high value means at least one reachable node is far away.",
      r"(Equivalent to `igraph::eccentricity()`.)"),

  rec("Distance and closeness",
      "Ineccentricity Centrality", "ineccentricity",
      "Ineccentricity computes eccentricity over incoming directed paths.",
      r"(\varepsilon^{\mathrm{in}}(v) = \max_{u \in V} d(u, v))",
      r"(—)",
      "It summarises the largest directed distance from other nodes into the focal node.",
      r"(Equivalent to `igraph::eccentricity(mode = "in")`.)"),

  rec("Distance and closeness",
      "Outeccentricity Centrality", "outeccentricity",
      "Outeccentricity computes eccentricity over outgoing directed paths.",
      r"(\varepsilon^{\mathrm{out}}(v) = \max_{u \in V} d(v, u))",
      r"(—)",
      "It summarises the largest directed distance from the focal node to reachable others.",
      r"(Equivalent to `igraph::eccentricity(mode = "out")`.)"),

  rec("Distance and closeness",
      "Closeness Vitality", "closeness_vitality",
      r"(Closeness vitality measures how total network distance changes when a node is removed, using the Wiener index $W(G) = \\sum_{s, t} d(s, t)$.)",
      r"(\mathrm{CV}(v) = W(G) - W(G \setminus v))",
      r"(`mode`)",
      "A high value indicates that removing the node substantially changes shortest-path structure.",
      r"(Corresponds to NetworkX closeness vitality conventions.)"),

  rec("Distance and closeness",
      "Entropy Centrality", "entropy",
      "Entropy centrality measures the change in graph entropy associated with a node, from the distribution of finite shortest-path distances after the node is removed.",
      r"(H(v) = -\sum_{w} Y_w \log_2 Y_w, \quad Y_w = \frac{|\{ x : d(w, x) < \infty \}|}{\sum_{w'} |\{ x : d(w', x) < \infty \}|})",
      r"(`mode`)",
      "A high value indicates strong contribution under the graph entropy definition being used.",
      r"(Validated against `centiserve::entropy()`.)"),

  rec("Distance and closeness",
      "Centroid Centrality", "centroid",
      "Centroid centrality compares distance dominance between pairs of nodes.",
      r"(f(v, u) = \gamma(v, u) - \gamma(u, v), \quad \gamma(v, u) = |\{ w : d(v, w) < d(u, w) \}|, \quad C_{\mathrm{cen}}(v) = \min_{u \ne v} f(v, u))",
      r"(`mode`)",
      "A high value indicates a favourable position in pairwise distance comparisons.",
      r"(Implemented natively because some reference implementations have known edge-case issues.)"),

  rec("Distance and closeness",
      "Distance Entropy", "distance_entropy",
      "Distance entropy is the normalised Shannon entropy of a node's hop-distance profile, so it summarises the spread of distances where closeness summarises their mean.",
      r"(h(v) = -\frac{1}{\log(M_v - m_v + 1)} \sum_{k = m_v}^{M_v} p_k \log p_k, \quad p_k = \frac{n_k(v)}{R_v})",
      r"(`mode`)",
      "A high value (up to 1) indicates reach spread evenly across many network layers; 0 means every reachable node sits at the same distance. Hop counts only; weights are ignored.",
      r"(Stella & De Domenico (2018). The normaliser uses $M_v - m_v + 1$ distance values so the index is bounded by 1; the printed formula divides by $\log(M_v - m_v)$, which is undefined for two distinct distances.)"),

  rec("Distance and closeness",
      "Local Dimension", "local_dimension",
      "Local dimension is the growth exponent of the ball around a node: how fast the number of nodes within $r$ hops grows with $r$.",
      r"(D_v = \frac{d \ln B_v(r)}{d \ln r}, \quad B_v(r) = 1 + |\{u : d(v, u) \le r\}|, \; r = 1, \ldots, d_{\max}(v))",
      r"(`mode`)",
      r"(A low value indicates a node that reaches most of the network within a few hops, so lower is more influential. With a single radius the discretised derivative $r\, n_v(r) / B_v(r)$ is reported.)",
      r"(Pu et al. (2014). Reproduces the worked example of Wen & Deng (2019), 0.9231 for ring sizes 4, 5, 4, 4.)"),

  rec("Distance and closeness",
      "Local Information Dimensionality", "local_information_dimension",
      "Local information dimensionality replaces the ball count of local dimension by its Shannon information and grows the box only to half the node's eccentricity.",
      r"(D^I_v = -\frac{d I_v(l)}{d \ln l}, \quad I_v(l) = -p_v(l) \ln p_v(l), \; p_v(l) = \frac{B_v(l)}{n}, \; l = 1, \ldots, \lceil d_{\max}(v) / 2 \rceil)",
      r"(`mode`)",
      r"(A high value indicates a more influential node. With a single box size the discretised derivative $l (1 + \ln p_v(l))\, n_v(l) / n$ is reported.)",
      r"(Wen & Deng (2020), formula verified against hand-computed path and star values.)"),

  rec("Distance and closeness",
      "Access Information", "access_information",
      "Access information is the mean number of bits a map-less walker needs to reach every other node along shortest paths.",
      r"(A_i = \frac{1}{N} \sum_j S(i \to j), \quad S(i \to j) = -\log_2 \sum_{p(i, j)} \frac{1}{k_i} \prod_{l \in p,\, l \ne i, j} \frac{1}{k_l - 1})",
      r"(—)",
      "A low value indicates a node that reaches the network with few decisions. Hubs score high, because a walker leaving a hub has many links to choose from.",
      r"(Rosvall et al. (2005); Sneppen et al. (2005). Matches enumeration of all shortest paths and the papers' star and bipartite examples.)"),

  rec("Distance and closeness",
      "Hide Information", "hide_information",
      "Hide information is the mean number of bits the rest of the network needs to locate a node.",
      r"(H_i = \frac{1}{N} \sum_j S(j \to i))",
      r"(—)",
      "A high value indicates a hidden, peripheral node; hubs have low hide information.",
      r"(Rosvall et al. (2005); Sneppen et al. (2005). Matches enumeration of all shortest paths.)"),

  rec("Distance and closeness",
      "Local Dimension, Fixed Radius", "local_dimension_fixed",
      "The Silva-Costa local dimension is the discretised growth exponent of the ball around a node at one chosen radius.",
      r"(D_v(r) = \frac{r\, n_v(r)}{B_v(r)})",
      r"(`mode`, `ld_radius`)",
      "A structural descriptor rather than a ranking: higher means the neighbourhood is still growing fast at that radius. Nodes with eccentricity below the radius score 0.",
      r"(Silva & Costa (2013), eq. 4, at a fixed radius (default 2). Reproduces the paper's path-graph values.)"),

  rec("Distance and closeness",
      "Fuzzy Local Dimension", "fuzzy_local_dimension",
      "Fuzzy local dimension replaces the ball count by a Gaussian-weighted average and takes its log-log slope.",
      r"(N_v(r) = \frac{\sum_{d_{vu} \le r} e^{-d_{vu}^2 / r^2}}{|\{u : d_{vu} \le r\}|}, \quad FLD(v) = \frac{d \log N_v(r)}{d \log r})",
      r"(`mode`)",
      "A high value indicates a more influential node (the opposite orientation to the rest of the dimension family).",
      r"(Wen & Jiang (2019). Reproduces the paper's Table 1 (Krackhardt kite) and its karate-club top ten in order.)"),

  rec("Distance and closeness",
      "Local Volume Dimension", "local_volume_dimension",
      "Local volume dimension is the log-log slope of the total degree inside the ball around a node.",
      r"(V_v(l) = \sum_{d_{vu} \le l} k_u, \quad LVD(v) = \frac{d \ln V_v(l)}{d \ln l})",
      r"(`mode`)",
      "A low value indicates a more important node. The source article is closed access; the definition follows the authors' later preprint.",
      r"(Li & Deng (2021). No published per-node values exist; matches an independent implementation.)"),

  rec("Distance and closeness",
      "Heatmap Centrality", "heatmap",
      "Heatmap centrality is a node's farness minus the mean farness of its neighbours.",
      r"(C_{HM}(v) = f(v) - \frac{1}{k_v} \sum_{u \in N(v)} f(u))",
      r"(`mode`)",
      "A low (more negative) value indicates a more central node. Isolates are undefined.",
      r"(Duron (2020). Reproduces every value and the ranking of the paper's Table 1.)"),

  rec("Distance and closeness",
      "Geodesic k-path", "geodesic_kpath",
      "Geodesic k-path centrality counts the shortest paths of length at most $k$ that start at a node, with multiplicity.",
      r"(C_k(v) = \sum_{0 < d(v, u) \le k} \sigma(v, u))",
      r"(`mode`, `kpath_k`)",
      "A high value indicates many short geodesics leaving the node. Counting nodes instead of paths gives m-reach, which is what `centiserve::geokpath` computes.",
      r"(Borgatti & Everett (2006), p. 469. Matches full shortest-path enumeration.)"),

  rec("Distance and closeness",
      "k-path Census", "kpath",
      "The k-path census counts the simple paths of length at most $k$ that a node lies on, endpoints included.",
      r"(C_{kP}(v) = |\{\, P : |P| \le k,\; v \in P \,\}|)",
      r"(`mode`, `kpath_len`)",
      "A high value indicates a node embedded in many short walks, not only in shortest ones. Length 1 alone reproduces degree. Enumeration is exhaustive, so cost grows with the branching factor to the power $k$.",
      r"(Sade (1989). Matches the per-vertex counts of `sna::kpath.census()` for $k = 2$ and $k = 3$ on directed and undirected graphs.)"),

  rec("Distance and closeness",
      "Distance-weighted Fragmentation", "fragmentation",
      "Distance-weighted fragmentation asks how much worse the network communicates once a node is deleted.",
      r"(F_d(v) = 1 - \frac{\sum_{i \ne j \ne v} 1 / d_{ij}^{\,G - v}}{(n-1)(n-2)})",
      r"(`mode`)",
      "A high value indicates a node whose removal fragments the network or stretches its distances. A node inside a clique scores near 0.",
      r"(Borgatti (2006), eq. 4. Matches `keyplayer::fragment()` on unweighted graphs. Held back from `type = \"all\"`: it re-solves all-pairs shortest paths once per node.)"),

  rec("Distance and closeness",
      "Geodesic Power Closeness", "delta_closeness",
      "Geodesic power closeness raises every distance to a negative power, so one exponent moves the measure between a local and a global reading.",
      r"(c_\delta(i) = \frac{1}{n-1} \sum_{j \ne i} d_{ij}^{-\delta})",
      r"(`mode`, `closeness_delta`)",
      r"(A high value indicates a node close to many others. The exponent spans the family: $\delta = 1$ is harmonic centrality over $n-1$, $\delta = 2$ is the inverse-square sum, a large $\delta$ approaches degree, and $\delta = 0$ counts the reachable set. Unreachable nodes contribute nothing but stay in the denominator.)",
      r"(Agneessens, Borgatti & Everett (2017), eq. 2. Reproduces `harmonic` and `harary` exactly at $\delta$ = 1 and 2.)"),

  ## ---- Family 3: Shortest-path brokerage and flow ----
  rec("Shortest-path brokerage and flow",
      "Betweenness Centrality", "betweenness",
      "Betweenness centrality measures how often a node lies on shortest paths between other pairs of nodes.",
      r"(C_B(v) = \sum_{s \ne v \ne t} \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(—)",
      "A high value is consistent with a bridge or brokerage position under the shortest-path model. It is not direct evidence of intentional mediation.",
      r"(Equivalent to `igraph::betweenness()` under matching directedness, weights, and normalization conventions.)"),

  rec("Shortest-path brokerage and flow",
      "Stress Centrality", "stress",
      "Stress centrality counts shortest paths passing through a node without fractional normalization across tied paths.",
      r"(C_S(v) = \sum_{s \ne v \ne t} \sigma_{st}(v))",
      r"(—)",
      "A high value indicates that many shortest paths include the node.",
      r"(Validated against `sna::stresscent()`.)"),

  rec("Shortest-path brokerage and flow",
      "Load Centrality", "load",
      "Load centrality distributes shortest-path load across alternative shortest routes: at each branch point a unit packet is split evenly among next hops on shortest paths.",
      r"(C_L(v) = \sum_{s \ne v \ne t} \mathrm{load}_{st}(v))",
      r"(—)",
      "A high value indicates that a node carries a large share of geodesic routing load.",
      r"(Validated against `sna::loadcent()`.)"),

  rec("Shortest-path brokerage and flow",
      "Length-scaled Betweenness", "length_scaled_betweenness",
      "Length-scaled betweenness counts the same brokered pairs as betweenness but weights each pair by the reciprocal of its distance.",
      r"(C_{LS}(v) = \sum_{s \ne v \ne t} \frac{1}{d(s,t)} \cdot \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(—)",
      "A high value indicates brokerage between pairs that were already close, which ordinary betweenness treats the same as brokerage across the graph.",
      r"(Borgatti & Everett (2006); Brandes (2008), Algorithm 5. Matches a brute-force enumeration of weighted geodesic pairs on directed and undirected graphs.)"),

  rec("Shortest-path brokerage and flow",
      "Distance-decayed Betweenness", "delta_betweenness",
      "Distance-decayed betweenness discounts each brokered pair by a power of its distance, so the exponent tunes how local the measure is.",
      r"(C_\delta(v) = \sum_{s \ne v \ne t} (d(s,t) - 1)^{-\delta} \cdot \frac{\sigma_{st}(v)}{\sigma_{st}})",
      r"(`betweenness_delta`)",
      r"(A high value indicates brokerage concentrated among nearby pairs. At $\delta = 0$ the measure is ordinary betweenness. Adjacent pairs have no intermediary, so the singularity at $d = 1$ never arises.)",
      r"(Agneessens, Borgatti & Everett (2017). Matches brute force at three exponents and reproduces betweenness exactly at zero.)"),

  rec("Shortest-path brokerage and flow",
      "Ego Betweenness", "ego_betweenness",
      "Ego betweenness is betweenness computed inside a node's own ego network rather than across the whole graph.",
      r"(C_{EB}(v) = \sum_{i < j \in N(v),\; A_{ij} = 0} \frac{1}{(A^2)_{ij}})",
      r"(—)",
      "A high value indicates a node that brokers among its own neighbours, which is what an egocentric survey can measure. A node with fewer than two neighbours scores 0. It is close to Burt's effective size but is not a function of it.",
      r"(Everett & Borgatti (2005). Matches the paper's $A^2(1-A)$ shortcut and ordinary betweenness on the induced ego subgraph.)"),

  rec("Shortest-path brokerage and flow",
      "Bottleneck Centrality", "bottleneck",
      "Bottleneck centrality counts cases where a node is critical in shortest-path tree structures.",
      r"(\mathrm{BN}(v) = \sum_{s \in V} p_s(v), \quad p_s(v) = 1 \text{ if } v \text{ carries} > \tfrac{n}{4} \text{ of the shortest-path tree } T_s)",
      r"(`mode`)",
      "A high value indicates frequent bottleneck position in local shortest-path trees.",
      r"(Validated against `centiserve::bottleneck()`.)"),

  rec("Shortest-path brokerage and flow",
      "Bridging Centrality", "bridging",
      "Bridging centrality combines betweenness with a bridging coefficient.",
      r"(\mathrm{Br}(v) = C_B(v) \cdot \beta(v), \quad \beta(v) = \frac{1/k_v}{\sum_{u \in N(v)} 1/k_u})",
      r"(—)",
      "A high value indicates a possible bridge position between locally distinct areas.",
      r"(Based on bridging centrality formulations by Hwang and colleagues.)"),

  rec("Shortest-path brokerage and flow",
      "Local bridging (legacy degree product)", "local_bridging",
      "Inverse focal degree multiplied by the bridging coefficient.",
      r"(\mathrm{LBr}(v) = \frac{1}{k_v} \cdot \beta(v), \quad \beta(v) = \frac{1/k_v}{\sum_{u \in N(v)} 1/k_u})",
      r"(—)",
      "Retains the original cograph degree-only score. This formula uses degrees and does not calculate paths between neighbors.",
      "Legacy formula, not Nanda-Kotz localized bridging or Macker Extended LBC. Use localized_bridging or extended_local_bridging for those source-defined ego-betweenness products."),

  rec("Shortest-path brokerage and flow",
      "Percolation Centrality", "percolation",
      "Percolation centrality weights shortest-path brokerage by node states in a percolation process.",
      r"(\mathrm{PC}(v) = \frac{1}{n - 2} \sum_{s \ne v \ne t} \frac{\sigma_{st}(v)}{\sigma_{st}} \cdot \frac{x_s}{\sum_{i \ne v} x_i})",
      r"(`states`)",
      "A high value indicates state-dependent path importance under the supplied state vector $x$.",
      r"(Based on Piraveenan, Prokopenko, and Hossain's percolation centrality; equivalent to betweenness-like behavior when states are equal.)"),

  rec("Shortest-path brokerage and flow",
      "Flow Betweenness Centrality", "flow_betweenness",
      "Flow betweenness measures brokerage using maximum flow rather than only shortest paths.",
      r"(C_{FB}(v) = \sum_{s \ne v \ne t} f_{st}(v), \quad f_{st}(v) = \text{flow through } v \text{ in a max } s\text{-}t \text{ flow})",
      r"(—)",
      "A high value indicates importance for potential flow capacity between other nodes under the graph model.",
      r"(Validated against `sna::flowbet()`.)"),

  rec("Shortest-path brokerage and flow",
      "Current-Flow Betweenness Centrality", "current_flow_betweenness",
      "Current-flow betweenness measures how much electrical current between node pairs passes through a node.",
      r"(C_{CFB}(v) = \frac{1}{(n - 1)(n - 2)} \sum_{s \ne t} \tau_{st}(v), \quad \tau_{st}(v) = \text{current through } v)",
      r"(—)",
      "A high value indicates an intermediary position under an all-path current-flow model.",
      r"(Corresponds to NetworkX current-flow betweenness centrality.)"),

  rec("Shortest-path brokerage and flow",
      "Current-Flow Closeness Centrality", "current_flow_closeness",
      "Current-flow closeness uses electrical-network (effective-resistance) distances rather than only shortest paths.",
      r"(C_{CFC}(v) = \frac{n - 1}{\sum_{u \ne v} R_{vu}}, \quad R_{vu} = \text{effective resistance between } v \text{ and } u)",
      r"(—)",
      "A high value indicates closeness under an all-path flow model. It generally requires connected graphs.",
      r"(Corresponds to NetworkX current-flow closeness centrality.)"),

  rec("Shortest-path brokerage and flow",
      "Entropy Variation, Betweenness", "entropy_variation_betweenness",
      "Entropy variation of the betweenness distribution: the drop in its Shannon entropy when the node is removed.",
      r"(EnV_b(i) = I_b(G) - I_b(G - i))",
      r"(—)",
      "A high value indicates a node whose removal concentrates shortest-path traffic on fewer nodes. Betweenness is recomputed per removal.",
      r"(Ai (2017). Matches the author's R code path and the paper's Table 2 betweenness quantiles.)",
      via_measures = TRUE),

  ## ---- Family 4: Spectral, walk and influence ----
  rec("Spectral, walk and influence",
      "Eigenvector Centrality", "eigenvector",
      "Eigenvector centrality gives high scores to nodes connected to other high-scored nodes.",
      r"(A\,\mathbf{x} = \lambda_{\max}\,\mathbf{x}, \quad C_E(v) = x_v)",
      r"(—)",
      "A high value indicates embeddedness in a central neighbourhood. It should not be interpreted as influence unless the relation supports that interpretation.",
      r"(Equivalent to `igraph::eigen_centrality()`.)"),

  rec("Spectral, walk and influence",
      "PageRank Centrality", "pagerank",
      "PageRank is a damped random-walk centrality. Nodes score highly when a random walker reaches them often.",
      r"(\mathrm{PR}(v) = \frac{1 - \alpha}{n} + \alpha \sum_{u \,:\, u \to v} \frac{\mathrm{PR}(u)}{k_u^{\mathrm{out}}}, \quad \alpha = 0.85)",
      r"(`damping`, `personalized`)",
      "A high value indicates random-walk prominence under the chosen damping, direction, and weight conventions.",
      r"(Equivalent to `igraph::page_rank()` under matching parameters; original method by Page, Brin, Motwani, and Winograd.)"),

  rec("Spectral, walk and influence",
      "Authority Centrality", "authority",
      "Authority centrality is part of HITS. Authorities are nodes pointed to by good hubs.",
      r"(\mathbf{a} = A^{\top} \mathbf{h}, \quad \mathbf{h} = A\,\mathbf{a} \;\Rightarrow\; \mathbf{a} = \text{principal eigenvector of } A^{\top} A)",
      r"(—)",
      "A high value indicates incoming support from nodes that point to good authorities.",
      r"(Equivalent to `igraph::authority_score()`; based on Kleinberg's HITS algorithm.)"),

  rec("Spectral, walk and influence",
      "Hub Centrality", "hub",
      "Hub centrality is the HITS counterpart to authority. Hubs point to good authorities.",
      r"(\mathbf{h} = \text{principal eigenvector of } A\,A^{\top})",
      r"(—)",
      "A high value indicates outgoing ties to high-authority nodes.",
      r"(Equivalent to `igraph::hub_score()`; based on Kleinberg's HITS algorithm.)"),

  rec("Spectral, walk and influence",
      "SALSA Centrality", "salsa",
      "SALSA is a stochastic link-analysis method related to HITS for directed graphs.",
      r"(\mathbf{a} = \text{principal eigenvector of } A_c^{\top} A_r, \quad A_r, A_c = \text{row- and column-normalised } A)",
      r"(—)",
      "A high value indicates directed authority under the SALSA random-walk model.",
      r"(Validated against `centiserve::salsa()` where applicable.)"),

  rec("Spectral, walk and influence",
      "LeaderRank Centrality", "leaderrank",
      "LeaderRank is a PageRank-like directed ranking method that adds a ground node $g$ linked both ways to every node; the stationary random-walk mass on $g$ is then redistributed equally.",
      r"(\mathbf{s}^{*} = \text{stationary distribution of the walk on } G \cup \{g\}, \quad C(v) = s^{*}_v + \tfrac{1}{n} s^{*}_g)",
      r"(—)",
      "A high value indicates directed prestige under the LeaderRank model.",
      r"(Validated against `centiserve::leaderrank()` where applicable.)"),

  rec("Spectral, walk and influence",
      "Alpha Centrality", "alpha",
      "Alpha centrality is an eigenvector-like measure that includes exogenous input.",
      r"(\mathbf{x} = (I - \alpha A^{\top})^{-1} \mathbf{e})",
      r"(`mode`)",
      "A high value indicates recursive prominence under the chosen attenuation and exogenous assumptions.",
      r"(Equivalent to `igraph::alpha_centrality()` under matching parameters.)"),

  rec("Spectral, walk and influence",
      "Bonacich Power Centrality", "power",
      r"(Bonacich power centrality scores nodes using the centrality of their neighbours and a parameter $\\beta$ controlling dependence.)",
      r"(\mathbf{c}(\alpha, \beta) = \alpha (I - \beta A)^{-1} A\,\mathbf{1})",
      r"(`mode`)",
      "A high value indicates a favourable recursive position under the selected Bonacich parameterization.",
      r"(Equivalent to `igraph::power_centrality()` under matching parameters.)"),

  rec("Spectral, walk and influence",
      "Katz Centrality", "katz",
      "Katz centrality counts walks from all nodes to a focal node, attenuating longer walks.",
      r"(\mathbf{x} = (I - \alpha A^{\top})^{-1} \mathbf{1}, \quad \alpha = 0.1)",
      r"(`katz_alpha`)",
      "A high value indicates that many short and longer walks reach the node. The attenuation parameter must be valid for the graph.",
      r"(Validated against `igraph::alpha_centrality(exo = 1)` and NetworkX Katz centrality conventions.)"),

  rec("Spectral, walk and influence",
      "Hubbell Centrality", "hubbell",
      "Hubbell centrality is an input-output centrality where status is recursively reinforced through ties.",
      r"(\mathbf{x} = (I - w W)^{-1} \mathbf{1}, \quad w = 0.5,\; W = \text{weighted adjacency})",
      r"(`hubbell_weight`)",
      "A high value indicates recursive prominence under the chosen weight factor. Some parameter settings are not solvable.",
      r"(Based on Hubbell's input-output centrality.)"),

  rec("Spectral, walk and influence",
      "Subgraph Centrality", "subgraph",
      "Subgraph centrality measures participation in closed walks, with shorter closed walks weighted more strongly.",
      r"(\mathrm{SC}(v) = \sum_{k=0}^{\infty} \frac{(A^k)_{vv}}{k!} = (e^{A})_{vv})",
      r"(—)",
      "A high value indicates embeddedness in many closed walk structures.",
      r"(Equivalent to `igraph::subgraph_centrality()`; based on Estrada's formulation.)"),

  rec("Spectral, walk and influence",
      "Laplacian Centrality", "laplacian",
      "Laplacian centrality measures a node's contribution to the graph's Laplacian energy.",
      r"(C_L(v) = \frac{E_L(G) - E_L(G \setminus v)}{E_L(G)}, \quad E_L(G) = \sum_i \mu_i^2 \;\; (\mu_i = \text{Laplacian eigenvalues}))",
      r"(—)",
      "A high value indicates a large local structural contribution under the Laplacian energy definition.",
      r"(Matches NetworkX and `centiserve::laplacian()` conventions.)"),

  rec("Spectral, walk and influence",
      "Communicability Centrality", "communicability",
      "Communicability centrality uses the matrix exponential to summarise walk-based communication potential.",
      r"(C_{\mathrm{Comm}}(v) = \sum_{u \in V} (e^{A})_{vu})",
      r"(—)",
      "A high value indicates many walk-based routes to other nodes, with shorter walks weighted more strongly.",
      r"(Based on Estrada communicability.)"),

  rec("Spectral, walk and influence",
      "Communicability Betweenness Centrality", "communicability_betweenness",
      "Communicability betweenness measures walk-based communicability between other pairs through a node.",
      r"(C_{CB}(v) = \frac{1}{(n-1)(n-2)} \sum_{s \ne t \ne v} \frac{G_{st} - G_{st}^{(v)}}{G_{st}}, \quad G = e^{A})",
      r"(—)",
      "A high value indicates walk-based intermediary position, not limited to shortest paths. $G^{(v)}$ is computed with $v$ removed.",
      r"(Based on Estrada, Higham, and Hatano's communicability betweenness.)"),

  rec("Spectral, walk and influence",
      "Random Walk Centrality", "random_walk",
      "Random walk centrality uses expected random-walk access times rather than shortest-path distances.",
      r"(C_{RW}(v) = \frac{1}{\sum_{u \ne v} \tilde{m}_{vu}}, \quad \tilde{m}_{vu} = \tfrac{1}{2}\bigl( m_{vu} + m_{uv} \bigr))",
      r"(—)",
      "A high value indicates that the node is reached efficiently under a random-walk process. $m_{uv}$ is the mean first-passage time.",
      r"(Corresponds to random-walk centrality based on mean first-passage or resistance-distance formulations.)"),

  rec("Spectral, walk and influence",
      "Markov Centrality", "markov",
      "Markov centrality is based on mean first-passage times in a Markov process on the graph.",
      r"(C_{\mathrm{Mk}}(v) = \frac{1}{\frac{1}{n} \sum_{u} m_{uv}}, \quad m_{uv} = \text{mean first-passage time } u \to v)",
      r"(—)",
      "A high value indicates that the node is reached quickly on average under the Markov process.",
      r"(Validated against `centiserve::markovcent()`. This is *not* Friedkin's immediate effects centrality; see `iec` for that measure and for the two differences between them.)"),

  rec("Spectral, walk and influence",
      "Immediate Effects Centrality (IEC)", "iec",
      "Score a node by how quickly everyone else's influence reaches it, along a chain in which every actor also listens to itself.",
      r"(c_{IEC}(j)=\Bigl(\frac{\sum_{i \ne j} m_{ij}}{n-1}\Bigr)^{-1},\qquad \mathbf{M}=(\mathbf{I}-\mathbf{Z}+\mathbf{E}\mathbf{Z}_{dg})\operatorname{diag}(1/c),\qquad \mathbf{Z}=(\mathbf{I}-\mathbf{W}+\mathbf{1}c')^{-1})",
      "`normalized`",
      "Immediacy rather than reach. Friedkin's model sends opinion round a group along a row-stochastic matrix of interpersonal influence; an actor whose effects travel over long sequences of influence is more dependent on the people in between than one whose effects travel over short sequences, so the measure is the reciprocal of the mean length of the sequences that end at the node. Those mean lengths are the mean first passage times of the chain, so the sum runs down a column of M and a high score marks a node the rest of the network reaches fast. The influence matrix is built the way the source builds it, and the construction is not cosmetic: the diagonal of the adjacency matrix is set to one before each row is divided by its sum, so every actor gives itself the same weight it gives each neighbour, a specification the paper takes from French (1956). Its footnote says why the self-loop is there — a strong network with a positive diagonal must be aperiodic — and the paper gives the two-cycle counterexample that a zero diagonal admits. This is what separates the measure from cograph's older `markov`, which drops the self-loop and also divides by n rather than n - 1: the second difference is a constant factor and cannot reorder anything, the first can and does, and the two rank the nodes differently on 2 of the 21 connected five-node graphs. Both are kept, `markov` because existing results depend on it. A reducible influence chain is refused rather than extended. Without irreducibility the left eigenvector has one dimension per closed class, so it is not determined and the diagonal matrix of its reciprocals is undefined; worse, the closed form does not announce the failure, returning a perfectly finite number for a pair whose true mean first passage time is infinite. Rather than publish a finite wrong number, cograph tests the chain first and returns NA at every node with a warning that says why. In practice that means a connected undirected graph or a strongly connected directed one; a graph with an isolate, an edgeless graph and a digraph that is connected but not strongly connected are all NA, and so is a one-node graph, where the formula divides by n - 1 = 0. An empty graph returns no scores. Direction is kept, because the influence matrix is directed by construction and row i is what actor i attends to, so there is no in/out/all variant and mode, cutoff and weight inversion are ignored. Weights are dropped deliberately: the unit diagonal is calibrated against unit edges, so rescaling the weights would silently re-weight each actor's self-reliance against the network, and the source demonstrates only the binary case. Loops in the input are absorbed by the mandated diagonal and parallel edges collapse. Marked costly, since the score needs one reachability closure and two dense solves; normalized = TRUE max-scales the finished vector, the source stating no normalization.",
      r"(Friedkin (1991), American Journal of Sociology 96(6), 1478-1504, DOI 10.1086/229694, equation (9) on page 1485, equation (11) on page 1486, equation (20) on page 1489, and the construction of W with Table 1 on pages 1492-1494; the mean first passage form is Kemeny and Snell (1960), page 79. The paper is open access at the author's institutional deposit and the full text was read, but the deposit is a 600 dpi scan with no text layer, so every equation was read from rendered page images rather than extracted. The paper prints a complete numerical fixture, rare in this catalogue: Table 1 gives the measure to three decimals for every node of all 21 connected non-isomorphic five-node graphs, and all 105 printed values are reproduced, in the paper's own node order, with the two values it truncates rather than rounds identified explicitly instead of absorbed into a tolerance. The 105 printed values of the companion total effects column reproduce as well. Verified in addition against four independent references — the closed form with an eigendecomposition, a first-step route that never forms the eigenvector or the fundamental matrix at all, exact rational arithmetic, and 60-digit mpmath — and against four closed forms derived by hand for complete graphs, rings, stars and directed cycles.)"),

  rec("Spectral, walk and influence",
      "Second-Order Centrality", "second_order",
      "Second-order centrality summarises variability in random-walk return times.",
      r"(\mathrm{SO}(v) = \operatorname{sd}_{u}\bigl( m_{uv} \bigr))",
      r"(via `centrality(measures = ...)`)",
      "The statistic describes random-walk regularity rather than direct connectivity (lower is more central).",
      r"(Rank behavior is checked against NetworkX second-order centrality in package tests.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Information Centrality", "information",
      "Information centrality measures centrality through resistance-distance or information-flow ideas (Stephenson and Zelen).",
      r"(C_I(v) = \left( C_{vv} + \frac{T - 2 R_v}{n} \right)^{-1}, \quad C = (D - A + J)^{-1},\; T = \operatorname{tr} C,\; R_v = \textstyle\sum_j C_{vj})",
      r"(—)",
      "A high value indicates a central position under the information-flow model.",
      r"(Based on Stephenson and Zelen's information centrality.)"),

  rec("Spectral, walk and influence",
      "Nonbacktracking Centrality", "nonbacktracking",
      "Nonbacktracking centrality scores nodes using walks that do not immediately return along the edge just traversed (the Hashimoto matrix $B$).",
      r"(B_{(i \to j),\,(k \to l)} = \delta_{jk}\,(1 - \delta_{il}), \quad C(v) \propto \text{aggregated leading eigenvector of } B)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates walk-based prominence after reducing immediate backtracking inflation.",
      r"(Validated against NetworkX-style nonbacktracking behavior in package tests.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Diffusion Degree", "diffusion",
      "The default Kandhway-Kuri method adds the scaled degree of the focal node and its neighbours. On a simple undirected graph:",
      r"(DD(i) = \lambda\left(k_i + \sum_{j\in N(i)} k_j\right))",
      r"(`mode`, `lambda`, `diffusion_method`)",
      "High values indicate local connectivity through the node and its neighbours. With `diffusion_method = \"power_series\"` (automatic for TNA inputs), the function instead returns row sums of W + W^2 + ... + W^n. That variant fixes the horizon at n and does not use lambda or mode.",
      r"(Default diffusion degree is checked against `centiserve::diffusion()` on simple graphs; the power-series variant follows TNA conventions. The independently parameterized Banerjee measure is `diffusion_centrality`.)"),

  rec("Spectral, walk and influence",
      "Infection Centrality", "infection",
      "Infection centrality estimates spreading potential through infection-style self-avoiding walks with attenuation.",
      r"(\mathrm{Inf}(v) = \sum_{d=1}^{L} \beta^{\,d+1} (1 - \mu)^{d}\, w_d(v), \quad \beta = 0.8,\; \mu = 0,\; L = 6)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates a favourable position under the assumed infection process, not observed contagion. $w_d(v)$ counts length-$d$ self-avoiding walks from $v$.",
      r"(Implemented according to infection centrality formulas used in the network centrality literature.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Edge Percolated Component", "epc",
      "The edge percolated component averages the size of the component a node ends up in when edges survive at random.",
      r"(\mathrm{EPC}(v) = \frac{1}{R\,n} \sum_{r=1}^{R} |C_r(v)|, \quad \Pr(\text{edge survives}) = 1 - t)",
      r"(`epc_threshold`, `epc_runs`, `epc_seed`)",
      "A high value indicates a node that stays connected to a large share of the network under random link failure. The value is a Monte Carlo estimate; set `epc_seed` to make it reproducible.",
      r"(Lin et al. (2008), the cytoHubba EPC. Recovers the exact bond-percolation mean on small graphs. cytoHubba and `centiserve::epc()` divide by $n$ alone, so their number is `epc_runs` times this one. Held back from `type = \"all\"` because it is both costly and stochastic.)"),

  rec("Spectral, walk and influence",
      "VoteRank Centrality", "voterank",
      "VoteRank is an iterative voting algorithm for ranking spreader candidates: each round the highest-voted node is selected, its voting ability is zeroed, and its neighbours' voting abilities are reduced.",
      r"()",
      r"(—)",
      "A high value indicates early selection by the VoteRank rule. It is a heuristic model result, not observed spread.",
      r"(Corresponds to NetworkX VoteRank behavior.)"),

  rec("Spectral, walk and influence",
      "Expected Influence 1-Step", "expected_influence_1",
      "Expected influence 1-step sums signed edge weights adjacent to a node.",
      r"(\mathrm{EI}_1(v) = \sum_{u \in V} W_{vu}, \quad W = \text{signed weight matrix})",
      r"(`mode`)",
      "A high positive value indicates strong positive immediate signed connectivity. This is mainly meaningful for signed networks.",
      r"(Based on Robinaugh, Millner, and McNally's expected influence measure.)"),

  rec("Spectral, walk and influence",
      "Expected Influence 2-Step", "expected_influence_2",
      "Expected influence 2-step extends signed influence to one- and two-step paths.",
      r"(\mathrm{EI}_2(v) = \mathrm{EI}_1(v) + \sum_{u \in V} W_{vu}\,\mathrm{EI}_1(u))",
      r"(`mode`)",
      "A high positive value indicates positive signed connectivity through direct and indirect paths. Interpretation requires a signed network.",
      r"(Based on Robinaugh, Millner, and McNally's expected influence measure.)"),

  rec("Spectral, walk and influence",
      "Spanning Tree Centrality", "spanning_tree",
      "Spanning tree centrality summarises a node's contribution across spanning-tree structures via the Laplacian pseudoinverse $L^{+}$.",
      r"(\mathrm{ST}(v) = \frac{1}{L^{+}_{vv}}, \quad L^{+} = \text{Moore-Penrose pseudoinverse of } L)",
      r"(via `centrality(measures = ...)`)",
      "A high value indicates structural participation across many tree-like ways of connecting the graph.",
      r"(Based on matrix-tree theorem centrality formulations.)",
      via_measures = TRUE),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 1", "shapley_game1",
      "Shapley value of the node in the coalition game whose worth is the number of nodes a coalition covers within one hop.",
      r"(SV_1(v) = \sum_{u \in \{v\} \cup N(v)} \frac{1}{1 + k_u})",
      r"(—)",
      "A high value indicates a node whose presence adds much one-hop coverage to a typical coalition. Values sum to $n$.",
      r"(Michalak et al. (2013), game 1. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 2", "shapley_game2",
      "Shapley value in the game where a node is covered once at least $k$ coalition members are adjacent to it.",
      r"(SV_2(v) = \min\!\left(1, \frac{k}{1 + k_v}\right) + \sum_{u \in N(v)} \max\!\left(0, \frac{k_u - k + 1}{k_u (1 + k_u)}\right))",
      r"(`shapley_k`)",
      "A high value indicates a node that helps push many neighbours over the $k$-neighbour threshold. With $k = 1$ this is game 1.",
      r"(Michalak et al. (2013), game 2. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Shapley Value, Game 3", "shapley_game3",
      "Shapley value in the game where a coalition covers every node within a hop cutoff.",
      r"(SV_3(v) = \sum_{u \in \{v\} \cup N_d(v)} \frac{1}{1 + |N_d(u)|}, \quad N_d(u) = \{w : d(u, w) \le d_{cut}\})",
      r"(`shapley_cutoff`)",
      "A high value indicates a node that reaches many otherwise hard-to-reach nodes within the cutoff. With cutoff 1 this is game 1.",
      r"(Michalak et al. (2013), game 3. Equal to exact Shapley values from full coalition enumeration in package tests.)"),

  rec("Spectral, walk and influence",
      "Rumor Centrality", "rumor",
      "Rumor centrality counts the spreading orders that could have started at a node; on a general graph it is evaluated on the node's breadth-first tree.",
      r"(\log R(v) = \log N! - \sum_{u} \log T^v_u)",
      r"(—)",
      "A high value indicates a plausible origin of a spread, typically a node near the centre. Returned on the log scale.",
      r"(Shah & Zaman (2011), eq. 24. Reproduces the paper's Fig. 5 values and brute-force spreading-order counts on trees.)"),

  rec("Spectral, walk and influence",
      "DegreeDiscountIC", "degree_discount",
      "DegreeDiscountIC is the greedy seed-selection order under degree discounting for the independent-cascade model.",
      r"(dd_v = d_v - 2 t_v - (d_v - t_v)\, t_v\, p)",
      r"(`discount_p`)",
      "A high score indicates an early selection: the first node selected scores 1, the last $1/n$. Ties follow node order.",
      r"(Chen, Wang & Yang (2009), Algorithm 4. Selection order matches an independent implementation on random graphs and the karate club.)"),

  rec("Spectral, walk and influence",
      "SingleDiscount", "single_discount",
      "SingleDiscount is the greedy seed-selection order where each neighbour of a new seed discounts its degree by one.",
      r"(dd_v = d_v - t_v)",
      r"(—)",
      "A high score indicates an early selection. Equivalent to repeatedly removing the highest-degree node.",
      r"(Chen, Wang & Yang (2009). Selection order matches an independent implementation and the node-removal formulation.)"),

  rec("Spectral, walk and influence",
      "NCVoteRank", "ncvoterank",
      "NCVoteRank is VoteRank with each voter's ability weighted by its normalised neighbourhood coreness, and two-hop weakening after each election.",
      r"(s_u = \sum_{v \in N(u)} va_v \,[\theta + (1 - \theta)\, nc_v])",
      r"(`ncvote_theta`)",
      r"(A high score indicates an early election. With $\theta = 1$ and no two-hop weakening this is VoteRank.)",
      r"(Kumar & Panda (2020), as restated by the Centrality Zoo and three later papers; the original article was not obtainable. VoteRank limit reproduces `networkx.voterank`.)"),

  rec("Spectral, walk and influence",
      "WVoteRank", "wvoterank",
      "WVoteRank is VoteRank for weighted graphs: votes are weighted by edge weight and the score takes a square root.",
      r"(s_v = \sqrt{k_v \sum_{u \in N(v)} va_u w_{vu}})",
      r"(—)",
      r"(A high score indicates an early election. Neighbours of an elected node lose $1/\langle w \rangle$, with $\langle w \rangle$ the average strength.)",
      r"(Sun, Chen, He & Ch'ng (2019). Reproduces all sixty numbers of the paper's Figure 1.)"),

  rec("Spectral, walk and influence",
      "EnRenew", "enrenew",
      "EnRenew elects the node whose neighbours supply the most entropy, then renews the entropies around it.",
      r"(E_v = \sum_{u \in N(v)} -p_{uv} \ln p_{uv}, \quad p_{uv} = \frac{k_u}{\sum_{l \in N(v)} k_l})",
      r"(`enrenew_depth`)",
      r"(A high score indicates an early election. Terms within the renewal radius are scaled by $1 - 1/(2^{d-1} \ln\langle k \rangle)$.)",
      r"(Guo, Yang, Guo, Pan & Chen (2020), eq. 1 and Algorithm 1. Reproduces the paper's Figure 1.)"),

  rec("Spectral, walk and influence",
      "VoteRank++", "voterank_plus",
      "VoteRank++ starts abilities from degree, splits votes in proportion to neighbour degree, and suppresses abilities multiplicatively after each election.",
      r"(s_v = \sqrt{k_v \sum_{u \in N(v)} va_u\, w_{u \to v}}, \quad va_v^{(0)} = \ln(1 + k_v / k_{\max}))",
      r"(`voterank_lambda`)",
      r"(A high score indicates an early election. Abilities are multiplied by $\lambda$ one step away and $\sqrt{\lambda}$ two steps away.)",
      r"(Liu, Li, Fang & Yao (2021). Matches the authors' released code exactly; the article is closed access.)"),

  rec("Spectral, walk and influence",
      "Node Contraction", "node_contraction",
      "Node contraction importance measures how much the network's cohesion rises when a node and its neighbours are merged into one.",
      r"(IMC(v) = 1 - \frac{\partial(G)}{\partial(G_v)}, \quad \partial(G) = \frac{1}{N \bar{L}})",
      r"(—)",
      "A high value indicates a node whose contraction shortens paths most. Reproduces the paper's Table 1 and the path-graph closed forms.",
      r"(Tan, Wu & Deng (2006), as restated by Wang et al. (2011), eqs. 1-3.)"),

  rec("Spectral, walk and influence",
      "Improved Node Contraction", "node_contraction_improved",
      "Improved node contraction adds the contraction scores of a node's edges, computed on the line graph.",
      r"(IIMC(v) = \alpha\, IMC(v) + \beta \sum_{e \ni v} IMC_{L(G)}(e), \quad \alpha / \beta = 5)",
      r"(`contraction_rho`)",
      "A high value indicates a node that is important both itself and through its edges. Not bounded by 1.",
      r"(Wang et al. (2011), eq. 4. Reproduces the paper's Table 1 with $\alpha + \beta = 1$.)"),

  rec("Spectral, walk and influence",
      "Two-Way Random Walk Betweenness", "two_way_rw",
      "Two-way random walk betweenness counts, over all node pairs, how often a node lies on the most likely two-step out-and-back route.",
      r"(T_{ij}[t, k] = P_{itj} P_{jki}, \quad P_{itj} = \frac{w_{it} w_{tj}}{d_i d_j})",
      r"(—)",
      "A high count indicates a node on many dominant two-way routes; nodes on none score 0. Cost grows as $n^4$.",
      r"(Curado, Rodriguez, Tortosa & Vicent (2022). Reproduces the paper's toy example exactly.)"),

  ## ---- Family 5: Neighbourhood structure and cohesion ----
  rec("Neighbourhood structure and cohesion",
      "Transitivity Centrality", "transitivity",
      "Transitivity measures local clustering: whether a node's neighbours are connected to each other.",
      r"(c(v) = \frac{2\, t_v}{k_v (k_v - 1)}, \quad t_v = \text{number of triangles through } v)",
      r"(`transitivity_type`, `isolates`)",
      "A high value indicates locally closed neighbourhoods. This can represent cohesion or redundancy, depending on the relation.",
      r"(Equivalent to `igraph::transitivity()` for standard types; `cograph` also supports weighted variants.)"),

  rec("Neighbourhood structure and cohesion",
      "Constraint Centrality", "constraint",
      "Constraint measures how redundant a node's contacts are, following Burt's structural holes framework.",
      r"(C(v) = \sum_{u \in N(v)} \left( p_{vu} + \sum_{q \ne v, u} p_{vq}\, p_{qu} \right)^2, \quad p_{vu} = \text{proportional tie strength})",
      r"(—)",
      "A high value indicates a locally constrained ego network. Lower constraint may indicate structural holes, depending on theory and relation type.",
      r"(Equivalent to `igraph::constraint()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Effective Size Centrality", "effective_size",
      "Effective size estimates the number of nonredundant contacts in a node's ego network (Burt).",
      r"(\mathrm{ES}(v) = k_v - \frac{1}{k_v} \sum_{u \in N(v)} |N(v) \cap N(u)|)",
      r"(—)",
      "A high value indicates relatively nonoverlapping contacts.",
      r"(Validated against `influenceR::effective_size()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Topological Coefficient Centrality", "topological_coefficient",
      "Topological coefficient centrality measures shared-neighbour overlap.",
      r"(T(v) = \frac{\operatorname{avg}_{u}\, J(v, u)}{k_v}, \quad J(v, u) = \text{number of neighbours shared by } v \text{ and } u)",
      r"(—)",
      "A high value indicates neighbourhood overlap or topological similarity.",
      r"(Validated against `centiserve::topocoefficient()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Diversity Centrality", "diversity",
      "Diversity centrality measures entropy in the distribution of edge weights around a node.",
      r"(\mathrm{Div}(v) = \frac{-\sum_{u \in N(v)} p_{vu} \log_2 p_{vu}}{\log_2 k_v}, \quad p_{vu} = \frac{w_{vu}}{\sum_{u'} w_{vu'}})",
      r"(—)",
      "A high value indicates that weighted ties are relatively evenly distributed rather than concentrated.",
      r"(Validated against `igraph::diversity()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Cross-Clique Centrality", "cross_clique",
      "Cross-clique centrality counts how many cliques contain a node.",
      r"(X(v) = |\{\, Q \in \mathcal{Q}(G) : v \in Q \,\}|, \quad \mathcal{Q}(G) = \text{set of cliques})",
      r"(—)",
      "A high value indicates participation in many fully connected local groups.",
      r"(Validated against `centiserve::crossclique()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Coreness Centrality", "coreness",
      "Coreness assigns nodes to k-core shells.",
      r"(C_{\mathrm{core}}(v) = \max \{\, k : v \in (k\text{-core of } G) \,\})",
      r"(`mode`)",
      "A high value indicates membership in a dense core. It does not imply brokerage or short paths to all nodes.",
      r"(Equivalent to `igraph::coreness()`.)"),

  rec("Neighbourhood structure and cohesion",
      "Onion Centrality", "onion",
      "Onion centrality assigns nodes to layers from onion decomposition, a fine-grained extension of k-core decomposition.",
      r"(\text{layer}(v) = \text{iteration index at which } v \text{ is peeled by the onion decomposition})",
      r"(via `centrality(measures = ...)`)",
      "A high layer indicates that the node remains until later stages of the peeling process.",
      r"(Validated against NetworkX onion layer behavior in package tests.)",
      via_measures = TRUE),

  rec("Neighbourhood structure and cohesion",
      "K-Reach Centrality", "kreach",
      "K-reach centrality counts nodes reachable within path length $k$.",
      r"(C_{kR}(v) = |\{\, u : 0 < d(v, u) \le k \,\}|, \quad k = 3)",
      r"(`mode`, `k`)",
      "A high value indicates broad reach within a fixed local radius. Results depend on the chosen $k$.",
      r"(Validated against k-path reach conventions.)"),

  rec("Neighbourhood structure and cohesion",
      "s-shell Index", "s_shell",
      "The s-shell index peels the graph by node strength built from asymmetric topological link weights, generalising k-shell.",
      r"(w_{ij} = 1 + (k_i\, k^{out}_j)^a, \quad s_i = \sum_{j \in N(i)} w_{ij})",
      r"(`s_shell_a`)",
      "A high shell index indicates a node deep in the strength-based core. With $a = 0$ the shells are the dense ranks of k-core.",
      r"(Liu, Tang, Do & Hui (2017). Each peeled shell equals the complement of the maximal subgraph with strength above the threshold; $a = 0$ reproduces k-core ranks.)"),

  rec("Neighbourhood structure and cohesion",
      "Weighted k-shell", "weighted_kshell",
      "The weighted k-shell peels the graph by a generalised degree that mixes degree and strength.",
      r"(k'_v = \big(k_v^{\alpha} s_v^{\beta}\big)^{1 / (\alpha + \beta)})",
      r"(`wks_alpha`, `wks_beta`)",
      "A high shell index indicates a node deep in the weighted core. Unit weights give the k-core number.",
      r"(Garas, Schweitzer & Havlin (2012), eq. 1 with their weight normalisation. Reproduces the paper's Figure 1 example and Table 2 core size.)"),

  rec("Neighbourhood structure and cohesion",
      "Renewed Coreness", "renewed_coreness",
      "Renewed coreness is the k-core number after removing links that lead nowhere new.",
      r"(D_{ij} = \frac{|N(j) \setminus N[i]| + |N(i) \setminus N[j]|}{2}, \quad \text{keep } D_{ij} \ge 2)",
      r"(`renewed_threshold`)",
      "A high value indicates a core node whose links reach beyond shared neighbourhoods. A clique with no outside links scores 0.",
      r"(Liu, Tang, Zhou & Do (2015). Reproduces the paper's Figure 1 and all twelve percentages of its Table S1.)"),

  rec("Neighbourhood structure and cohesion",
      "s-core Index", "s_core",
      "The s-core index is the weighted k-core: the largest strength threshold whose core still contains the node.",
      r"(s\text{-core}(s) = \text{maximal } H \subseteq G \text{ with } s_i^H \ge s \;\; \forall i \in H)",
      r"(—)",
      "A high value indicates a node deep in the strength-based core. Unit weights give the k-core number exactly.",
      r"(Eidsaa & Almaas (2013). Matches `igraph::coreness()` on unweighted graphs and a brute-force reading of the definition on weighted ones; `brainGraph::s_core()` reports the peeling round instead.)"),

  rec("Neighbourhood structure and cohesion",
      "Local Efficiency", "local_efficiency",
      "Local efficiency is how well a node's neighbours still communicate once the node itself is gone, using only the links among them.",
      r"(E_{loc}(v) = \frac{1}{k_v (k_v - 1)} \sum_{i \ne j \in N(v)} \frac{1}{d_{ij}^{\,G_v}})",
      r"(`mode`)",
      "A high value indicates a fault-tolerant neighbourhood; a node whose neighbours are mutually unconnected scores 0. Note that `igraph::local_efficiency()` measures those distances through the rest of the network instead, so it reports larger values.",
      r"(Latora & Marchiori (2001). Matches `brainGraph::efficiency(type = \"local\")` and the networkx induced-subgraph form.)"),

  ## ---- Family 6: Directed prestige and hierarchy ----
  rec("Directed prestige and hierarchy",
      "Prestige Domain Centrality", "prestige_domain",
      "Prestige domain centrality counts how many nodes can reach a focal node in a directed graph.",
      r"(P(v) = |\{\, u \ne v : u \rightsquigarrow v \,\}|)",
      r"(—)",
      "A high value indicates a large incoming reach domain.",
      r"(Based on Wasserman-Faust prestige concepts and `sna`-style prestige measures.)"),

  rec("Directed prestige and hierarchy",
      "Prestige Domain Proximity Centrality", "prestige_domain_proximity",
      "Prestige domain proximity measures how close nodes in the prestige domain are to the focal node.",
      r"(C(v) = \frac{|R^{-}(v)|^2}{(n - 1) \sum_{u \in R^{-}(v)} d(u, v)}, \quad R^{-}(v) = \{ u \ne v : u \rightsquigarrow v \})",
      r"(—)",
      "A high value indicates that many predecessors can reach the node through short directed paths.",
      r"(Based on Wasserman-Faust prestige proximity concepts.)"),

  rec("Directed prestige and hierarchy",
      "Local Reaching Centrality", "reaching_local",
      "Local reaching centrality measures how much of the network is reachable from a node through directed paths.",
      r"(\mathrm{LRC}(v) = \frac{|\{\, u : v \rightsquigarrow u \,\}|}{n - 1})",
      r"(`mode`)",
      "A high value indicates broad directed reach from the node.",
      r"(Matches `networkx.local_reaching_centrality` in package equivalence tests.)"),

  rec("Directed prestige and hierarchy",
      "Pairwise Disconnectivity Centrality", "pairwisedis",
      "Pairwise disconnectivity measures how directed reachability between pairs changes when a node is removed.",
      r"(\mathrm{Dis}(v) = \frac{P(G) - P(G \setminus v)}{P(G)}, \quad P(G) = |\{ (s, t) : s \rightsquigarrow t \}|)",
      r"(—)",
      "A high value indicates structural importance for preserving directed reachability.",
      r"(Validated against reference implementations in package tests.)"),

  rec("Directed prestige and hierarchy",
      "Trophic Level Centrality", "trophic_level",
      "Trophic level estimates hierarchical position in a directed flow network.",
      r"((I - W)\,\mathbf{s} = \mathbf{1}, \quad W_{ji} = \frac{a_{ij}}{k_j^{\mathrm{in}}}, \quad \text{basal nodes have level } 1)",
      r"(via `centrality(measures = ...)`)",
      "A higher value indicates a higher position in the inferred directed hierarchy. This is appropriate only for flow-like relations.",
      r"(Checked against NetworkX trophic-level behavior in package tests.)",
      via_measures = TRUE),

  ## ---- Family 7: Community and group-based ----
  rec("Community and group-based",
      "Participation Coefficient", "participation",
      "Participation coefficient measures how evenly a node's ties are distributed across communities.",
      r"(P(v) = 1 - \sum_{m} \left( \frac{k_v^{(m)}}{k_v} \right)^2, \quad k_v^{(m)} = \text{ties from } v \text{ to module } m)",
      r"(`membership`, `mode`)",
      "A high value indicates ties spread across multiple communities. It requires a meaningful membership vector.",
      r"(Validated against `brainGraph` participation coefficient conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Within-Module Z Centrality", "within_module_z",
      "Within-module z centrality standardises a node's within-community degree against other nodes in the same community.",
      r"(z(v) = \frac{k_v^{(m_v)} - \mu_{m_v}}{\sigma_{m_v}}, \quad m_v = \text{community of } v)",
      r"(`membership`, `mode`)",
      "A high value indicates unusually high within-module connectivity.",
      r"(Validated against `brainGraph` within-module z-score conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Gateway Centrality", "gateway",
      "Gateway centrality measures inter-community brokerage weighted by centrality of communities or nodes involved.",
      r"(g(v) = 1 - \frac{1}{k_v^2} \sum_{s} k_{vs}^2\, \gamma_{vs}^2, \quad k_{vs} = \text{ties from } v \text{ to module } s)",
      r"(`membership`, `mode`)",
      "A high value indicates a structurally prominent position between communities.",
      r"(Validated against `brainGraph::gateway()` conventions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Coordinator Centrality", "brokerage_coordinator",
      r"(Coordinator brokerage occurs when a node mediates between two nodes in its own group. It counts open directed two-paths $a \\to v \\to c$ (with no direct $a \\to c$).)",
      r"(\mathrm{Coord}(v) = |\{\, a \to v \to c : g(a) = g(v) = g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates within-group mediation under the supplied membership vector.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Itinerant Centrality", "brokerage_itinerant",
      "Itinerant brokerage occurs when a node mediates between two nodes in another group.",
      r"(\mathrm{Itin}(v) = |\{\, a \to v \to c : g(a) = g(c) \ne g(v) \,\}|)",
      r"(`membership`)",
      "A high value indicates brokerage among members outside the node's own group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Representative Centrality", "brokerage_representative",
      "Representative brokerage occurs when a node mediates from its own group to another group.",
      r"(\mathrm{Rep}(v) = |\{\, a \to v \to c : g(a) = g(v) \ne g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates outward brokerage from the node's group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Gatekeeper Centrality", "brokerage_gatekeeper",
      "Gatekeeper brokerage occurs when a node mediates from another group into its own group.",
      r"(\mathrm{Gate}(v) = |\{\, a \to v \to c : g(a) \ne g(v) = g(c) \,\}|)",
      r"(`membership`)",
      "A high value indicates inward brokerage into the node's group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Brokerage Liaison Centrality", "brokerage_liaison",
      "Liaison brokerage occurs when a node mediates between two groups, neither of which is its own.",
      r"(\mathrm{Liai}(v) = |\{\, a \to v \to c : g(a),\, g(v),\, g(c) \text{ all distinct} \,\}|)",
      r"(`membership`)",
      "A high value indicates between-group brokerage outside the node's own group.",
      r"(Based on Gould-Fernandez brokerage roles.)",
      grp = TRUE),

  rec("Community and group-based",
      "Modularity Vitality", "modularity_vitality",
      "Modularity vitality is the drop in Newman modularity when a node is deleted and the remaining nodes keep their communities.",
      r"(V_Q(v) = Q(G, C) - Q(G - v,\; C \setminus \{v\}))",
      r"(`membership`)",
      "A positive value indicates a community hub; a negative value indicates a bridge whose removal sharpens the partition. Weighted and directed graphs use the corresponding modularity.",
      r"(Magelinski, Bartulovic & Carley (2021). Matches brute-force `igraph::modularity()` after vertex deletion on random directed, undirected and weighted graphs.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community Hub-Bridge", "community_hub_bridge",
      "Community hub-bridge scores nodes that are hubs inside their community and bridges between communities.",
      r"(CHB(v) = |C_v|\, k^{intra}_v + NNC_v\, k^{inter}_v)",
      r"(`membership`, `mode`)",
      "A high value indicates a node with many intra-community links in a large community and links into several other communities.",
      r"(Ghalmane, El Hassouni & Cherifi (2019), eqs. 2-4, raw form. Matches an independent implementation on random partitions.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community-Based Centrality", "community_based",
      "Community-based centrality weights every link of a node by the size of the community it lands in.",
      r"(CbC(v) = \frac{1}{N} \sum_w d_{vw} S_w)",
      r"(`membership`, `mode`)",
      "A high value indicates many links into large communities. No tuning parameter.",
      r"(Zhao, Wang, Zhang & Zhu (2015), eq. 1. Reproduces the paper's Table 1 and Table 1 of Tulu et al. (2018).)",
      grp = TRUE),

  rec("Community and group-based",
      "Comm Centrality", "comm_centrality",
      "Comm centrality combines a node's scaled intra-community degree with the square of its scaled inter-community degree, weighted by how outward-looking its community is.",
      r"(CC(v) = (1 + \mu_C)\,\frac{k^{in}_v}{\max_{u \in C} k^{in}_u} R + (1 - \mu_C)\left(\frac{k^{out}_v}{\max_{u \in C} k^{out}_u} R\right)^2)",
      r"(`membership`, `mode`, `comm_r`)",
      "A high value indicates a node that is central within its community and well linked outside it. $R$ defaults to the community's maximum intra-degree.",
      r"(Gupta, Singh & Cherifi (2016), eqs. 3-4. Matches an independent implementation; the paper prints no per-node values.)",
      grp = TRUE),

  rec("Community and group-based",
      "Community-Based Mediator", "community_mediator",
      "The community-based mediator score is the entropy of a node's link distribution over communities times its share of total degree.",
      r"(CbM(v) = H_v \frac{d_v}{\sum_u d_u}, \quad H_v = -\sum_k p_{vk} \log_2 p_{vk})",
      r"(`membership`, `mode`)",
      "A high value indicates a well-connected node whose links are spread over several communities; nodes linked to one community score 0.",
      r"(Tulu, Hou & Younas (2018), eqs. 9-12. Base-2 entropy reproduces the paper's Table 1 exactly.)",
      grp = TRUE)
)

family_order <- c(
  "Degree, strength and local connectivity",
  "Distance and closeness",
  "Shortest-path brokerage and flow",
  "Spectral, walk and influence",
  "Neighbourhood structure and cohesion",
  "Directed prestige and hierarchy",
  "Community and group-based"
)
stopifnot(all(vapply(records, function(r) r$family, character(1)) %in%
                family_order))

emit_measure <- function(r) {
  cat("\n### ", r$title, " {#cent-", r$key, "}\n\n", sep = "")
  cat(r$concept, "\n\n", sep = "")
  if (nzchar(r$math)) cat("$$\n", r$math, "\n$$\n\n", sep = "")
  cat("**Meaning.** ", r$meaning, "\n\n", sep = "")
  cat("```r\n", r$example, "\n```\n\n", sep = "")
  cat("**Equivalence reference.** ", r$reference, "\n\n", sep = "")
}

emit_family <- function(fam) {
  cat("\n## ", fam, "\n\n", sep = "")
  for (r in records) if (identical(r$family, fam)) emit_measure(r)
}
```

## Catalogue index

```{r index, results = 'asis', echo = FALSE}
cat("<div class=\"cg-fam-index\">\n\n")
for (fam in family_order) {
  cat("**", fam, "**\n\n", sep = "")
  items <- Filter(function(r) identical(r$family, fam), records)
  links <- vapply(items, function(r) sprintf("[%s](#cent-%s)", r$title, r$key),
                  character(1))
  cat(paste(links, collapse = " · "), "\n\n")
}
cat("</div>\n\n")
```

```{r families_1_6, results = 'asis', echo = FALSE}
for (fam in family_order[1:6]) emit_family(fam)
```

The measures below need a **community membership vector**. Build one with
`detect_communities()` (`walktrap` works on the directed `student_interactions`
graph), then pass it as `membership =`:

```{r groups}
comm   <- detect_communities(student_interactions, method = "walktrap")
groups <- setNames(comm$community, comm$node)
centrality_participation(student_interactions, membership = groups)
```

```{r families_7, results = 'asis', echo = FALSE}
emit_family(family_order[7])
```

## Argument catalogue {#argument-catalogue}

All measures are reachable through the single `centrality()` verb. These
arguments control how they are computed. Measure-specific knobs are repeated in
each measure's **Arguments** line.

| Argument | Default | Affects | What it does |
|---|---|---|---|
| `type` | `"basic"` | all | Curated tier: `"basic"`, `"extended"`, or `"all"` (ordinary-cost measures). |
| `include` | `NULL` | all | Add named measures, or `"costly"` for every costly measure. |
| `map_flow` | `"unrecorded"` | Map equation | Unrecorded link teleportation, or `"recorded"` uniform node teleportation. |
| `map_convention` | `"paper"` | Map equation | Include module exits as in eq11, or `"infomap"` to reproduce its implementation and Table1. |
| `ninl_order` | `3` | NINL | Nonnegative iteration count; zero returns initial degree volume. |
| `sr_prior` | `0` | SpectralRank | Nonnegative scalar or node vector; zero gives ordinary SR and nonzero values give diagonal-prior WSR. Ground prior stays zero. |
| `ninl_radius` | `NULL` | NINL | Automatic ceiling of mean path length, or explicit nonnegative integer/`Inf`. Disconnected automatic radius is infinite; only reachable nodes contribute. |
| `beta_direction` | `"positive"` | BG-index / beta power | Positive credits predecessors; negative reverses the graph and credits destinations. |
| `mdd_lambda` | `0.7` | MDD | Weight assigned to exhausted degree, between 0 and 1. |
| `volume_radius` | `2` | Volume | Closed hop neighbourhood; nonnegative integer or `Inf`. |
| `diffusion_q` | `1` | Finite-horizon diffusion | Walk multiplier in [0, 1]. |
| `diffusion_steps` | `3` | Finite-horizon diffusion | Nonnegative integer horizon; independent of the TNA method. |
| `ds_beta` | `0.1` | Dynamics-sensitive | Spreading rate between zero and one. |
| `ds_mu` | `1` | Dynamics-sensitive | Recovery rate between zero and one; zero selects SI. |
| `ds_steps` | `5` | Dynamics-sensitive | Nonnegative integer time horizon. |
| `measures` | `NULL` | all | Character vector of specific measures to compute (overrides `type`). |
| `mode` | `"all"` | directed measures | Traversal direction: `"all"`, `"in"`, or `"out"`. |
| `normalized` | `FALSE` | most | Divide each score by its maximum. |
| `weighted` | `TRUE` | weighted measures | Use edge weights when present. |
| `directed` | `NULL` | all | Force directed/undirected; `NULL` auto-detects. |
| `loops` | `TRUE` | degree, strength | Keep self-loops. |
| `simplify` | `"sum"` | multigraphs | How to combine parallel edges. |
| `cutoff` | `-1` | path-based | Cap path length (`-1` = no cap). |
| `invert_weights` | `NULL` | distance/path | Treat weights as distances vs. strengths. |
| `alpha` | `1` | weight transform | Exponent applied when `invert_weights = TRUE`. |
| `damping` | `0.85` | PageRank | Random-walk damping factor. |
| `personalized` | `NULL` | PageRank | Personalization vector. |
| `transitivity_type` | `"local"` | transitivity | `"local"`, `"global"`, or weighted variants. |
| `isolates` | `"nan"` | transitivity | How isolates are scored. |
| `lambda` | `1` | diffusion | Diffusion scaling factor. |
| `k` | `3` | k-reach | Path-length radius. |
| `states` | `NULL` | percolation | Per-node percolation state vector. |
| `decay_parameter` | `0.5` | decay, generalized closeness | Distance-decay base. |
| `dmnc_epsilon` | `1.7` | DMNC | Density exponent. |
| `katz_alpha` | `0.1` | Katz | Attenuation factor. |
| `hubbell_weight` | `0.5` | Hubbell | Weight factor $w$. |
| `membership` | `NULL` | group-based | Community assignment vector. |
| `digits` | `NULL` | all | Round numeric columns. |
| `sort_by` | `NULL` | all | Order rows by a column name. |
