---
title: "Introduction to cograph"
author: "[Mohammed Saqr](https://saqr.me) and [Sonsoles López-Pernas](https://sonsoles.me)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cograph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 6,
  fig.dpi = 72,
  dpi = 72,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(cograph)
```

## Why cograph

R offers several network packages, each with its own data format and
interface, among them igraph for graph algorithms, qgraph for psychometric
networks, statnet for statistical network models and tidygraph for data
manipulation. An analysis that uses more than one of them begins by
converting the network between their formats.

cograph accepts the formats of all of these packages without conversion, and
cograph's analysis functions return their results as tidy data frames.
cograph visualizes networks with specialized styling for transition and
psychological networks, and plots the results of bootstrap, permutation and
stability analyses directly. cograph offers a family of wrangling verbs for
selecting, filtering, thresholding and editing networks, a large collection of
node centrality measures across all major families, and a wide array of
network-level statistics from density and diameter to efficiency and clique
size. For community structure, cograph provides a range of detection
algorithms together with consensus, comparison and significance testing of
partitions, and for local structure, cograph provides motif analysis that
identifies the nodes forming each pattern. cograph also supports robustness
and vulnerability analysis, backbone extraction with the disparity filter,
hierarchical plots for multi-cluster networks, multilayer networks and
higher-order pathways. cograph's figures carry statistical annotations such as
confidence intervals, p-values and significance stars.

The examples below use `regulation_net`, a synthetic weighted transition
network among ten learning states such as Explore, Plan and Reflect, included
in the package.

## Plotting

cograph offers tools for visualizing networks through `splot()` and a set of
specialized plots. `splot()` plots any supported network input with base R
graphics and has arguments for controlling the layout, the nodes and their pie
and donut decorations, the edges with their curvature, arrows and labels, the
legends and the theme. It has specialized styling for transition networks
(`tna_styling`) and psychological networks (`psych_styling`), and it plots the
result objects of tna and Nestimate directly, including bootstrap, permutation
and stability results, multilevel VAR models and group comparisons.
Heterogeneous transition networks are plotted with `plot_htna()`.

```{r fig.height=6}
splot(regulation_net, tna_styling = TRUE, minimum = 0.1,
  title = "Learning Regulation Network")
```

```{r eval=FALSE}
splot(regulation_net, layout = "spring")
splot(regulation_net, minimum = 0.1, edge_labels = TRUE)
splot(regulation_net, scale_nodes_by = "betweenness")
splot(regulation_net, theme = "dark")
splot(regulation_net, tna_styling = TRUE)
```

## Specialized plots

cograph offers a wide array of network plots across visualization domains.
These include transitions, flows and individual trajectories over time,
network evolution in temporal small multiples and three-dimensional prisms,
weight matrices as heatmaps and chord diagrams, centrality profiles with their
distributions, comparisons and stability, edge-weight and degree distributions,
motifs, comparisons between networks, bootstrap confidence intervals and
permutation tests, mixed directed and undirected networks, multi-cluster,
multi-group and multilayer structure, community overlays, higher-order
pathways and robustness curves.

| Function | Purpose |
|----------|---------|
| `splot()` | Network graph (base R) |
| `plot_tna()` / `tplot()` | TNA-style wrappers with qgraph-compatible parameters |
| `plot_chord()` | Chord diagram (directed/undirected ribbons) |
| `plot_heatmap()` | Adjacency heatmap with clustering |
| `plot_ml_heatmap()` | Multi-layer comparison heatmap |
| `plot_transitions()` / `plot_alluvial()` | Alluvial / Sankey flow diagrams |
| `plot_trajectories()` | Individual trajectory tracking |
| `plot_difference()` | Difference network between two matrices |
| `plot_comparison_heatmap()` | Side-by-side heatmap comparison |
| `plot_mixed_network()` | Directed + undirected edges combined |
| `plot_bootstrap_forest()` | Bootstrap CI forest plots (linear, circular, grouped) |
| `plot_edge_diff_forest()` | Edge difference plots (linear, circular, chord, tile) |
| `plot_simplicial()` | Higher-order pathway blob overlays |
| `overlay_communities()` | Community blob overlays on network |
| `plot_mcml()` | Two-layer hierarchical cluster visualization |
| `plot_mtna()` | Flat multi-cluster layout |
| `plot_mlna()` | Stacked multilayer 3D perspective |
| `plot_htna()` | Multi-group heterogeneous TNA layout |
| `plot_robustness()` | Robustness degradation curves |
| `plot_permutation()` / `plot_group_permutation()` | Permutation test results |
| `plot_centrality()` / `plot_centrality_distribution()` | Centrality profiles and their distributions |
| `plot_centrality_heatmap()` / `plot_centrality_compare()` | Centrality across nodes and groups |
| `plot_net_stability()` | Centrality stability results |
| `plot_edge_weights()` / `plot_degree_correlation()` | Edge-weight distribution and degree-degree correlation |
| `plot_motifs()` | Motif and subgraph results |
| `plot_network_evolution()` | Network evolution in small multiples |
| `plot_temporal()` | Temporal network as a three-dimensional prism |

```{r fig.height=6, fig.width=10}
plot_simplicial(regulation_net,
  c("Explore Plan -> Monitor",
    "Monitor Adapt -> Reflect",
    "Discuss Synthesize -> Evaluate",
    "Create Share -> Explore"),
  dismantled = TRUE, ncol = 2,
  title = "Higher-Order Pathways")
```

## Input formats

cograph accepts adjacency matrices, edge lists, and igraph, statnet, qgraph and
tna objects without conversion. Its conversion functions export a network to
igraph, statnet, matrix and edge-list formats for exchange with other
packages, and `from_qgraph()` imports the styling of a qgraph plot.

| Format | Example |
|--------|---------|
| Matrix | `splot(regulation_net)` |
| Edge list | `splot(data.frame(from = "A", to = "B", weight = 1))` |
| igraph | `splot(igraph::make_ring(5))` |
| statnet | `splot(network::network(regulation_net))` |
| qgraph | `from_qgraph(q)` |
| tna | `splot(tna::tna(data))` |

| Function | Output |
|----------|--------|
| `as_cograph(x)` | cograph_network object |
| `to_igraph(x)` | igraph object |
| `to_matrix(x)` | Adjacency matrix |
| `to_data_frame(x)` / `to_df(x)` | Edge list data frame |
| `to_network(x)` | statnet network object |
| `from_qgraph(q)` | Extract qgraph styles into cograph |

## Wrangling

cograph offers a family of wrangling verbs for selecting and filtering nodes
and edges, thresholding and transforming weights, and restructuring and
editing a network. Every verb accepts any supported input, takes its options as
named arguments and returns a network, so verbs chain with the native pipe.
`as.data.frame()` returns the edges as a tidy data frame, and
`as.data.frame(what = "nodes")` returns the nodes.

```{r}
strong <- filter_edges(regulation_net, weight > 0.3)
as.data.frame(strong)
```

`select_nodes()` selects nodes by name or index, the top nodes by any
centrality measure, the neighbours of given nodes up to a chosen order, or the
nodes of a connected component. `select_edges()` selects the strongest edges,
the edges involving or joining given sets of nodes, bridges and mutual ties.
Centrality measures named in a selection are computed when the verb runs.

```{r}
top3 <- select_nodes(regulation_net, top = 3, by = "betweenness")
get_labels(top3)
```

`filter_nodes()` keeps the nodes that satisfy logical expressions over node
attributes, any centrality measure, and structural properties such as
component membership, k-core, isolation and cut vertices. `filter_edges()`
keeps the edges that satisfy expressions over edge columns, such as
`weight > mean(weight)`. Filters combine with the other verbs into pipelines
that prepare a network for analysis in a single, reproducible expression. The
pipeline below keeps the ties with weights of at least 0.3, removes the nodes
left without ties, and adds each node's degree and a hub indicator to the node
table.

```{r}
regulation_net |>
  threshold_edges(minimum = 0.3) |>
  remove_isolates() |>
  mutate_nodes(deg = degree, hub = degree >= 3) |>
  as.data.frame(what = "nodes")
```

### Selecting

cograph provides functions for extracting ego networks of several orders,
connected components, k-cores, bridges and the edges between two sets of
nodes.

| Function | Purpose |
|----------|---------|
| `filter_edges(x, ...)` | Filter by weight, endpoints, any edge column |
| `filter_nodes(x, ...)` | Filter by degree, centrality, label |
| `select_nodes(x, ...)` | Top-N by centrality, by name, neighbors, component |
| `select_edges(x, ...)` | Top-N, involving, between, bridges, mutual |
| `select_neighbors(x, of)` | Ego-network extraction (multi-hop) |
| `select_component(x)` | Largest or named component |
| `select_top(x, n, by)` | Top-N nodes by any centrality |
| `select_k_core(x, k)` | The k-core |
| `split_components(x)` | One network per component |
| `select_bridges(x)` | Bridge edges only |
| `select_top_edges(x, n)` | Top-N edges by weight |
| `select_edges_involving(x, nodes)` | Edges touching specific nodes |
| `select_edges_between(x, s1, s2)` | Edges between two node sets |
| `subset_nodes(x, ...)` / `subset_edges(x, ...)` | Aliases of the filters |

### Weights

cograph provides functions for thresholding edges by weight, count, proportion
or density, binarizing weights, and symmetrizing a directed network by
maximum, minimum, mean, sum or mutuality. Further functions normalize weights
by row, column, maximum, sum or range, and convert similarities into
distances for path-based measures.

| Function | Purpose |
|----------|---------|
| `threshold_edges(x, ...)` | Keep edges by weight, count, proportion, density |
| `binarize(x)` | Replace weights with 0/1 |
| `symmetrize(x, method)` | Combine opposite arcs into one edge |
| `normalize_weights(x, method)` | Rescale by row, column, max, sum, min-max |
| `invert_weights(x, method)` | Similarities to distances |

### Structure and editing

cograph provides functions for converting between directed and undirected
networks, reversing arcs, contracting groups of nodes into single nodes with
aggregated weights, extracting minimum or maximum spanning trees and forming
the complement of a network. Nodes and edges can be added or removed, their
attributes computed, and two networks combined by union, intersection or
difference.

| Function | Purpose |
|----------|---------|
| `to_undirected(x)` / `to_directed(x)` | Change directedness |
| `reverse_edges(x)` | Reverse every arc |
| `remove_isolates(x)` | Drop nodes with no edges |
| `contract_nodes(x, groups)` | Collapse groups into single nodes |
| `spanning_tree(x)` | Minimum or maximum spanning tree |
| `complement_network(x)` | Join the non-adjacent pairs |
| `reorder_nodes(x, order)` / `rename_nodes(x, from, to)` | Node order and labels |
| `add_nodes()` / `remove_nodes()` / `add_edges()` / `remove_edges()` | Editing |
| `mutate_nodes(x, ...)` / `mutate_edges(x, ...)` | Compute and store attributes |
| `bind_networks(x, y, method)` | Union, intersection, difference |
| `simplify(x)` | Remove multi-edges and self-loops |

The node and edge tables, labels, size, direction, group assignments and
layout of a network object can be read and set with accessor functions.

| Function | Purpose |
|----------|---------|
| `as.data.frame(x)` | Tidy edge table (`what = "nodes"` for nodes) |
| `get_nodes(x)` / `set_nodes(x, df)` | Node data frame |
| `get_edges(x)` / `set_edges(x, df)` | Edge data frame |
| `get_labels(x)` | Node label vector |
| `n_nodes(x)` / `n_edges(x)` | Counts |
| `is_directed(x)` | Directedness |
| `set_groups(x)` / `get_groups(x)` | Group assignments |
| `set_layout(x, layout)` | Layout coordinates |

## Centrality

cograph offers `r nrow(list_centralities())` node centrality measures through
`centrality()`, which returns a tidy data frame with a column for each
measure, and through individual functions that return a single measure. The
measures span degree and strength, distance and closeness, shortest-path
brokerage, spectral and walk-based influence, neighbourhood cohesion, directed
prestige and community-based roles. Measures that are also implemented
elsewhere are tested against igraph, sna, centiserve, brainGraph, influenceR,
netrankr and NetworkX. The examples in this section use the built-in
`student_interactions` edge list, which `centrality()` accepts directly.

```{r}
data(student_interactions)
centrality(student_interactions)
```

By default, `centrality()` returns six classical measures: degree, strength,
closeness, betweenness, eigenvector centrality and PageRank. Any other measure
is chosen by name with `measures`, and `type = "all"` returns every measure of
ordinary computational cost.

```{r}
centrality_degree(student_interactions)
centrality_pagerank(student_interactions)
```

The measures fall into seven families: degree, strength and local
connectivity; distance and closeness; shortest-path brokerage and flow;
spectral, walk and influence; neighbourhood structure and cohesion; community
and group-based roles; and directed prestige and hierarchy. Recent measures
from these families include Trust-PageRank, randomized shortest-path
betweenness, the Lhc index and the BG-index, and any of them can be requested
alongside the classical ones. Community-based measures also require a
partition, supplied with `membership`. The centrality catalogue documents
every measure with its definition, interpretation and an example.

```{r}
centrality(student_interactions,
           measures = c("collective_influence", "harmonic", "rsp_betweenness",
                        "trust_pagerank", "lhc", "beta_measure"),
           sort_by = "trust_pagerank", digits = 3)
```

## Network properties

cograph offers network-level statistics through `network_summary()`, which
returns density, diameter, mean distance, centralization, reciprocity,
transitivity and degree assortativity in a data frame with one row for the
network, and up to 37 statistics with `detailed = TRUE` and
`extended = TRUE`. Individual functions compute small-worldness, global and
local efficiency, the rich-club coefficient, girth, radius, bridges, cut
vertices, vertex connectivity and clique size.

```{r}
network_summary(regulation_net)
```

| Function | Purpose |
|----------|---------|
| `network_summary()` | 37 metrics (density, diameter, clustering, etc.) |
| `network_small_world()` | Small-world coefficient |
| `network_rich_club()` | Rich-club coefficient |
| `network_global_efficiency()` | Global efficiency |
| `network_local_efficiency()` | Local efficiency |
| `degree_distribution()` | Degree histogram |
| `network_girth()` | Shortest cycle |
| `network_radius()` | Minimum eccentricity |
| `network_bridges()` | Bridge edges |
| `network_cut_vertices()` | Articulation points |
| `network_vertex_connectivity()` | Minimum vertices to disconnect |
| `network_clique_size()` | Largest complete subgraph |

## Community detection

cograph offers tools for studying community structure through detection,
consensus, comparison, quality assessment and significance testing of
partitions. `communities()` runs eleven community detection algorithms,
including Louvain, Leiden, Infomap, walktrap and spinglass, through one call
and returns the partition with its modularity, and each algorithm also has its
own function with a short alias. `community_consensus()` runs an algorithm
repeatedly and returns the consensus partition across runs.
`compare_communities()` compares two partitions by variation of information,
normalized mutual information, split-join distance or the Rand and adjusted
Rand indices, `cluster_quality()` scores a partition, and
`cluster_significance()` tests its modularity against random networks that
preserve the degree sequence or the number of edges.

```{r}
comms <- communities(regulation_net, method = "walktrap")
comms
community_sizes(comms)
```

| Function | Algorithm | Alias |
|----------|-----------|-------|
| `community_louvain()` | Louvain modularity | `com_lv()` |
| `community_leiden()` | Leiden (improved Louvain) | `com_ld()` |
| `community_fast_greedy()` | Fast greedy | `com_fg()` |
| `community_walktrap()` | Random walk | `com_wt()` |
| `community_infomap()` | Information flow | `com_im()` |
| `community_label_propagation()` | Label propagation | `com_lp()` |
| `community_edge_betweenness()` | Edge betweenness | `com_eb()` |
| `community_leading_eigenvector()` | Leading eigenvector | `com_le()` |
| `community_spinglass()` | Spin glass | `com_sg()` |
| `community_optimal()` | Exact optimization | `com_op()` |
| `community_fluid()` | Fluid communities | `com_fl()` |

| Function | Purpose |
|----------|---------|
| `community_consensus()` | Run algorithm N times, keep stable assignments |
| `compare_communities()` | Compare partitions (NMI, VI, Rand, adjusted Rand) |
| `community_sizes()` | Size of each community |
| `color_communities()` | Color vector from community membership |
| `cluster_quality()` | Quality metrics (silhouette, Dunn index) |
| `cluster_significance()` | Permutation-based significance testing |
| `detect_communities()` | Alternative interface (returns data frame) |

## Motifs

cograph offers motif analysis for directed networks based on the 16 triads of
the MAN classification. `motifs()` counts each triad type and tests its
frequency with a permutation test, across the whole network, per actor, or
within rolling and tumbling windows. `subgraphs()` identifies the nodes behind
each motif and reports which node triples form each pattern, in how many
sessions or actors they occur, and whether they occur more often than
expected. `plot()` visualizes the counts, their significance, the triads and
the patterns.

```{r}
mot <- motifs(regulation_net, significance = FALSE)
mot
```

| Function | Purpose |
|----------|---------|
| `motifs()` | MAN type census with significance testing |
| `subgraphs()` | Named node triples forming each pattern |
| `motif_census()` | Low-level triad census |
| `extract_motifs()` | Per-individual motif extraction |
| `extract_triads()` | Extract specific triad types |
| `triad_census()` | Raw 16-type triad count |
| `get_edge_list()` | Edge list from tna for motif input |

## Robustness

cograph offers tools for studying network robustness and vulnerability through
simulated attacks and node-level efficiency loss. `robustness()` simulates the
sequential removal of nodes or edges, ordered by a centrality measure or at
random, and returns the size of the largest component at each step. The
ranking can be recomputed after every removal or fixed at the start, and
random removal is averaged over repeated runs. `robustness_auc()` and
`robustness_summary()` summarize each curve, including the area under it, and
`plot_robustness()` visualizes several attack strategies together.
`vulnerability()` computes, for each node, the relative drop in global
efficiency when that node is removed.

```{r eval=FALSE}
robustness(regulation_net, type = "vertex", measure = "betweenness", n_iter = 100)
plot_robustness(x = regulation_net, measures = c("betweenness", "degree", "random"))
```

| Function | Purpose |
|----------|---------|
| `robustness()` | Simulate removal attacks (vertex or edge) |
| `plot_robustness()` | Plot robustness curves for multiple strategies |
| `robustness_summary()` | AUC and summary statistics |
| `robustness_auc()` | Area under the robustness curve |
| `vulnerability()` | Relative drop in global efficiency when each node is removed |

## Disparity filter

cograph offers backbone extraction for weighted networks through the disparity
filter (Serrano et al., 2009), which keeps the edges whose weights are
significantly larger than expected if each node's strength were spread
uniformly over its ties. `disparity_filter()` applies the test at a chosen
significance level. For a matrix it returns a binary matrix of the
significant edges, and for a network object it returns a backbone that
`splot()` plots directly.

```{r eval=FALSE}
backbone <- disparity_filter(as_cograph(regulation_net), level = 0.05)
splot(backbone)
```

## Multi-cluster visualization

cograph offers hierarchical plots for multi-cluster multi-level (MCML)
networks, whose nodes belong to known clusters. `plot_mcml()` shows the
network as a two-layer hierarchy. The lower layer places every node inside its
cluster's shell with the within- and between-cluster edges, and the upper
layer collapses each cluster into a single node whose pie chart shows its
share of the initial state distribution. `plot_mtna()` shows the clusters as
shells in one plane, with individual edges within clusters and summary edges
between them. `csum()` aggregates an estimated weight matrix into
cluster-level transitions, and `summarize_clusters()` estimates the Markov
chain over cluster states from the raw transition data.

```{r eval=FALSE}
clusters <- list(
  Cognitive  = c("Explore", "Plan", "Monitor", "Adapt", "Reflect"),
  Social     = c("Discuss", "Synthesize", "Share"),
  Evaluative = c("Evaluate", "Create")
)
plot_mcml(regulation_net, clusters, mode = "tna")
plot_mtna(regulation_net, clusters)
```

| Function | Architecture |
|----------|-------------|
| `plot_mcml()` | Two-layer: detail nodes + summary pies |
| `plot_mtna()` | Flat cluster layout |
| `csum()` | Aggregate an estimated weight matrix to cluster level |
| `summarize_clusters()` | Estimate the cluster-level Markov chain from transition data |
| `as_tna()` / `as_mcml()` | Convert cluster summaries to tna objects |
| `summarize_network()` / `cnet()` | Extract cluster-level network (matrix aggregation) |

## Multilayer networks

cograph offers tools for constructing, analysing and visualizing multilayer and
multiplex networks. `supra_adjacency()` builds the supra-adjacency matrix, with
the layers as its diagonal blocks and the inter-layer coupling, diagonal, full
or user-defined and weighted by `omega`, off the diagonal. `supra_layer()` and
`supra_interlayer()` extract its blocks. `aggregate_layers()` combines layers
by sum, mean, maximum, minimum, union or intersection, and
`layer_similarity()` compares two layers by Jaccard, overlap, Hamming, cosine
or Pearson similarity. `plot_mlna()` visualizes the layers stacked in a
three-dimensional perspective with dashed inter-layer edges, and
`plot_ml_heatmap()` shows each layer as a heatmap on a tilted plane.

| Function | Purpose |
|----------|---------|
| `supra_adjacency()` | Build the supra-adjacency matrix |
| `supra_layer()` / `supra_interlayer()` | Extract individual layers |
| `aggregate_layers()` / `aggregate_weights()` | Combine layers |
| `layer_similarity()` | Similarity between two layers |
| `plot_mlna()` / `mlna()` | Layers stacked in 3D perspective |
| `plot_ml_heatmap()` | Multi-layer heatmap comparison |

## Higher-order networks

cograph offers visualization of higher-order network models, which capture
sequential dependencies beyond a first-order Markov chain and are estimated
with the Nestimate package. `plot_simplicial()` visualizes higher-order
pathways as blobs over the network layout, from pathway strings, higher-order
network (HON) and HYPA objects, or multi-order model transitions. Given a tna
model or a Nestimate network with sequence data, it builds the pathways
itself, as a HON, as anomalous paths under a hypergeometric null, or as
association rules.

| Function | Purpose |
|----------|---------|
| `Nestimate::build_hon()` | Higher-Order Network construction |
| `Nestimate::build_hypa()` | Path anomaly detection (hypergeometric null) |
| `Nestimate::build_mogen()` | Multi-order model selection (AIC/BIC) |
| `Nestimate::path_counts()` | k-step path frequencies |
| `plot_simplicial()` | Visualize pathways as blob overlays |
| `Nestimate::build_simplicial()` | Simplicial complex from cliques |
| `Nestimate::persistent_homology()` | Topological persistence across thresholds |
| `Nestimate::q_analysis()` | Multi-level structural connectivity |
| `Nestimate::verify_simplicial()` | Cross-validate via Euler-Poincare theorem |

## TNA integration

cograph offers visualization for Transition Network Analysis (TNA) models
estimated with the tna package. `splot()` plots tna models with donut rings
filled by the initial probabilities, bootstrap results with edges styled by
stability, permutation tests as difference networks, and communities and
disparity backbones. Group models appear as one panel per group, or as a
single group selected with `i`. `plot_tna()` and `tplot()` accept qgraph's
argument names, so plotting code written for qgraph carries over, and
`plot_htna()` plots heterogeneous TNA models, whose nodes belong to groups of
different kinds, in circular, bipartite or polygonal layouts.

| Object | What splot() does |
|--------|-------------------|
| `tna` | Network with donut rings, TNA styling |
| `group_tna` | Multi-panel grid per group |
| `tna_bootstrap` | Stability-styled edges |
| `tna_permutation` | Colored difference network |
| `group_tna_permutation` | Multi-panel permutation results |
| `tna_communities` | Network coloured by community |
| `tna_disparity` | Backbone filter visualization |

## Palettes

cograph offers colour palettes for sequential, diverging and categorical
encodings. They include viridis, blue and red gradients, a blue-white-red
diverging scale with a configurable midpoint, the colour-blind-safe Okabe-Ito
colours and a pastel set. Each palette function returns `n` colours.

| Function | Colors |
|----------|--------|
| `palette_viridis(n)` | Viridis scale |
| `palette_pastel(n)` | Soft pastel |
| `palette_blues(n)` | Blue gradient |
| `palette_reds(n)` | Red gradient |
| `palette_diverging(n)` | Blue-white-red |
| `palette_colorblind(n)` | Colorblind-safe |
| `palette_rainbow(n)` | Rainbow |

## Further reading

**Package resources:**

- [cograph function reference](https://saqr.me/cograph/), complete list of all functions with examples
- [cograph pkgdown site](https://sonsoles.me/cograph/), full documentation and articles

**Blog posts:**

- [cograph: Complex Network Analysis and Visualization](https://saqr.me/blog/2026/cograph-network-visualization/), overview of the package design and capabilities
- [Human–AI Interaction: A TNA with cograph](https://saqr.me/blog/2026/human-ai-interaction-cograph/), worked example analyzing 13,002 turns of human–AI coding collaboration

**References:**

- Serrano, M. Á., Boguñá, M., & Vespignani, A. (2009). Extracting the multiscale backbone of complex weighted networks. *Proceedings of the National Academy of Sciences*, 106(16), 6483–6488. <https://doi.org/10.1073/pnas.0808904106>

- Saqr, M., López-Pernas, S., Conde-González, M. Á., & Hernández-García, Á. (2024). Social Network Analysis: A Primer, a Guide and a Tutorial in R. In *Learning Analytics Methods and Tutorials* (pp. 491–518). Springer. <https://doi.org/10.1007/978-3-031-54464-4_15>

- Hernández-García, Á., Cuenca-Enrique, C., Traxler, A., López-Pernas, S., Conde-González, M. Á., & Saqr, M. (2024). Community detection in learning networks using R. In *Learning Analytics Methods and Tutorials* (pp. 519–540). Springer. <https://doi.org/10.1007/978-3-031-54464-4_16>

- Saqr, M., López-Pernas, S., Törmänen, T., Kaliisa, R., Misiejuk, K., & Tikka, S. (2025). Transition Network Analysis: A Novel Framework for Modeling, Visualizing, and Identifying the Temporal Patterns of Learners and Learning Processes. In *Proceedings of the 15th LAK Conference* (pp. 351–361). ACM.  <https://doi.org/10.1145/3706468.3706513>

- Tikka, S., López-Pernas, S., & Saqr, M. (2025). tna: An R Package for Transition Network Analysis. *Applied Psychological Measurement*, 49(6), 326–328. <https://doi.org/10.1177/01466216251348840>
