---
title: "Network Estimation and Visualization with Nestimate + cograph"
description: |
    From raw sequence data to publication-ready statistical network plots ---
    build, bootstrap, compare, and visualize using Nestimate and cograph together.
date: "2026-03-18"
author:
  - name: Mohammed Saqr
    url: https://saqr.me
    affiliation: University of Eastern Finland
  - name: Sonsoles López-Pernas
    url: https://sonsoles.me
    affiliation: University of Eastern Finland
categories:
  - tutorial
  - R
  - visualization
  - Nestimate
warning: false
message: false
fig.align: center
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: false
    code-tools: false
    theme: cosmo
    self-contained: true
execute:
  warning: false
  message: false
knitr:
  opts_chunk:
    fig.width: 8
    fig.height: 7
    dpi: 150
    comment: ""
---

```{r}
#| label: setup
#| include: false
library(Nestimate)
library(tna)
devtools::load_all("..")
```

# Introduction

**Nestimate** estimates networks from sequence data using a unified `build_network()`
interface — pick your estimator (`"relative"`, `"glasso"`, `"pcor"`, `"frequency"`,
and more) and Nestimate handles the rest. The result is a `netobject` that already
inherits `cograph_network`, so `splot()` renders it immediately.

But the real payoff is in the statistical layer: bootstrapped stability analysis,
permutation-based group comparisons, and group-level multi-panel views. All of these
objects dispatch through `splot()` automatically — no conversion, no adapter code.

This tutorial walks through the full pipeline with the `group_regulation` dataset
from the `tna` package.

---

# Data

`group_regulation` is a wide-format sequence dataset of 9 collaborative regulation
behaviors coded across student groups. `group_regulation_long` adds achievement-group
labels for multi-group analysis.

```{r}
#| label: data
data("group_regulation")
data("group_regulation_long")
dim(group_regulation)
head(group_regulation[, 1:8], 3)
```

---

# Estimating Networks

`build_network()` estimates a network from raw sequence data. The `method` argument
selects the estimator. Here we use `"relative"` — row-normalized transition
probabilities, the standard for TNA.

```{r}
#| label: build-network
net <- build_network(group_regulation, method = "relative")
net
```

`net` is a `netobject` (which inherits `cograph_network`), so `splot()` renders it
directly with no extra steps:

```{r}
#| label: fig-base
#| fig-cap: "Collaborative regulation network — row-normalized transitions (relative method)"
splot(net)
```

Other available estimators:

```{r}
#| label: estimators
#| echo: true
#| eval: false
build_network(group_regulation, method = "frequency")   # raw counts
build_network(group_regulation, method = "co_occurrence") # co-occurrence
build_network(group_regulation, method = "glasso")      # LASSO partial correlations
build_network(group_regulation, method = "pcor")        # partial correlations
```

---

# Bootstrap Stability (`net_bootstrap`)

`bootstrap_network()` resamples the data, refits the model at each iteration, and
identifies which edges are stable vs. sampling artifacts. The result is a
`net_bootstrap` object — pass it directly to `splot()`.

```{r}
#| label: run-bootstrap
#| cache: true
set.seed(265)
boot <- bootstrap_network(net, iter = 1000)
boot
```

## Styled mode (default)

Significant edges (p < 0.05) appear **solid dark blue**; non-significant edges appear
**dashed grey**. This immediately separates the stable network structure from noise.

```{r}
#| label: fig-boot-styled
#| fig-cap: "Bootstrapped network — solid = stable edges, dashed = sampling artifacts"
splot(boot)
```

## Significant edges only

```{r}
#| label: fig-boot-sig
#| fig-cap: "Only statistically stable edges retained"
splot(boot, display = "significant")
```

## Full network (no styling)

```{r}
#| label: fig-boot-full
#| fig-cap: "All edges shown with uniform styling (bootstrap weights)"
splot(boot, display = "full")
```

## Significance stars on edge labels

```{r}
#| label: fig-boot-stars
#| fig-cap: "Bootstrap network with significance stars (*, **, ***)"
splot(boot, show_stars = TRUE)
```

## Confidence interval labels

```{r}
#| label: fig-boot-ci
#| fig-cap: "Bootstrap weights with 95% CI bounds on each edge label"
splot(boot, show_ci = TRUE)
```

::: {.callout-tip collapse="true"}
## `splot()` display modes for `net_bootstrap`

| `display` | Description |
|---|---|
| `"styled"` (default) | Significant = solid blue, non-significant = dashed grey |
| `"significant"` | Only significant edges |
| `"full"` | All edges, uniform styling |

Additional parameters: `show_stars`, `show_ci`, `inherit_style`.
:::

---

# Group Networks (`netobject_group`)

Pass `group =` to `build_network()` and it estimates a separate network per group,
returning a `netobject_group` — a named list. `splot()` dispatches to
`plot_netobject_group()` and renders all groups in an automatic grid.

```{r}
#| label: build-group
grp_net <- build_network(
  group_regulation_long, method = "relative",
  action = "Action", actor = "Actor", time = "Time",
  group = "Achiever"
)
names(grp_net)
```

```{r}
#| label: fig-group-default
#| fig-cap: "High vs. Low achievers — side-by-side on a common weight scale"
#| fig-width: 12
#| fig-height: 6
splot(grp_net)
```

`common_scale = TRUE` (default) ensures both panels use the same maximum weight, so
edge widths are directly comparable. Turn it off when you want each panel to use its
own scale:

```{r}
#| label: fig-group-noscale
#| fig-cap: "Each group on its own weight scale — emphasises internal structure"
#| fig-width: 12
#| fig-height: 6
splot(grp_net, common_scale = FALSE, title_prefix = "Achievers: ")
```

---

# Permutation Testing (`net_permutation`)

`Nestimate::permutation_test()` tests whether each edge **differs significantly**
between two groups by comparing the observed difference to a permutation null
distribution.

```{r}
#| label: run-perm
#| cache: true
set.seed(265)
perm <- Nestimate::permutation_test(grp_net$High, grp_net$Low, iter = 1000)
perm
```

Pass the result directly to `splot()`:

```{r}
#| label: fig-perm-sig
#| fig-cap: "Permutation test — green = High > Low, red = Low > High (p < 0.05)"
splot(perm)
```

## Show non-significant edges

```{r}
#| label: fig-perm-nonsig
#| fig-cap: "All edges — coloured solid = significant, dashed grey = non-significant"
splot(perm, show_nonsig = TRUE)
```

## With significance stars and effect sizes

```{r}
#| label: fig-perm-stars-effect
#| fig-cap: "Permutation test with stars and effect sizes (Cohen's d in parentheses)"
splot(perm, show_stars = TRUE, show_effect = TRUE)
```

::: {.callout-tip collapse="true"}
## `splot()` parameters for `net_permutation`

| Parameter | Default | Description |
|---|---|---|
| `show_nonsig` | `FALSE` | Show non-significant edges |
| `edge_positive_color` | `"#009900"` | Color when High > Low |
| `edge_negative_color` | `"#C62828"` | Color when Low > High |
| `show_stars` | `TRUE` | Significance stars (*, **, ***) |
| `show_effect` | `FALSE` | Effect size in parentheses |
:::

---

# The Dispatch Chain

Every Nestimate object routes through `splot()` — no wrapper functions, no
class-checking in your analysis code:

```{r}
#| label: dispatch-chain
#| eval: false
splot(net)      # netobject      → standard network plot
splot(boot)     # net_bootstrap  → stability-styled network
splot(grp_net)  # netobject_group → multi-panel grid
splot(perm)     # net_permutation → coloured difference network
```

Each dispatcher respects all standard `splot()` arguments (`layout`, `node_fill`,
`edge_color`, `title`, etc.), so the same customization API works everywhere.

---

```{r}
#| label: session
sessionInfo()
```
