---
title: "Network Visualization with cograph"
description: |
  A hands-on introduction to cograph — layouts, edge styles,
  community detection, and publication-ready network plots.
date: "2026-03-18"
author:
  - name: Mohammed Saqr
    url: https://saqr.me
    affiliation: University of Eastern Finland
  - name: Sonsoles López-Pernas
    url: https://sonsoles.me
    affiliation: University of Eastern Finland
categories:
  - tutorial
  - R
  - visualization
warning: false
message: false
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
knitr:
  opts_chunk:
    fig.align: center
    dpi: 150
    comment: ''
---

```{r setup, include=FALSE}
devtools::load_all("..", quiet = TRUE)
```

## The Network

We use a 15-node undirected network representing collaboration ties between
students in an online course. Edge weights reflect interaction frequency.
The network has a planted block structure — three groups of five students —
with dense within-group ties and sparse cross-group ties.

```{r create-network}
set.seed(42)
n   <- 15
nms <- paste0("S", 1:15)

# Helper: add edges within a block (upper-triangle only, then symmetrize)
add_block <- function(W, rows, cols, density, lo = 0.15, hi = 0.8) {
  p   <- expand.grid(i = rows, j = cols)
  p   <- p[p$i < p$j, ]
  sel <- sample(nrow(p), ceiling(nrow(p) * density))
  p   <- p[sel, ]
  W[cbind(p$i, p$j)] <- round(runif(nrow(p), lo, hi), 2)
  W
}

W <- matrix(0, n, n, dimnames = list(nms, nms))
W <- add_block(W, 1:5,   1:5,   0.7)           # Group A — dense
W <- add_block(W, 6:10,  6:10,  0.7)           # Group B — dense
W <- add_block(W, 11:15, 11:15, 0.7)           # Group C — dense
W <- add_block(W, 1:5,   6:10,  0.2, 0.05, 0.3)   # A–B bridge
W <- add_block(W, 6:10,  11:15, 0.2, 0.05, 0.3)   # B–C bridge
W <- add_block(W, 1:5,   11:15, 0.1, 0.05, 0.2)   # A–C rare
W <- W + t(W)                                  # symmetrize
diag(W) <- 0

cat(n, "nodes |", sum(W != 0) / 2, "edges | weight range:",
    round(min(W[W > 0]), 2), "–", round(max(W), 2))
```

A first look with default settings:

```{r basic-plot, fig.width=7, fig.height=5.5}
splot(W,
      title      = "Student Collaboration Network",
      node_fill  = "#4FC3F7",
      edge_color = "#555555")
```

---

## Layouts

The same network with five layout algorithms. Layout choice changes which
structural features become salient.

```{r layouts, fig.width=10, fig.height=7}
layouts <- c("oval", "spring", "circle", "grid", "mds")
titles  <- c("Oval (deterministic)", "Spring (Fruchterman-Reingold)",
             "Circle", "Grid", "MDS (structural similarity)")

par(mfrow = c(2, 3), mar = c(1, 1, 2.5, 1))
for (k in seq_along(layouts)) {
  splot(W,
        layout      = layouts[k],
        title       = titles[k],
        node_fill   = "#4FC3F7",
        edge_color  = "#777777",
        label_size  = 0.7)
}
par(mfrow = c(1, 1))
```

::: {.callout-tip}
**When to use which layout**

| Layout | Best for |
|---|---|
| `"oval"` | Compact, reproducible figures |
| `"spring"` | Revealing clusters |
| `"circle"` | Comparing node positions by degree |
| `"grid"` | Regular structures, lattices |
| `"mds"` | Placing similar nodes close together |
:::

---

## Edge Styles

`edge_style` controls the line type (R `lty` values 1–5).
All plots use the oval layout so only the edge rendering varies.

```{r edge-styles, fig.width=10, fig.height=7}
style_names <- c("Solid (1)", "Dashed (2)", "Dotted (3)",
                 "Dot-dash (4)", "Long-dash (5)")

par(mfrow = c(2, 3), mar = c(1, 1, 2.5, 1))
for (k in 1:5) {
  splot(W,
        layout      = "oval",
        edge_style  = k,
        title       = style_names[k],
        node_fill   = "#fbb550",
        edge_color  = "#333333",
        label_size  = 0.7)
}
par(mfrow = c(1, 1))
```

---

## Community Detection

`detect_communities()` wraps igraph's community algorithms and returns
node membership. We map membership to colours.

```{r communities, fig.width=7, fig.height=5.5}
net    <- cograph(W)
comm   <- detect_communities(net, method = "louvain")
mems   <- setNames(comm$community, comm$node)
n_comm <- length(unique(mems))

palette <- c("#E53935", "#43A047", "#1E88E5", "#FB8C00", "#8E24AA")
cols    <- palette[mems[nms]]   # colour per node, in network order

splot(W,
      layout     = "spring",
      node_fill  = cols,
      title      = paste0("Louvain Communities  (k = ", n_comm, ")"),
      edge_color = "#999999")
```

```{r community-table, echo=FALSE}
grp_tbl <- data.frame(
  Community = paste0("C", sort(unique(mems))),
  Members   = vapply(sort(unique(mems)), function(g)
                paste(names(mems[mems == g]), collapse = ", "), character(1)),
  Size      = vapply(sort(unique(mems)), function(g) sum(mems == g), integer(1))
)
knitr::kable(grp_tbl, caption = "Community membership")
```

---

## Polished Plot

A single publication-ready figure: TNA styling, community colours,
edge labels off, weak ties filtered with `minimum`.

```{r publication, fig.width=7, fig.height=6}
splot(W,
      layout       = "oval",
      tna_styling  = TRUE,
      node_fill    = cols,
      edge_labels  = FALSE,
      minimum      = 0.15,
      label_size   = 0.85,
      title        = "Student Collaboration Network")
```

---

## Heatmap

`plot_heatmap()` renders the weight matrix directly — useful for spotting
density asymmetries and the block structure across subgroups.

```{r heatmap, fig.width=6.5, fig.height=5.5}
plot_heatmap(W, title = "Interaction Weight Matrix")
```

---

## Quick Reference

```r
splot(W)                           # basic plot
splot(W, layout = "spring")        # change layout
splot(W, edge_style = 2)           # dashed edges
splot(W, node_fill = cols)         # colour nodes
splot(W, tna_styling = TRUE)       # TNA defaults (oval, arrows, palette)
splot(W, minimum = 0.15)           # filter weak ties
detect_communities(net)            # community detection
plot_heatmap(W)                    # weight matrix heatmap
```
