---
title: "cograph and the Centrality Zoo"
author: "[Mohammed Saqr](https://saqr.me) and [Sonsoles López-Pernas](https://sonsoles.me)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cograph and the Centrality Zoo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Every number on this page is computed from the files tracked in docs/zoo.
zoo_dir <- file.path("..", "..", "docs", "zoo")
fmt <- function(x, digits = 2) formatC(x, format = "f", digits = digits)

coverage <- utils::read.csv(file.path(zoo_dir, "coverage_map.csv"))
coverage$measure <- sub(" .*", "", coverage$cograph_measure)
zoo <- jsonlite::fromJSON(gzfile(file.path(zoo_dir, "correlation.json.gz")))
zoo_matrix <- zoo$matrix
dimnames(zoo_matrix) <- list(zoo$labels, zoo$labels)
package_measures <- cograph::list_centralities()$measure

# Zoo reach of other packages. Each package function is mapped to the cograph
# measure it computes (docs/zoo/package_measures.csv) and from there to a Zoo
# label. centiserve's and CINNA's link-community centrality has no cograph
# counterpart; it is credited to them as the Zoo's "Community centrality",
# the reading least favourable to cograph.
package_functions <- subset(utils::read.csv(file.path(zoo_dir, "package_measures.csv")),
                            nzchar(trimws(cograph)))
unmatched_credit <- c(centiserve = "Community centrality", CINNA = "Community centrality")
zoo_reach <- function(pkg) {
  measures <- subset(package_functions, package %in% pkg)$cograph
  labels <- subset(coverage, measure %in% setdiff(measures, "-"))$zoo_label
  unique(c(labels, unname(unmatched_credit[intersect(pkg, names(unmatched_credit))])))
}
other_packages <- sort(unique(package_functions$package))
package_language <- function(pkg) ifelse(pkg == "networkx", "Python", "R")
display_name <- function(pkg) ifelse(pkg == "networkx", "NetworkX", pkg)
name_list <- function(x) paste(paste(x[-length(x)], collapse = ", "), "and", x[length(x)])
package_table <- function() {
  rows <- lapply(other_packages, function(pkg) data.frame(
    Package = display_name(pkg),
    Language = package_language(pkg),
    `Centrality functions` = sum(package_functions$package == pkg),
    `Zoo measures reached` = length(zoo_reach(pkg)),
    check.names = FALSE
  ))
  others <- do.call(rbind, rows)
  others <- others[order(-others$`Zoo measures reached`, others$Package), ]
  lead <- data.frame(Package = "**cograph**", Language = "R",
                     `Centrality functions` = length(package_measures),
                     `Zoo measures reached` = nrow(coverage), check.names = FALSE)
  pooled <- data.frame(Package = "All nine others, pooled", Language = "",
                       `Centrality functions` = nrow(package_functions),
                       `Zoo measures reached` = length(zoo_reach(other_packages)),
                       check.names = FALSE)
  rbind(lead, others, pooled)
}
reach_table <- package_table()
pooled_reach <- length(zoo_reach(other_packages))

# Measure counts of earlier releases cannot be computed from the current
# code; they are recorded, with their commits, in release_measure_counts.csv.
release_counts <- utils::read.csv(file.path(zoo_dir, "release_measure_counts.csv"))
cran_release <- release_counts[nrow(release_counts), ]

available_table <- function(cov) {
  out <- data.frame(`Zoo measure` = cov$zoo_label,
                    `cograph measure` = paste0("`", cov$measure, "`"),
                    check.names = FALSE)
  out[order(tolower(out$`Zoo measure`)), ]
}
nearest_mapped <- function(label) {
  row <- zoo_matrix[label, coverage$zoo_label]
  best <- which.max(row)
  data.frame(`Zoo measure` = label,
             `Closest measure in cograph` = paste0("`", coverage$measure[best], "`"),
             `Zoo correlation` = fmt(row[[best]]),
             check.names = FALSE)
}
missing_table <- function() {
  out <- do.call(rbind, lapply(setdiff(zoo$labels, coverage$zoo_label), nearest_mapped))
  out[order(-as.numeric(out$`Zoo correlation`), out$`Zoo measure`), ]
}
```

The number of proposed node centralities has grown far faster than the number
of distinct ideas behind them. Many new measures recombine a small set of
ingredients, such as degree, shortest-path distance, walk counts, the leading
eigenvector, the k-shell decomposition and local clustering. A practitioner
who meets an unfamiliar measure needs to know whether it is available and, more
importantly, whether it adds information to simpler measures.

`cograph` offers the largest collection of node centralities of any package
compared in this article, in R or in Python. Its `r length(package_measures)`
measures reach `r nrow(coverage)` of the `r nrow(zoo_matrix)` measures
catalogued in the Centrality Zoo (Shvydun, 2025). Nine established centrality
packages, `r name_list(display_name(other_packages))`, reach `r pooled_reach`
between them when every function they offer is pooled (Table 1). The
collection is also growing quickly: `cograph` `r cran_release$version`, the
release on CRAN in `r format(as.Date(cran_release$date), "%B %Y")`, offered
`r cran_release$measures` measures, and the current version offers
`r length(package_measures)`,
`r fmt(length(package_measures) / cran_release$measures, 1)` times as many.
Every measure is computed by a single function, `centrality()`, which returns
a tidy data frame.

```{r packages}
knitr::kable(reach_table, row.names = FALSE,
             caption = "Table 1. Node centralities in cograph and in nine other packages. A function counts towards the Zoo only if the measure it computes is catalogued there; two functions computing the same measure count once.")
```

## Zoo measures available in cograph

```{r available}
knitr::kable(available_table(coverage), row.names = FALSE)
```

## Zoo measures missing from cograph

```{r missing}
knitr::kable(missing_table(), row.names = FALSE)
```

## References

Shvydun, S. (2025). *Zoo of centralities: Encyclopedia of node metrics in
complex networks*. arXiv:2511.05122. https://arxiv.org/abs/2511.05122
