---
title: "Network Analysis and Visualization with cograph"
description: |
    From raw data to publication-ready network plots, centrality analysis,
    community detection, and statistical testing — all in one package.
date: "2026-04-01"
author:
  - name: Mohammed Saqr
    url: https://saqr.me
    affiliation: University of Eastern Finland
  - name: Sonsoles López-Pernas
    url: https://sonsoles.me
    affiliation: University of Eastern Finland
categories:
  - tutorial
  - R
  - network analysis
  - visualization
warning: false
message: false
fig.align: center
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: false
    code-tools: false
    theme: cosmo
    self-contained: true
execute:
  warning: false
  message: false
knitr:
  opts_chunk:
    fig.width: 8
    fig.height: 7
    dpi: 150
    comment: ""
---

```{r}
#| label: setup
#| include: false
library(tna)
library(cograph)
```

# Introduction


**cograph** is a single package that handles the full workflow: import any network format, compute most centrality measures, run all community detection algorithms and produce publication-ready visualizations for several network types including multi-layaer and higher order networks
Every function accepts every major format — matrices, edge lists, igraph, statnet, qgraph, and tna objects. No manual conversion. No format lock-in.

```{r}
#| eval: false
install.packages("cograph")

# Development version
remotes::install_github("sonsoleslp/cograph")
```


# Data

We use the `group_regulation` dataset from the `tna` package throughout. It contains coded collaborative regulation behaviors from student groups — 9 states forming a directed, weighted transition network.

```{r}
#| label: data
data("group_regulation")
model <- tna(group_regulation)
model
```


# The Plot

One function. One argument.

```{r}
#| label: fig-the-plot
#| fig-cap: "splot(model) — publication-ready with zero configuration"
splot(model)
```

`splot()` detects the input type and applies sensible defaults. For TNA objects: oval layout, weighted directed edges, donut rings encoding initial state probabilities, and automatic color assignment.


# Layouts

Layout choice determines which structural features become visible. The same network can tell different stories depending on spatial arrangement.

```{r}
#| label: fig-layouts
#| fig-cap: "Five layout algorithms on the same network"
#| fig-width: 12
#| fig-height: 8
par(mfrow = c(2, 3), mar = c(1, 1, 2, 1))
for (lay in c("oval", "spring", "circle", "kk", "drl")) {
  splot(model, layout = lay, title = lay)
}
```

| Layout | Best for |
|--------|----------|
| `oval` | Compact, reproducible |
| `spring` | Revealing clusters (Fruchterman-Reingold) |
| `circle` | Comparing node positions |
| `kk` | Regular structures |
| `drl` | Placing similar nodes close together |

Custom coordinates work too — pass a two-column matrix to `layout`.


# Styling

`splot()` exposes 80+ parameters. Here are the ones that matter most.

## Nodes

```{r}
#| label: fig-node-styling
#| fig-cap: "Custom node appearance"
splot(model,
  node_fill = "#4FC3F7",
  node_border_color = "white",
  node_border_width = 2,
  node_size = 10,
  title = "Custom node fill and border")
```

Scale node size by any centrality measure:

```{r}
#| label: fig-scale-nodes
#| fig-cap: "Node size proportional to betweenness centrality"
splot(model,
  scale_nodes_by = "betweenness",
  node_size_range = c(4, 14),
  title = "Scaled by betweenness")
```

## Edges

```{r}
#| label: fig-edge-styling
#| fig-cap: "Filtering weak edges and adjusting curvature"
splot(model,
  minimum = 0.08,
  curvature = 0.3,
  edge_labels = TRUE,
  title = "Edges above 0.08, curved")
```

## Donuts

TNA objects display donut rings by default — the outer ring encodes initial state probabilities. You can supply custom donut values for any network:

```{r}
#| label: fig-donuts
#| fig-cap: "Donut rings showing initial probabilities"
splot(model,
  donut_values = model$inits,
  title = "Initial state probabilities as donuts")
```


# Themes and Palettes

Seven built-in themes change the entire visual style in one argument:

```{r}
#| label: fig-themes
#| fig-cap: "Built-in themes"
#| fig-width: 14
#| fig-height: 8
par(mfrow = c(2, 4), mar = c(1, 1, 2, 1))
for (th in c("default", "dark", "minimal", "gray",
             "nature", "colorblind", "viridis")) {
  splot(model, theme = th, title = th)
}
```

Palette functions generate color vectors:

```{r}
#| label: fig-palettes
#| fig-cap: "Viridis and pastel palettes"
#| fig-width: 12
#| fig-height: 6
par(mfrow = c(1, 2))
splot(model, node_fill = palette_viridis(9), title = "Viridis")
splot(model, node_fill = palette_pastel(9), title = "Pastel")
```


# Input Formats



```{r}
#| label: input-igraph
# From igraph
library(igraph)

mat <- model$weights

# igraph masks several cograph functions — restore them
communities         <- cograph::communities
degree_distribution <- cograph::degree_distribution
is_directed         <- cograph::is_directed
motifs              <- cograph::motifs

g <- graph_from_adjacency_matrix(mat, mode = "directed", weighted = TRUE)
as_cograph(g)

```

Conversion functions go in both directions:

```{r}
#| label: conversions
#| eval: false
to_igraph(mat)       # → igraph object
to_matrix(g)         # → adjacency matrix
to_data_frame(mat)   # → edge list
to_network(mat)      # → statnet network
```


# Filtering and Selection

## Filtering edges

```{r}
#| label: filter-edges
strong <- filter_edges(mat, weight > 0.15)
get_edges(strong)
```

```{r}
#| label: fig-filter-edges
#| fig-cap: "Only edges above 0.15"
splot(strong, title = "Filtered: weight > 0.15")
```

## Filtering nodes

Centrality measures are available as lazy-computed columns inside filter expressions:

```{r}
#| label: filter-nodes
high_degree <- filter_nodes(mat, degree > 4)
get_labels(high_degree)
```

## Selection

```{r}
#| label: select-top
# Top 3 by betweenness
top3 <- select_nodes(mat, top = 3, by = "betweenness")
get_labels(top3)
```

```{r}
#| label: select-neighbors
# Ego network: "monitor" and its neighbors
ego <- select_neighbors(mat, of = "monitor", order = 1)
get_labels(ego)
```

```{r}
#| label: select-edges
# Top 5 strongest edges
top5 <- select_top_edges(mat, n = 5)
get_edges(top5)

# Bridge edges
bridges <- select_bridges(model$weights + t(model$weights))
get_edges(bridges)
```


# Centrality

## All measures at once

`centrality()` computes any combination of 25 measures and returns a tidy data frame:

```{r}
#| label: centrality-all
centrality(mat, measures = c("degree", "strength", "betweenness",
                              "closeness", "pagerank"))
```

## Individual centralities

Each measure has a dedicated function returning a named numeric vector:

```{r}
#| label: centrality-individual
centrality_degree(mat)
centrality_betweenness(mat)
centrality_pagerank(mat)
```

## Directional measures

For directed networks, in/out variants are available:

```{r}
#| label: centrality-directional
centrality_instrength(mat)
centrality_outstrength(mat)
```

## Edge centrality

```{r}
#| label: edge-centrality
cograph::edge_betweenness(mat)
```


# Network Properties

`network_summary()` computes up to 37 network-level metrics in one call:

```{r}
#| label: network-summary
network_summary(mat)
```

```{r}
#| label: network-summary-extended
network_summary(mat, extended = TRUE)
```

Individual property functions:

```{r}
#| label: properties
degree_distribution(mat)

```


# Community Detection

## Algorithms

cograph wraps 11 community detection algorithms with a consistent interface:

```{r}
#| label: communities

# Resolve igraph masking
communities <- cograph::communities

comms <- communities(model$weights + t(model$weights), method = "louvain")
comms
membership(comms)
community_sizes(comms)
modularity(comms)
```

Other algorithms:

```{r}
#| label: community-algorithms
#| eval: false
community_fast_greedy(mat)
community_walktrap(mat)
community_infomap(mat)   # supports directed
community_label_propagation(mat)

```

## Consensus communities

Run an algorithm many times and keep stable assignments:

```{r}
#| label: consensus
mat_sym <- model$weights + t(model$weights)
consensus <- community_consensus(mat_sym, method = "louvain", n_runs = 100, seed = 42)
consensus
```

## Comparing partitions

```{r}
#| label: compare-communities
comms_wt <- community_walktrap(mat_sym)
compare_communities(comms, comms_wt, method = "nmi")
compare_communities(comms, comms_wt, method = "adjusted.rand")
```

## Community visualization

`overlay_communities()` renders a network with smooth blob overlays highlighting each community:

```{r}
#| label: fig-overlay
#| fig-cap: "Community blobs overlaid on the network"
#| fig-width: 10
#| fig-height: 10
overlay_communities(model, "fast_greedy")
```

Manual community definitions work too:

```{r}
#| label: fig-overlay-manual
#| fig-cap: "Theory-driven community grouping"
#| fig-width: 10
#| fig-height: 10
overlay_communities(model, list(
  Regulatory = c("plan", "monitor", "adapt"),
  Social     = c("cohesion", "emotion", "consensus"),
  Task       = c("discuss", "synthesis", "coregulate")
))
```


# Specialized Plots

## Chord diagram

```{r}
#| label: fig-chord
#| fig-cap: "Chord diagram of transitions"
plot_chord(model, minimum = 0.05, title = "Group Regulation — Chord")
```

## Heatmap

```{r}
#| label: fig-heatmap
#| fig-cap: "Adjacency heatmap"
plot_heatmap(model, title = "Transition Matrix")
```

## Alluvial / trajectories

```{r}
#| label: fig-alluvial
#| fig-cap: "Aggregate state transitions over time"
plot_alluvial(group_regulation[,1:4], title = "Regulation Flow")
```

## Difference network

```{r}
#| label: fig-compare
#| fig-cap: "Difference between two networks"
data("group_regulation_long")
prepared <- prepare_data(group_regulation_long,
                         action = "Action", actor = "Actor", time = "Time")
gm <- group_tna(prepared, group = "Achiever")

cograph::plot_compare(gm$High, gm$Low,
  title = "High vs Low Achievers")
```

## Mixed network

`plot_mixed_network()` combines directed and undirected edges in one plot — useful when you have both symmetric relationships (co-occurrence) and asymmetric ones (transitions):

```{r}
#| label: fig-mixed
#| fig-cap: "Directed transitions + undirected co-occurrence"
mat_sym <- (mat + t(mat)) / 2
plot_mixed_network(mat, mat_sym,
  title = "Directed + Undirected")
```


# Bootstrap and Permutation

## Bootstrap

Bootstrap resampling assesses edge stability. Significant edges appear solid; non-significant edges appear dashed:

```{r}
#| label: bootstrap
#| cache: true
set.seed(42)
boot <- bootstrap(model, iter = 1000)
```

```{r}
#| label: fig-boot-styled
#| fig-cap: "Bootstrap: solid = stable, dashed = unstable"
splot(boot)
```

```{r}
#| label: fig-boot-sig
#| fig-cap: "Significant edges only"
splot(boot, display = "significant", show_stars = TRUE)
```

```{r}
#| label: fig-boot-ci
#| fig-cap: "With confidence intervals"
splot(boot, show_ci = TRUE)
```

## Permutation test

Compare two groups and identify significantly different edges:

```{r}
#| label: permutation
#| cache: true
set.seed(42)
perm <- tna::permutation_test(gm$High, gm$Low, iter = 1000)
```

```{r}
#| label: fig-perm
#| fig-cap: "Green = High > Low, Red = Low > High (p < 0.05)"
splot(perm, show_nonsig = TRUE, show_stars = TRUE)
```


# Multi-Cluster Visualization

`plot_mcml()` draws two layers simultaneously: individual nodes inside cluster shells (bottom) and aggregated cluster-level summary pies (top).

```{r}
#| label: fig-mcml
#| fig-cap: "Two-layer hierarchical cluster view"
#| fig-width: 9
#| fig-height: 9
clusters <- list(
  Social    = c("discuss", "consensus", "cohesion", "emotion"),
  Cognitive = c("plan", "monitor", "adapt", "synthesis"),
  Meta      = c("coregulate")
)

plot_mcml(mat, clusters, mode = "tna",
  title = "Collaborative Regulation Clusters")
```

`plot_mtna()` provides a flat single-layer alternative:

```{r}
#| label: fig-mtna
#| fig-cap: "Flat cluster layout"
#| fig-width: 9
#| fig-height: 9
plot_mtna(mat, clusters, show_labels = TRUE, label_abbrev = 4,
  title = "Flat Cluster Map")
```


# Nestimate Integration

The **Nestimate** package estimates networks from sequence data using multiple methods. Its objects dispatch through `splot()` automatically.

```{r}
#| label: nestimate
library(Nestimate)

net <- build_network(group_regulation, method = "relative")
splot(net, title = "Nestimate: relative transitions")
```

Bootstrap stability:

```{r}
#| label: nestimate-boot
#| cache: true
set.seed(42)
nboot <- bootstrap_network(net, iter = 500)
splot(nboot, title = "Nestimate bootstrap")
```

Group comparison:

```{r}
#| label: nestimate-group
#| fig-width: 12
#| fig-height: 6
grp <- build_network(group_regulation_long, method = "relative",
  action = "Action", actor = "Actor", time = "Time",
  group = "Achiever")
splot(grp)
```


# Motifs

Motif analysis identifies recurring local connectivity patterns — the building blocks of network structure. cograph uses the MAN (Mutual, Asymmetric, Null) classification for directed triads: 16 possible patterns from empty (003) to fully connected (300).

## Census

`motifs()` counts how often each MAN type appears and tests significance against a configuration model null:

```{r}
#| label: motifs-census
mot <- motifs(model, significance = TRUE, n_perm = 100, seed = 42)
mot

```

## Visualization



```{r}
#| label: fig-motifs-significance
#| fig-cap: "Significance: z-scores against configuration model"
plot(mot, type = "significance")
```

```{r}
#| label: fig-motifs-patterns
#| fig-cap: "MAN triad pattern diagrams"
#| fig-width: 10
#| fig-height: 6
plot(mot, type = "patterns")
```

## Named subgraphs

`subgraphs()` identifies the specific node triples forming each pattern — which states participate in which motifs:

```{r}
#| label: subgraphs
sg <- subgraphs(model, significance = TRUE, top = 10, pattern="triangle")
sg

```

```{r}
#| label: fig-subgraphs
#| fig-cap: "Top triads as network diagrams"
#| fig-width: 10
#| fig-height: 6
plot(sg, n = 10, ncol = 5)

```


# Higher-Order Networks

Standard TNA assumes first-order Markov dynamics: the next state depends only on the current state. Higher-order analysis tests whether longer sequential memory exists — cases where what happened two or three steps ago changes the transition probabilities.

## Model order selection

`build_mogen()` fits Markov models at increasing orders and selects the best via AIC/BIC:

```{r}
#| label: hon-setup
data("human_cat", package = "Nestimate")
hon_net <- build_network(human_cat, method = "tna",
  action = "category", time = "timestamp", session = "session_id")
```

```{r}
#| label: mogen
mg <- build_mogen(hon_net, max_order = 4)
summary(mg)
```

```{r}
#| label: fig-mogen
#| fig-cap: "Model selection: information criteria across Markov orders"
#| fig-width: 8
#| fig-height: 5
plot(mg)
```

## Higher-Order Network (HON)

HON detects *where* in the state space higher-order dependencies exist — which transitions change depending on prior context:

```{r}
#| label: hon
hon <- build_hon(hon_net)
hon
```

## Path anomaly detection (HYPA)

HYPA identifies paths that occur significantly more or less often than expected under a hypergeometric null model:

```{r}
#| label: hypa
hypa <- build_hypa(hon_net)
table(hypa$scores$anomaly)
```

Over-represented paths — learned behavioral routines:

```{r}
#| label: hypa-over
over <- subset(hypa$scores, anomaly == "over")

head(over)

```

## Simplicial visualization

`plot_simplicial()` renders higher-order pathways as smooth blobs over the network. Source states appear in blue, target states in red.

```{r}
#| label: fig-simplicial
#| fig-cap: "Top 6 higher-order pathways (HON)"
#| fig-width: 10
#| fig-height: 10
plot_simplicial(hon_net, max_pathways = 6,
  title = "Higher-Order Pathways")
```

Dismantled view — one panel per pathway:

```{r}
#| label: fig-simplicial-dismantled
#| fig-cap: "Individual pathway panels"
#| fig-width: 12
#| fig-height: 12
plot_simplicial(hon_net, max_pathways = 9,
  dismantled = TRUE, ncol = 3)
```

HYPA anomalous pathways:

```{r}
#| label: fig-simplicial-hypa
#| fig-cap: "Anomalous pathways detected by HYPA"
#| fig-width: 12
#| fig-height: 12
plot_simplicial(hon_net, method = "hypa", max_pathways = 9,
  dismantled = TRUE, ncol = 3)
```


# Robustness

`robustness()` simulates network degradation under targeted and random node/edge removal:

```{r}
#| label: fig-robustness
#| fig-cap: "Network robustness under targeted and random node removal"
plot_robustness(x = mat,
  measures = c("betweenness", "degree", "random"),
  n_iter = 50, seed = 42,
  title = "Node Removal Robustness")
```





# References {.unnumbered}

- Saqr, M., López-Pernas, S., Törmänen, T., Kaliisa, R., Misiejuk, K., & Tikka, S. (2025). Transition Network Analysis: A Novel Framework for Modeling, Visualizing, and Identifying the Temporal Patterns of Learners and Learning Processes. In *Proceedings of the 15th International Learning Analytics and Knowledge Conference (LAK '25)* (pp. 351--361). ACM. <https://doi.org/10.1145/3706468.3706513>

- Tikka, S., López-Pernas, S., & Saqr, M. (2025). tna: An R Package for Transition Network Analysis. *Applied Psychological Measurement*. <https://doi.org/10.1177/01466216251348840>

- cograph: <https://github.com/sonsoleslp/cograph>
