---
title: "TNA Plotting Gallery and Visual Smoke Test"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5.5,
  fig.dpi = 120,
  dpi = 120,
  warning = FALSE,
  message = FALSE,
  error = FALSE
)

library(cograph)
library(tna)

set.seed(20260823)
```

This page is an executable visual smoke test for the complete plotting surface
of **tna** and its integration with **cograph**. Knitting stops on the first
plotting error. Statistical resampling uses deliberately small iteration counts
so that the page can be rebuilt during development; the results below are for
visual and API verification, not inference.

The gallery covers:

- `plot()` for single and grouped TNA models, bootstrap objects, centralities,
  cliques, communities, comparisons, permutations, reliability, sequence
  comparisons, and stability objects;
- `hist()`, `plot_model()`, `plot_compare()`, `plot_frequencies()`,
  `plot_mosaic()`, `plot_sequences()`, and `plot_associations()`;
- cograph's enhanced TNA bootstrap, difference, permutation, forest, and
  heterogeneous-network renderers.

```{r versions}
data.frame(
  package = c("tna", "cograph"),
  version = c(
    as.character(utils::packageVersion("tna")),
    as.character(utils::packageVersion("cograph"))
  )
)
```

# Shared fixtures

The fixtures use 400 rows from `group_regulation`, split into two groups. This
is large enough to exercise real TNA objects while keeping resampling fast.

```{r fixtures, include=FALSE}
data("group_regulation", package = "tna")

gallery_data <- utils::head(group_regulation, 400)
gallery_group <- rep(c("First half", "Second half"), each = 200)

model <- tna::tna(gallery_data)
model_first <- tna::tna(gallery_data[gallery_group == "First half", ])
model_second <- tna::tna(gallery_data[gallery_group == "Second half", ])
group_models <- tna::group_tna(gallery_data, group = gallery_group)

frequency_model <- tna::ftna(gallery_data)
group_frequency_models <- tna::group_ftna(
  gallery_data,
  group = gallery_group
)

# A small long-format fixture ensures the tna_data plotting methods are also
# exercised, including grouping through retained metadata.
long_fixture <- data.frame(
  actor = rep(sprintf("P%02d", 1:24), each = 6),
  step = rep(1:6, times = 24),
  cohort = rep(rep(c("A", "B"), each = 12), each = 6),
  event = sample(c("plan", "monitor", "evaluate", "adapt"), 144, TRUE)
)
prepared_data <- tna::prepare_data(
  long_fixture,
  actor = "actor",
  order = "step",
  action = "event"
)
```

# Core network plots

## Single TNA model

Exercises `plot.tna()` and its default cograph renderer.

```{r plot-tna, fig.width=8, fig.height=7}
plot(model, title = "Single TNA model", minimum = 0.05)
```

## Grouped TNA models

Exercises `plot.group_tna()`.

```{r plot-group-tna, fig.show='hold', out.width='49%', fig.width=7, fig.height=6}
plot(group_models, minimum = 0.05)
```

## Heterogeneous TNA model

Passing a complete two-part `node_list` routes `plot.tna()` through cograph's
heterogeneous TNA renderer.

```{r plot-heterogeneous-tna, fig.width=9, fig.height=6}
split_at <- ceiling(length(model$labels) / 2)
node_list <- list(
  model$labels[seq_len(split_at)],
  model$labels[seq.int(split_at + 1, length(model$labels))]
)
plot(
  model,
  node_list = node_list,
  title = "Heterogeneous TNA model",
  minimum = 0.05
)
```

## Weight matrix

Exercises the exported `plot_model()` entry point.

```{r plot-model-matrix, fig.width=8, fig.height=7}
tna::plot_model(
  model$weights,
  labels = model$labels,
  title = "TNA weight matrix"
)
```

# Edge and state distributions

## Edge-weight histograms

Exercises both `hist.tna()` and `hist.group_tna()`.

```{r hist-tna}
hist(model, main = "Single-model edge weights")
```

```{r hist-group-tna, fig.show='hold', out.width='49%'}
hist(group_models)
```

## State frequencies

Exercises `plot_frequencies.tna()` and `plot_frequencies.group_tna()`.

```{r plot-frequencies-tna}
tna::plot_frequencies(model)
```

```{r plot-frequencies-group}
tna::plot_frequencies(group_models)
```

## Mosaic plots

Exercises mosaic methods for frequency TNA, grouped frequency TNA, and
prepared `tna_data` objects.

```{r plot-mosaic-tna}
tna::plot_mosaic(frequency_model)
```

```{r plot-mosaic-group}
tna::plot_mosaic(group_frequency_models)
```

```{r plot-mosaic-tna-data}
tna::plot_mosaic(prepared_data, group = "cohort")
```

## Association network

Exercises `plot_associations.tna()` using the required integer-valued
frequency model.

```{r plot-associations, fig.width=8, fig.height=7}
tna::plot_associations(
  frequency_model,
  title = "Association network"
)
```

# Sequence plots

## Single-model index and distribution plots

Exercises `plot_sequences.tna()` in both modes.

```{r plot-sequences-tna-index, fig.width=9, fig.height=6}
tna::plot_sequences(model, type = "index", tick = 1)
```

```{r plot-sequences-tna-distribution, fig.width=9, fig.height=6}
tna::plot_sequences(model, type = "distribution", geom = "area", tick = 1)
```

## Grouped sequences

Exercises `plot_sequences.group_tna()`.

```{r plot-sequences-group, fig.width=10, fig.height=6}
tna::plot_sequences(group_models, type = "distribution", tick = 1)
```

## Data-frame sequences

Exercises `plot_sequences.default()` with an explicit grouping vector.

```{r plot-sequences-data-frame, fig.width=10, fig.height=6}
tna::plot_sequences(
  gallery_data,
  group = gallery_group,
  type = "distribution",
  tick = 1
)
```

## Prepared TNA data

Exercises `plot_sequences.tna_data()` and metadata-based grouping.

```{r plot-sequences-tna-data, fig.width=10, fig.height=6}
tna::plot_sequences(
  prepared_data,
  group = "cohort",
  type = "index",
  tick = 1
)
```

# Structural analysis plots

```{r structural-objects, include=FALSE}
centrality_result <- tna::centralities(model)
group_centrality_result <- tna::centralities(group_models)

community_result <- tna::communities(model, methods = "walktrap")
group_community_result <- tna::communities(
  group_models,
  methods = "walktrap"
)

clique_result <- tna::cliques(model, size = 2, threshold = 0)
group_clique_result <- tna::cliques(group_models, size = 2, threshold = 0)
```

## Centralities

Exercises `plot.tna_centralities()` and `plot.group_tna_centralities()`.

```{r plot-centralities, fig.width=10, fig.height=7}
plot(centrality_result, ncol = 3)
```

```{r plot-group-centralities, fig.width=10, fig.height=7}
plot(group_centrality_result, ncol = 3)
```

## Communities

Exercises `plot.tna_communities()` and `plot.group_tna_communities()`.

```{r plot-communities, fig.width=8, fig.height=7}
plot(community_result, title = "Walktrap communities")
```

```{r plot-group-communities, fig.show='hold', out.width='49%', fig.width=7, fig.height=6}
plot(group_community_result)
```

## Cliques

Exercises `plot.tna_cliques()` and `plot.group_tna_cliques()`. Only the first
dyad is drawn for each object to keep the gallery compact.

```{r plot-cliques, fig.width=7, fig.height=6}
plot(clique_result, n = 1, ask = FALSE, title = "First dyad")
```

```{r plot-group-cliques, fig.show='hold', out.width='49%', fig.width=7, fig.height=6}
plot(group_clique_result, n = 1, ask = FALSE)
```

# Bootstrap plots

```{r bootstrap-objects, include=FALSE}
set.seed(42)
bootstrap_result <- tna::bootstrap(model, iter = 30)
group_bootstrap_result <- tna::bootstrap(group_models, iter = 20)
```

## TNA bootstrap method

Exercises `plot.tna_bootstrap()`.

```{r plot-bootstrap-tna, fig.width=8, fig.height=7}
plot(bootstrap_result, title = "TNA bootstrap")
```

## Grouped bootstrap method

Exercises `plot.group_tna_bootstrap()`.

```{r plot-bootstrap-group, fig.show='hold', out.width='49%', fig.width=7, fig.height=6}
plot(group_bootstrap_result)
```

## Cograph bootstrap render modes

These plots verify all enhanced `splot.tna_bootstrap()` display modes.

```{r splot-bootstrap-significant, fig.width=8, fig.height=7}
cograph::splot(
  bootstrap_result,
  display = "significant",
  title = "Bootstrap: significant edges",
  show_stars = TRUE
)
```

```{r splot-bootstrap-styled, fig.width=8, fig.height=7}
cograph::splot(
  bootstrap_result,
  display = "styled",
  title = "Bootstrap: styled full network",
  show_stars = TRUE
)
```

```{r splot-bootstrap-ci, fig.width=8, fig.height=7}
cograph::splot(
  bootstrap_result,
  display = "ci",
  title = "Bootstrap: confidence intervals",
  show_ci = TRUE
)
```

```{r plot-bootstrap-forest, fig.width=8, fig.height=7}
cograph::plot_bootstrap_forest(
  bootstrap_result,
  layout = "grouped",
  title = "Bootstrap forest grouped by source"
)
```

# Permutation plots

```{r permutation-objects, include=FALSE}
set.seed(43)
permutation_result <- tna::permutation_test(
  model_first,
  model_second,
  iter = 30
)
group_permutation_result <- tna::permutation_test(group_models, iter = 20)
```

## TNA permutation method

Exercises `plot.tna_permutation()`.

```{r plot-permutation-tna, fig.width=8, fig.height=7}
plot(permutation_result, title = "TNA permutation differences")
```

## Grouped permutation method

Exercises `plot.group_tna_permutation()`.

```{r plot-permutation-group, fig.width=8, fig.height=7}
plot(group_permutation_result)
```

## Cograph permutation renderer

Exercises the richer cograph permutation display directly.

```{r plot-permutation-cograph, fig.width=8, fig.height=7}
cograph::plot_permutation(
  permutation_result,
  title = "Cograph permutation renderer",
  show_nonsig = TRUE
)
```

# Stability and reliability plots

```{r validation-objects, include=FALSE}
set.seed(44)
stability_result <- tna::estimate_cs(
  model,
  measures = c("InStrength", "OutStrength"),
  drop_prop = c(0.3, 0.6),
  iter = 10
)
group_stability_result <- tna::estimate_cs(
  group_models,
  measures = c("InStrength", "OutStrength"),
  drop_prop = c(0.3, 0.6),
  iter = 10
)
reliability_result <- tna::reliability(model, iter = 30)
```

## Centrality stability

Exercises `plot.tna_stability()`.

```{r plot-stability, fig.width=9, fig.height=6}
plot(stability_result)
```

## Grouped centrality stability

Exercises `plot.group_tna_stability()`. The method returns its ggplots
invisibly, so the gallery prints each returned plot explicitly.

```{r plot-group-stability, fig.show='hold', out.width='49%', fig.width=8, fig.height=6}
group_stability_plots <- plot(group_stability_result)
invisible(lapply(group_stability_plots, print))
```

## Reliability distributions

Exercises all three modes of `plot.tna_reliability()`.

```{r plot-reliability-histogram}
plot(reliability_result, type = "histogram")
```

```{r plot-reliability-density}
plot(reliability_result, type = "density")
```

```{r plot-reliability-boxplot}
plot(reliability_result, type = "boxplot")
```

# Comparison plots

```{r comparison-objects, include=FALSE}
comparison_result <- tna::compare(
  model_first,
  model_second,
  measures = c("InStrength", "OutStrength", "Betweenness")
)
sequence_comparison_result <- tna::compare_sequences(
  group_models,
  sub = 1:2,
  min_freq = 1,
  test = FALSE
)
```

## Difference networks

Exercises `plot_compare.tna()` and `plot_compare.group_tna()`, both of which
delegate to `cograph::plot_compare()`.

```{r plot-compare-tna, fig.width=8, fig.height=7}
tna::plot_compare(
  model_first,
  model_second,
  title = "First half minus second half"
)
```

```{r plot-compare-group, fig.width=8, fig.height=7}
tna::plot_compare(group_models)
```

## TNA comparison object

Exercises every mode of `plot.tna_comparison()`.

```{r plot-comparison-heatmap, fig.width=8, fig.height=7}
plot(comparison_result, type = "heatmap")
```

```{r plot-comparison-scatterplot}
plot(comparison_result, type = "scatterplot")
```

```{r plot-comparison-centrality-heatmap, fig.width=9, fig.height=7}
plot(comparison_result, type = "centrality_heatmap")
```

```{r plot-comparison-weight-density}
plot(comparison_result, type = "weight_density")
```

## Sequence comparison

Exercises `plot.tna_sequence_comparison()`.

```{r plot-sequence-comparison, fig.width=9, fig.height=6}
plot(sequence_comparison_result, n = 10, cells = TRUE)
```

# Build result

If this section is visible, every plotting chunk above completed without an
error.

```{r build-result}
data.frame(
  status = "PASS",
  tna = as.character(utils::packageVersion("tna")),
  cograph = as.character(utils::packageVersion("cograph")),
  rendered_at = format(Sys.time(), tz = "UTC", usetz = TRUE)
)
```
