---
title: "Centrality Zoo coverage matrix"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 12, fig.height = 12, dpi = 110)
# Resolve everything from the repository root, so the document renders the
# same whether it is knitted in place or from elsewhere.
root <- normalizePath(".")
while (!file.exists(file.path(root, "DESCRIPTION")) &&
       dirname(root) != root) {
  root <- dirname(root)
}
at <- function(...) file.path(root, ...)
zoo <- jsonlite::fromJSON(gzfile(at("docs/zoo/correlation.json.gz")))
labels <- zoo$labels
M <- zoo$matrix
dimnames(M) <- list(labels, labels)

# Zoo label -> cograph measure, emitted by docs/zoo/zoo_coverage.py
covered <- utils::read.csv(at("docs/zoo/coverage_map.csv"), stringsAsFactors = FALSE)
names(covered) <- c("zoo", "cograph")
covered$batch <- ifelse(grepl("batch 7", covered$cograph), "7",
                 ifelse(grepl("batch 8", covered$cograph), "8",
                 ifelse(grepl("batch 9", covered$cograph), "9", "earlier")))
covered$cograph <- sub(" \\(also .*\\)| \\[batch [0-9]\\]", "", covered$cograph)
covered <- covered[!duplicated(covered$cograph), ]
uncovered <- setdiff(labels, covered$zoo)
best <- apply(M[uncovered, covered$zoo, drop = FALSE], 1, max)
novel <- names(best)[best < 0.70]

# Our own averaged Kendall tau over 19 real networks
ours_path <- at("local_testing_and_equivalence/zoo_consistency_matrix.csv")
has_ours <- file.exists(ours_path)
if (has_ours) {
  ours <- as.matrix(utils::read.csv(ours_path, row.names = 1,
                                    check.names = FALSE))
  colnames(ours) <- rownames(ours)
}
prof <- if (has_ours) {
  utils::read.csv(at("local_testing_and_equivalence/zoo_consistency.csv"),
                  stringsAsFactors = FALSE)
} else {
  NULL
}

seq_pal <- grDevices::colorRampPalette(c("#FFFFFF", "#4A6FE3"))(100)
div_pal <- grDevices::colorRampPalette(c("#D33F6A", "#FFFFFF", "#4A6FE3"))(101)
heat <- function(mat, main, cex = 0.7, pal = seq_pal, zlim = c(0, 1),
                 mar = c(1, 14, 12, 1)) {
  n_r <- nrow(mat); n_c <- ncol(mat)
  op <- graphics::par(mar = mar); on.exit(graphics::par(op), add = TRUE)
  graphics::image(seq_len(n_c), seq_len(n_r), t(mat[n_r:1, , drop = FALSE]),
                  col = pal, zlim = zlim, axes = FALSE, xlab = "", ylab = "",
                  main = main)
  graphics::axis(3, at = seq_len(n_c), labels = colnames(mat), las = 2,
                 cex.axis = cex, tick = FALSE, line = -0.5)
  graphics::axis(2, at = seq_len(n_r), labels = rev(rownames(mat)), las = 1,
                 cex.axis = cex, tick = FALSE, line = -0.5)
}
```

Source: average Kendall rank correlation between node rankings of
`r length(labels)` measures over 648 ICON networks
([Centrality Zoo](https://centralityzoo.github.io/comparison/), Shvydun 2025).
`cograph` implements `r nrow(covered)` distinct measures covering
`r nrow(read.csv(at("docs/zoo/coverage_map.csv")))` of those labels,
`r sum(covered$batch != "earlier")` of them added in batches 7 to 9.
Colour: white = 0, blue = 1 for correlations; red to blue through white for
differences. Every figure is followed by the numbers, so nothing is encoded
by colour alone.

## Covered measures: the Zoo's view

Rows and columns are labelled with the cograph name and ordered by
hierarchical clustering of `1 - tau`, so redundant measures sit together.

```{r covered-heatmap}
C <- M[covered$zoo, covered$zoo]
dimnames(C) <- list(covered$cograph, covered$cograph)
ord <- stats::hclust(stats::as.dist(1 - C), method = "average")$order
C <- C[ord, ord]
heat(C, "Zoo: Kendall tau among the measures cograph implements", cex = 0.6)
```

### Redundant pairs inside cograph (tau >= 0.95)

```{r covered-pairs}
pairs <- which(upper.tri(C) & C >= 0.95, arr.ind = TRUE)
tab <- data.frame(measure_1 = rownames(C)[pairs[, 1]],
                  measure_2 = colnames(C)[pairs[, 2]],
                  tau = round(C[pairs], 2))
tab <- unique(tab[tab$measure_1 != tab$measure_2, ])
tab <- tab[order(-tab$tau, tab$measure_1), ]
rownames(tab) <- NULL
knitr::kable(tab)
```

## Our measurements against the Zoo

```{r ours-setup, eval = has_ours}
shared <- intersect(rownames(ours), colnames(C))
shared <- colnames(C)[colnames(C) %in% shared]   # keep the clustered order
Z <- C[shared, shared]
O <- abs(ours[shared, shared])                   # Zoo tau are non-negative
D <- O - Z
paired <- data.frame(zoo = Z[upper.tri(Z)], ours = O[upper.tri(O)])
# A pair is NA when one of its measures could not be computed on any shared
# network (alpha and power fail with a singular solve on les_miserables).
paired <- paired[stats::complete.cases(paired), ]
```

`r if (!has_ours) "This half needs the measured matrix, which is not in the repository because it is a few megabytes of derived data. Produce it with Rscript local_testing_and_equivalence/zoo_consistency.R and knit again."`

```{r ours-note, results = "asis", eval = has_ours}
dif <- abs(paired$ours - paired$zoo)
cat(sprintf(paste0("The same %d measures computed on 19 real undirected ",
                   "networks (10 to 81 nodes: karate, kite, UKfaculty, ",
                   "macaque, 12 food webs, les_miserables, florentine, ",
                   "davis), pairwise Kendall tau averaged over networks, ",
                   "then compared pair by pair.\n\n"),
            length(shared)))
cat(sprintf(paste0("| Statistic over the %d measure pairs | Value |\n",
                   "|---|---|\n",
                   "| Correlation between the two matrices | %.2f |\n",
                   "| Mean absolute difference | %.2f |\n",
                   "| Median absolute difference | %.2f |\n",
                   "| Pairs agreeing within 0.20 | %.0f%% |\n"),
            nrow(paired), stats::cor(paired$zoo, paired$ours),
            mean(dif), stats::median(dif), 100 * mean(dif < 0.2)))
drop <- c("constraint", "clusterrank", "dmnc", "local_dimension",
          "flow_coefficient")
kp <- !(shared %in% drop)
Z2 <- Z[kp, kp]; O2 <- O[kp, kp]
p2 <- stats::complete.cases(cbind(Z2[upper.tri(Z2)], O2[upper.tri(O2)]))
cat(sprintf(paste0("\nFive measures carry most of the disagreement: constraint, ",
                   "clusterrank, dmnc, local_dimension and flow_coefficient. ",
                   "Dropping them lifts the correlation to **%.2f** over the ",
                   "remaining %d pairs. The first three match their reference ",
                   "implementations exactly, so the gap is about the Zoo's ",
                   "conventions rather than cograph's arithmetic.\n"),
            stats::cor(Z2[upper.tri(Z2)][p2], O2[upper.tri(O2)][p2]),
            sum(p2)))
```

```{r ours-heatmap, fig.height = 12, eval = has_ours}
heat(O, "Ours: Kendall tau over 19 real networks (same ordering)", cex = 0.6)
```

```{r diff-heatmap, fig.height = 12, eval = has_ours}
heat(D, "Ours minus Zoo (blue = we find them more alike)", cex = 0.6,
     pal = div_pal, zlim = c(-1, 1))
```

```{r scatter, fig.width = 7, fig.height = 7, eval = has_ours}
op <- graphics::par(mar = c(4, 4, 3, 1)); on.exit(graphics::par(op), add = TRUE)
graphics::plot(paired$zoo, paired$ours, pch = 16, cex = 0.35,
               col = grDevices::adjustcolor("#0072B2", alpha.f = 0.25),
               xlab = "Zoo tau (648 ICON networks)",
               ylab = "our tau (19 real networks)",
               main = "Every pair of covered measures", asp = 1,
               xlim = c(0, 1), ylim = c(0, 1))
graphics::abline(0, 1, col = "#000000", lty = 2)
graphics::legend("topleft", legend = c("one measure pair", "equality"),
                 pch = c(16, NA), lty = c(NA, 2),
                 col = c("#0072B2", "#000000"), bty = "n", cex = 0.9)
```

### Where the two disagree most

`flow_coefficient` against `transitivity` is the clearest case: the Zoo
prints an unbounded formula that differs from the paper's, while ours
equals one minus the clustering coefficient on an undirected graph, so the
two matrices report 0.02 and 1.00 for the same pair. `constraint` is
negatively oriented, so its agreement depends on a sign convention the Zoo
does not state, and `dmnc` differs because `centiserve::dmnc()` counts a
component's edges in the wrong index space.

An earlier run of this report put `katz` among the worst rows. That turned
out to be cograph's own defect rather than a convention difference: Katz
converges only for an attenuation below one over the spectral radius, and
the 0.1 default is invalid on several of these food webs. This run uses a
valid attenuation per network, and `katz` moved from a profile correlation
of 0.56 to 0.76. `centrality()` now warns when the attenuation cannot
converge.

```{r worst-pairs, eval = has_ours}
idx <- which(upper.tri(D), arr.ind = TRUE)
dd <- data.frame(measure_1 = rownames(D)[idx[, 1]],
                 measure_2 = colnames(D)[idx[, 2]],
                 zoo = round(Z[idx], 2), ours = round(O[idx], 2),
                 difference = round(D[idx], 2))
dd <- dd[order(-abs(dd$difference)), ]
rownames(dd) <- NULL
knitr::kable(head(dd, 25))
```

## Per-measure agreement with the Zoo

`r if (!has_ours) "Needs the measured matrix; see above."`

Each measure's row of tau values, correlated with the Zoo's row for the
same measure. Established measures set the achievable band, since the two
matrices come from different network collections.

```{r profile, eval = has_ours}
prof$batch <- covered$batch[match(prof$measure, covered$cograph)]
pt <- prof[, c("measure", "batch", "profile_cor", "mean_abs_diff",
               "nearest_ours", "tau_ours", "nearest_zoo", "tau_zoo")]
pt$profile_cor <- round(pt$profile_cor, 2)
pt$mean_abs_diff <- round(pt$mean_abs_diff, 2)
pt$tau_ours <- round(pt$tau_ours, 2)
pt$tau_zoo <- round(pt$tau_zoo, 2)
pt <- pt[order(pt$profile_cor), ]
rownames(pt) <- NULL
knitr::kable(pt)
```

## Uncovered measures with real new information

The `r length(novel)` Zoo measures whose maximum tau against any cograph
measure is below 0.70, against all covered measures.

```{r novel-heatmap, fig.height = 9}
N <- M[novel, covered$zoo]
colnames(N) <- covered$cograph
N <- N[order(best[novel]), ord]
heat(N, "Novel Zoo measures (rows) vs cograph measures (columns)", cex = 0.6)
```

```{r novel-table}
nearest <- covered$cograph[apply(M[novel, covered$zoo, drop = FALSE], 1,
                                 which.max)]
nt <- data.frame(zoo_measure = novel, max_tau = round(best[novel], 2),
                 nearest_cograph = nearest)
nt <- nt[order(nt$max_tau), ]
rownames(nt) <- NULL
knitr::kable(nt)
```

## Full coverage document

```{r coverage-md, results = "asis"}
cat(readLines(at("docs/CENTRALITY-ZOO-COVERAGE.md"))[-1], sep = "\n")
```
